### 2020-11-16 algebra.tex
Add files via upload

\documentclass[12pt]{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}

\usepackage{amscd, amssymb, mathtools, amsthm, amsmath}
\usepackage{enumerate}
% Palatino for main text and math
\usepackage[osf,sc]{mathpazo}

% Helvetica for sans serif
% (scaled to match size of Palatino)
\usepackage[scaled=0.90]{helvet}

% Bera Mono for monospaced
% (scaled to match size of Palatino)
\usepackage[scaled=0.85]{beramono}

\usepackage{hyperref}

% To write appendixes
\usepackage[page]{appendix}

\renewcommand{\thesubsection}{\arabic{subsection}}
%
%
\newenvironment{eq}{\begin{equation}}{\end{equation}}
%
\newenvironment{remarks}{{\bf Remarks}:\begin{enumerate}}{\end{enumerate}}
\newenvironment{examples}{{\bf Examples}:\begin{enumerate}}{\end{enumerate}}  
%
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}[proposition]{Lemma}
\newtheorem{definition}[proposition]{Definition}
\newtheorem{theorem}[proposition]{Theorem}
\newtheorem{cor}[proposition]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{pretheorem}[proposition]{Pretheorem}
\newtheorem{hypothesis}[proposition]{Hypothesis}
\newtheorem{example}[proposition]{Example}
\newtheorem*{rem}{Remark}
\newtheorem{remark}[proposition]{Remark}
\newtheorem{ex}[proposition]{Exercise}
\newtheorem{cond}[proposition]{Conditions}
\newtheorem{cons}[proposition]{Construction}
%
\newtheorem{problem}[proposition]{Problem}
\newtheorem{construction}[proposition]{Construction}
%
\newtheorem*{nota}{Notation}
\newtheorem{notation}{Notation}
\newtheorem*{axiom}{Axiom}

% For diagrams:
\usepackage{tikz-cd}
\usetikzlibrary{cd}

% To avoid automatic identation of paragraphs:
\usepackage[parfill]{parskip}

% To create an index:
\usepackage{makeidx}

% To make the index and bibliography appear in the table of contents:
\usepackage[nottoc]{tocbibind}

\makeindex

\begin{document}

\title{Blueprint}
\author{}
\date{\today}
\maketitle

Let $k$ be an algebraically closed field and $A$ denote the ring $k \left[ x_1, \dots, x_n \right]$. \\

\begin{definition}[affine $n$-space] 
	The affine $n$-space over $k$, denoted $\mathbb{A}^n_k$ or simply $\mathbb{A}^n$, is the set of all $n$-tuples of elements of $k$.  
\end{definition}

\begin{remark}
	An element $P$ of $\mathbb{A}^n$ will be called a point. \\
	If $P = (a_1, \dots, a_n)$ with $a_i \in k$, then $a_i$ will be called the $i$th coordinate of $P$.
\end{remark}

\begin{notation}
	if $P = (a_1, \dots, a_n)$ (\textit{resp.} $f$) belongs to $\mathbb{A}^n$ (\textit{resp.} $A$), then $f(P)$ is $f(a_1, \dots, a_n)$.
\end{notation}

\begin{definition}[zero set]
	If $T$ is any subset of $A$, one defines the zero set of $T$, denoted $Z(T)$, to be the common zeros of all the elements of $T$. \\
	In other words one has
	\[
	Z(T) \coloneqq \lbrace P \in \mathbb{A}^n \mid f(P) = 0 \quad \text{for all}\, f \in T \rbrace \, . 
	\]
\end{definition}

\begin{definition}[algebraic set]
	A subset $Y$ of $\mathbb{A}^n$ is an algebraic set if there exists a subset $T \subseteq A$ such that $Y = Z(T)$. 
\end{definition}

\begin{ex}
	Prove the empty space $\emptyset$ and the whole space $\mathbb{A}^n$ are algebraic sets.
\end{ex}

\begin{ex}
	Prove the intersection of any family of algebraic sets is an algebraic set.
\end{ex}

\begin{ex}
	Prove the union of two algebraic sets is an algebraic set.
\end{ex}

\begin{definition}[Zariski topology]
	One defines the Zariski topology on $\mathbb{A}^n$ by taking the open sets to be the complements of the algebraic sets.
\end{definition}

\begin{ex}
	Prove the Zariski topology is a topology. 
\end{ex}

\begin{definition}[irreducible subset]
	A nonempty subset $Y$ of a topological space $X$ is irreducible if $Y$ cannot be expressed as the union of two proper closed subsets of $X$. 
\end{definition}

\begin{definition}[affine algebraic variety]
	An affine algebraic variety or simply an affine variety is an irreducible closed subset of $\mathbb{A}^n$ endowed with the induced topology. 
\end{definition}

\begin{definition}[quasi-affine variety]
	A quasi-affine variety is an open subset of an affine variety. 
\end{definition}

\end{document}

### 2020-11-23 blueprint.tex
Updates blueprint

--- 2020-11-16 algebra.tex
@@
 
-\usepackage{amscd, amssymb, mathtools, amsthm, amsmath}
+\usepackage{amscd, amssymb, mathtools, amsthm, amsmath, mathrsfs}
 \usepackage{enumerate}
@@
 
+Let $R$ be a commutative ring.
+
+\begin{definition}[ideal]
+	An ideal $\mathfrak{a}$ of $R$ is a subset of $R$ which is an additive subgroup such that $R\mathfrak{a} = \mathfrak{a}$.
+\end{definition}
+
+\begin{ex}
+	Prove that $\lbrace 0 \rbrace$ and $R$ are ideals of $R$.
+\end{ex}
+
+\begin{ex}
+	Let $\mathfrak{a}$ and $\mathfrak{b}$ be two ideals of $R$. Check that $\mathfrak{a} \mathfrak{b}$ is also an ideal of $R$.
+\end{ex}
+
+\begin{definition}[zero divisor]
+	Two elements $x$ and $y$ of $R$ are zero divisors if $x \neq 0$, $y \neq 0$ and $x y = 0$.
+\end{definition}
+
+\begin{definition}[entire ring]
+	The ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
+\end{definition}
+
+\begin{definition}[prime ideal]
+	A prime ideal $\mathfrak{p}$ of $R$ is an ideal $\mathfrak{p} \neq R$ such that $R/\mathfrak{p}$ is an entire ring. 	
+\end{definition}
+
+\begin{ex}
+	Equivalently, a prime ideal is an ideal $\mathfrak{p} \neq R$ such that $x y \in \mathfrak{p}$ implies $x \in \mathfrak{p}$ or $y \in \mathfrak{p}$ for every elements $x$ and $y$ in $R$.
+\end{ex}
+
+\begin{remark}
+	In a formal setting it is probably better to use the characterization above as the definition of prime ideals.
+\end{remark}
+
+\begin{notation}
+	If $\mathfrak{i}$ is an ideal of $R$, $V(\mathfrak{a})$ denotes the set of all prime ideals of $R$ which contain $\mathfrak{a}$. 
+\end{notation}
+
+\begin{remark}
+	On has $V(R) = \emptyset$ and $V(\lbrace 0 \rbrace)$ is the set of all prime ideals of $R$.
+\end{remark}
+
+\begin{ex}
+Prove the equality $V(\mathfrak{a} \mathfrak{b}) = V(\mathfrak{a}) \cup V(\mathfrak{b})$.	
+\end{ex}
+
+\begin{ex}
+	Prove the equality $V(\sum \mathfrak{a}_i) = \bigcap V(\mathfrak{a}_i)$ for any familly of prime ideals.
+\end{ex}
+
+\begin{ex}
+	Prove the subsets of the form $V(\mathfrak{a})$ as the closed subsets define a topology on the set of all primes ideals of $R$. 
+\end{ex}
+
+\begin{notation}
+	Spec $R$ will denote the topological space of all prime ideals of $R$.
+\end{notation}
+
+\begin{definition}[presheaf of rings]
+	Let $X$ be a topological space. A presheaf $\mathscr{F}$ of rings on $X$ consists of the following data:
+	\begin{itemize}
+		\item for every open set $U$, a ring $\mathscr{F}(U)$
+		\item for every inclusion $V \subseteq U$ of open subsets, a morphism of rings $\rho_{UV}: \mathscr{F}(U) \rightarrow \mathscr{F}(V)$  
+	\end{itemize}
+satisfying 
+	\begin{enumerate}
+		\item $\mathscr{F}(\emptyset) = \lbrace 0 \rbrace$
+		\item $\rho_{UU}$ is the identity map for every open subset $U$
+		\item  If $W \subseteq V \subseteq U$ are three open subsets, then $\rho_{UW} = \rho_{VW} \circ \rho_{UV}$.
+	\end{enumerate}
+\end{definition}
+
+\begin{notation}
+	The elements of $\mathscr{F}(U)$ are sometimes called the sections of the presheaf $\mathscr{F}$ and given $s \in \mathscr{F}(U)$, $s\restriction V$ denotes the element $\rho_{UV}(s)$.
+\end{notation}
+
+\begin{definition}[sheaf of rings]
+	A sheaf of rings on a topological space $X$ is a presheaf on $X$ that satisfies the following additional properties:
+	\begin{enumerate}
+	\setcounter{enumi}{3}
+		\item Given an open set $U$, $\lbrace V_i \rbrace$ an open covering of $U$ and $s \in \mathscr{F}(U)$ such that $s \restriction V_i = 0$ for all $i$, then one has $s = 0$.
+		\item Given an open set $U$, $\lbrace V_i \rbrace$ an open covering of $U$ and elements $s_i \in \mathscr{F}(V_i)$ for each $i$ satisfying $s_i \restriction V_i \cap V_j = s_j \restriction V_i \cap V_j$ for all $i$ and $j$, then there exists an element $s \in \mathscr{F}(U)$ such that $s \restriction V_i = s_i$ for all $i$.
+	\end{enumerate}	
+\end{definition}
+
+%\begin{definition}[localization of a ring]
+
+%\end{definition}
+
+%\begin{definition}[spectrum of a ring]
+
+%\end{definition}
+
+\begin{appendices}
+	\addappheadtotoc
+
+\chapter{Commutative Algebra}
+\label{chap:commalg}
+
+\section{Fields}
+\label{sec:fields}
+
+\end{appendices}
+
 \end{document}

### 2020-11-24 blueprint.tex
Updates blueprint

@@
 \title{Blueprint}
-\author{}
+\author{Anthony Bordg}
 \date{\today}
@@
 
-Let $R$ be a commutative ring.
+\begin{definition}[zero divisor]
+	Two elements $x$ and $y$ of a ring are zero divisors if $x \neq 0$, $y \neq 0$ and $x y = 0$.
+\end{definition}
+
+\begin{definition}[entire ring]
+	A ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
+\end{definition}
+
+Let $R$ be an entire ring.
 
@@
 
-\begin{definition}[zero divisor]
-	Two elements $x$ and $y$ of $R$ are zero divisors if $x \neq 0$, $y \neq 0$ and $x y = 0$.
-\end{definition}
-
-\begin{definition}[entire ring]
-	The ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
-\end{definition}
-
 \begin{definition}[prime ideal]
@@
 \end{remark}
+
+\begin{remark}
+	If $\mathfrak{p}$ is a prime ideal, then $1 \notin \mathfrak{p}$.
+\end{remark}
+
+\begin{ex}
+	Let $\mathfrak{p}$ be a prime ideal and $S$ be the complement of $\mathfrak{p}$ in $R$. Prove $S$ is a multiplicative submonoid of $R$. 
+\end{ex}
 
@@
 
-%\begin{definition}[localization of a ring]
+\begin{cons}
+	Let $S$ be a multiplicative submonoid of $R$. We consider pairs $(r, s)$ with $r \in R$ and $s \in S$ and we define the following relation on them
+	\[
+	(r, s) \sim (r', s')
+	\]
+	if and only if there exists $s_1 \in S$ such that $s_1(s' r - s r') = 0$.
+One checks that the relation $\sim$ is an equivalence relation.
+The equivalence class of a pair $(r, s)$ is denoted by $r/s$ and the set of equivalence classes is denoted by $S^{-1} R$.
+We define the following addition on $S^{-1} R$.
+	\[
+	\frac{r}{s} + \frac{r'}{s'} = \frac{r s' + r' s}{s s'}
+	\]
+	We also define the following multiplication on $S^{-1} R$. 
+	\[
+	\frac{r}{s} \times \frac{r'}{s'} = \frac{r r'}{s s'}
+	\]
+\end{cons}
 
-%\end{definition}
+\begin{ex}
+	Prove $(S^{-1} R, 0/1, +, 1/1, \times)$ is a ring.
+\end{ex}
 
-%\begin{definition}[spectrum of a ring]
+\begin{definition}[quotient ring]
+	Let $S$ be a multiplicative submonoid of $R$. The quotient ring of $R$ by $S$ is $S^{-1} R$. 
+\end{definition}
 
-%\end{definition}
+\begin{definition}[local ring]
+Let $\mathfrak{p}$ be a prime ideal of $R$ and $S$ the complement of $\mathfrak{p}$ in $R$. The local ring of $R$ at $\mathfrak{p}$, denoted $R_{\mathfrak{p}}$, is $S^{-1} R$. 	
+\end{definition}
+
+\begin{cons}
+	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}(U)$ to be the set of all functions 
+	\[
+	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
+	\]
+	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$.
+\end{cons}
+
+\begin{ex}
+	Prove $\mathscr{O}$ is a sheaf of rings on Spec $R$. 
+\end{ex}
+
+\begin{definition}[spectrum of a ring]
+	The spectrum of the ring $R$ is the pair consisting of the topological space $Spec R$ together with the sheaf of rings $\mathscr{O}$.
+\end{definition}
 

### 2020-11-24 blueprint.tex
Updates blueprint

@@
 The equivalence class of a pair $(r, s)$ is denoted by $r/s$ and the set of equivalence classes is denoted by $S^{-1} R$.
+\\
 	We define the following addition on $S^{-1} R$.
@@
 	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$.
+\\
+	We endow $\mathscr{O}(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$.
+\\
+	Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}(U) \rightarrow \mathscr{O}(V)$ maps each $s \in \mathscr{O}(u)$ on its restriction $s \restriction V$. 
 \end{cons}

### 2020-11-25 blueprint.tex
Updates blueprint

@@
-\documentclass[12pt]{report}
+\documentclass[12pt]{article}
 
@@
 
-\title{Blueprint}
+\title{What is a Scheme in Algebraic Geometry?}
 \author{Anthony Bordg}
@@
 \maketitle
+
+\begin{abstract}
+% To be completed	
+\end{abstract}
 
@@
 
+\begin{definition}[morphism of presheaves of rings]
+	A morphism $\phi: \mathscr{F} \rightarrow \mathscr{F}'$ of sheaves of rings on a topological space $X$ is given by a morphism $\phi_U: \mathscr{F}(U) \rightarrow \mathscr{F}'(U)$ for each open subset $U$ of $X$ such that  the following diagram commutes
+	\[
+	\begin{tikzcd}
+	\mathscr{F}(U) \arrow[r, "\phi_U"] \arrow[d, "\rho_{UV}"] & \mathscr{F}'(U) \arrow[d, "\rho'_{UV}"] \\
+	\mathscr{F}(V) \arrow[r, "\phi_V"] & \mathscr{F}'(V) 
+	\end{tikzcd}
+	\]
+	for every inclusion $V \subseteq U$. \\
+	An isomorphism of presheaves is a morphism which has a two-sided inverse.
+\end{definition}
+
 \begin{definition}[sheaf of rings]
@@
 	\end{enumerate}	
+\end{definition}
+
+\begin{definition}[morphism of sheaves of rings]
+	A morphism of sheaves of rings is a morphism of presheaves of rings.
+\end{definition}
+
+\begin{cons}
+	Let $f: X \rightarrow Y$ be a continuous map between topological spaces and $\mathscr{F}$ a sheaf of rings on $X$.
+Given an open subset $V$ of $Y$, define $(f_{*} \mathscr{F})(V)$ to be $\mathscr{F} (f^{-1}(Y))$.
+\end{cons}
+
+\begin{ex}
+	Prove $f_{*} \mathscr{F}$ above is a sheaf of rings on the topological space $Y$.  
+\end{ex}
+
+\begin{definition}[direct image sheaf]
+	Let $f: X \rightarrow Y$ be a continuous map between topological spaces and $\mathscr{F}$ a sheaf of rings on $X$. The sheaf $f_{*} \mathscr{F}$ is the direct image of $\mathscr{F}$. 
 \end{definition}
@@
 
+\begin{definition}[ringed space]
+	A ringed space is a pair $(X, \mathscr{O}(X))$, where $X$ is a topological space and $\mathscr{O}(X)$ is a sheaf of rings on $X$.
+\end{definition}
+
+\begin{definition}[morphism of ringed spaces]
+	A morphism of ringed spaces from $(X, \mathscr{O}(X))$ to $(Y, \mathscr{O}(Y))$ is a pair $(f, f^{\sharp})$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $f^{\sharp}: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.
+\end{definition}
+
+\begin{definition}[locally ringed space]
+
+\end{definition}
+
+\begin{ex}
+	Prove $(Spec R, \mathscr{O})$ is a locally ringed space.
+\end{ex}
+
+\begin{definition}[morphism of locally ringed spaces]
+
+\end{definition}
+
+\begin{definition}[affine scheme]
+	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O})$ for some ring $R$. 
+\end{definition}
+
+\begin{definition}[scheme]
+
+\end{definition}
+
 \begin{appendices}
@@
 
-\chapter{Commutative Algebra}
-\label{chap:commalg}
+\section{Solutions of exercises}
 
-\section{Fields}
-\label{sec:fields}
+% To be completed
+
+%\section{Commutative Algebra}
+%\label{chap:commalg}
+
+%\subsection{Fields}
+%\label{sec:fields}
 

### 2020-11-25 blueprint.tex
Updates blueprint

@@
 \begin{definition}[entire ring]
-	A ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
+	A ring $R$ is said to be entire if it is commutative, $1 \neq 0$ and there are no zero divisors in $R$. 
 \end{definition}
@@
 \begin{notation}
-	If $\mathfrak{i}$ is an ideal of $R$, $V(\mathfrak{a})$ denotes the set of all prime ideals of $R$ which contain $\mathfrak{a}$. 
+	If $\mathfrak{a}$ is an ideal of $R$, $V(\mathfrak{a})$ denotes the set of all prime ideals of $R$ which contain $\mathfrak{a}$. 
 \end{notation}
@@
 \begin{ex}
-	Prove the equality $V(\sum \mathfrak{a}_i) = \bigcap V(\mathfrak{a}_i)$ for any familly of prime ideals.
+	Prove the equality $V(\sum \mathfrak{a}_i) = \bigcap V(\mathfrak{a}_i)$ for any family of prime ideals.
 \end{ex}
@@
 \begin{cons}
-	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}(U)$ to be the set of all functions 
+	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}_R(U)$ to be the set of all functions 
 	\[
@@
 \\
-	We endow $\mathscr{O}(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$.
+	We endow $\mathscr{O}_R(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$.
 \\
-	Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}(U) \rightarrow \mathscr{O}(V)$ maps each $s \in \mathscr{O}(u)$ on its restriction $s \restriction V$. 
+	Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_R(U) \rightarrow \mathscr{O}_R(V)$ maps each $s \in \mathscr{O}_R(U)$ on its restriction to $V$. 
 \end{cons}
@@
 \begin{ex}
-	Prove $\mathscr{O}$ is a sheaf of rings on Spec $R$. 
+	Prove $\mathscr{O}_R$ is a sheaf of rings on Spec $R$. 
 \end{ex}
@@
 \begin{definition}[spectrum of a ring]
-	The spectrum of the ring $R$ is the pair consisting of the topological space $Spec R$ together with the sheaf of rings $\mathscr{O}$.
+	The spectrum of the ring $R$ is the pair consisting of the topological space $Spec R$ together with the sheaf of rings $\mathscr{O}_R$.
 \end{definition}
@@
 \begin{definition}[morphism of ringed spaces]
-	A morphism of ringed spaces from $(X, \mathscr{O}(X))$ to $(Y, \mathscr{O}(Y))$ is a pair $(f, f^{\sharp})$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $f^{\sharp}: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.
+	A morphism of ringed spaces from $(X, \mathscr{O}(X))$ to $(Y, \mathscr{O}(Y))$ is a pair $(f, \phi_f)$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $\phi_f: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.
 \end{definition}
@@
 \begin{ex}
-	Prove $(Spec R, \mathscr{O})$ is a locally ringed space.
+	Prove $(Spec R, \mathscr{O}_R)$ is a locally ringed space.
 \end{ex}
@@
 \begin{definition}[affine scheme]
-	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O})$ for some ring $R$. 
+	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O}_R)$ for some ring $R$. 
 \end{definition}

### 2020-11-25 blueprint.tex
Updates blueprint

@@
 
+\begin{ex}
+	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $U$ an open subset of $X$.
+\\ Prove that $\mathscr{F}|_U$, defined by $\mathscr{F}|_U(V) \coloneqq \mathscr{F}(U \cap V)$, is a sheaf of rings on $U$ for the induced topology.
+\end{ex}
+
 \begin{cons}
@@
 
+\begin{construction}
+	Let $X$ be a topological space and $\mathscr{F}$ a sheaf of rings on $X$. The set $I$ will denote a subset of the set of all open subsets of $X$. \\
+	Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we says that 
+	$s \sim t$ if and only if there exists $W \in I$ such that $W \subseteq U \cap V$ and $s \restriction W = t \restriction W$. One checks that $\sim$ is an equivalence relation. \\
+	Now, we consider the quotient of the disjoint union of the $\mathscr{F}(U)$'s.
+	\[
+	\varinjlim \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
+	\]
+	Note that for any two elements $U, V \in I$, one has $[0_U] = [0_V]$ and $[1_U] = [1_V]$, where $[0_U]$ (\textit{resp.} $[1_U]$) denotes the class of the zero element (\textit{resp.} the multiplicative unit) of the ring $\mathscr{F}(U)$.
+\\
+	Last, on each component $\mathscr{F}(U)$ the ring operations of $\varinjlim \mathscr{F}(U)$ are those of $\mathscr{F}(U)$. 
+\end{construction}
+
+\begin{ex}
+	Prove $(\varinjlim \mathscr{F}(U), 0, +, 1, \times)$ is a ring. 
+\end{ex}
+
+\begin{definition}[direct limit]
+	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $I$ a set of open subsets of $X$. The direct limit over $I$ is the ring $\varinjlim \mathscr{F}(U)$.
+\end{definition}
+
+\begin{definition}[stalks of a presheaf]
+	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $x$ an element of $X$. \\
+	The stalk $\mathscr{F}_x$ of $\mathscr{F}$ at $x$ is the direct limit over the set of all the open neighborhoods of $x$.   
+\end{definition}
+
 \begin{definition}[locally ringed space]
-
+	A locally ringed space is a ringed space $(X, \mathscr{O}_X)$ such that the stalk $(\mathscr{O}_X)_x$ is a local ring for every $x \in X$.
 \end{definition}
@@
 \begin{definition}[scheme]
-
+	A scheme is a locally ringed space $(X, \mathscr{O}_X)$ in which every point has an open neighborhood $U$ such that the topological space $U$, together with the sheaf $\mathscr{O}_X | _U$, is an affine scheme.
 \end{definition}

### 2020-11-26 blueprint.tex
updates blueprint

@@
 
-\title{What is a Scheme in Algebraic Geometry?}
+\title{Blueprint}	
+%\title{What is a Scheme in Algebraic Geometry?}
 \author{Anthony Bordg}
@@
 
-\begin{definition}[local ring]
+\begin{definition}[local ring at a prime ideal] \label{localringat}
 	Let $\mathfrak{p}$ be a prime ideal of $R$ and $S$ the complement of $\mathfrak{p}$ in $R$. The local ring of $R$ at $\mathfrak{p}$, denoted $R_{\mathfrak{p}}$, is $S^{-1} R$. 
@@
 
+\begin{definition}[maximal ideal]
+	Let $\mathfrak{m}$ be an ideal of $R$. The ideal $\mathfrak{m}$ is maximal if $\mathfrak{m} \neq R$ and there is no ideal $\mathfrak{a} \neq R$ such that $\mathfrak{m} \subset \mathfrak{a}$.
+\end{definition}
+
+\begin{definition}[local ring]
+	A ring is a local ring if it is commutative and it has a unique maximal ideal. 	
+\end{definition}
+
+\begin{ex}
+	Prove $R_{\mathfrak{p}}$ \ref{localringat} is a local ring.
+\end{ex}
+
+\begin{definition}[local homomorphism]
+	Let $A$ and $B$ be two local rings and $\mathfrak{m}_A$, $\mathfrak{m}_B$ their respective maximal ideals. \\
+	A local homomorphism $f: A \rightarrow B$ is a morphism of rings such that $f^{-1} (\mathfrak{m}_B) = \mathfrak{m}_A$. 
+\end{definition}
+
 \begin{definition}[locally ringed space]
@@
 
+\begin{cons}
+
+\end{cons}
+
 \begin{definition}[morphism of locally ringed spaces]
-
+	A morphism of locally ringed spaces from $(X, \mathscr{O}_X)$ to $(Y, \mathscr{O}_Y)$ is a morphism $(f, \phi_f)$ between ringed spaces such that the induced map of local rings $\phi_{f, x}: (\mathscr{O}_Y)_{f(x)} \rightarrow (\mathscr{O}_X)_x$ is a local homomorphism for every $x \in X$.
 \end{definition}
@@
 \begin{definition}[affine scheme]
-	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O}_R)$ for some ring $R$. 
+	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(Spec R, \mathscr{O}_R)$ for some ring $R$. 
 \end{definition}

### 2020-11-26 blueprint.tex
Updates blueprint

@@
 \title{Blueprint}
-%\title{What is a Scheme in Algebraic Geometry?}
 \author{Anthony Bordg}
@@
 \maketitle
-
-\begin{abstract}
-% To be completed	
-\end{abstract}
 
@@
 	\[
-	\varinjlim \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
+	\varinjlim_I \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
 	\]
@@
 \\
-	Last, on each component $\mathscr{F}(U)$ the ring operations of $\varinjlim \mathscr{F}(U)$ are those of $\mathscr{F}(U)$. 
+	Last, on each component $\mathscr{F}(U)$ the ring operations of $\displaystyle \varinjlim_{I} \mathscr{F}(U)$ are those of $\mathscr{F}(U)$. 
 \end{construction}
@@
 \begin{ex}
-	Prove $(\varinjlim \mathscr{F}(U), 0, +, 1, \times)$ is a ring. 
+	Prove $(\displaystyle \varinjlim_I \mathscr{F}(U), 0, +, 1, \times)$ is a ring. 
 \end{ex}
@@
 \begin{definition}[direct limit]
-	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $I$ a set of open subsets of $X$. The direct limit over $I$ is the ring $\varinjlim \mathscr{F}(U)$.
+	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $I$ a set of open subsets of $X$.
+The direct limit over $I$ is the ring $\displaystyle \varinjlim_I \mathscr{F}(U)$ or simply $\varinjlim \mathscr{F}(U)$.
 \end{definition}
@@
 \begin{cons}
-
+	Let $(X, \mathscr{O}_X)$, $(Y, \mathscr{O}_Y)$ be two ringed spaces and $(f, \phi_f)$ a morphism between them. Given $x \in X$, consider 
+	\[
+	I \coloneqq \lbrace V \mid V \, \text{is an open neighborhhood of}\, f(x) \rbrace .
+	\]
+	Since we have a morphism $\phi_f: \mathscr{O}_Y \rightarrow f_* \mathscr{O}_X $ of sheaves on $Y$, we get a map between the direct limits over $I$. 
+	\[
+	(\mathscr{O}_Y)_{f(x)} \rightarrow \displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)
+	\]
+	Last, there is a natural inclusion from $\displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)$ to $(\mathscr{O}_X)_x$, so eventually we get an induced morphism of rings from $(\mathscr{O}_Y)_{f(x)}$ to $(\mathscr{O}_X)_x$ which we will denote $\phi_{f, x}$.
 \end{cons}

### 2020-11-30 blueprint.tex
Updates blueprint

@@
 
-Let $k$ be an algebraically closed field and $A$ denote the ring $k \left[ x_1, \dots, x_n \right]$. \\
-
-\begin{definition}[affine $n$-space] 
-	The affine $n$-space over $k$, denoted $\mathbb{A}^n_k$ or simply $\mathbb{A}^n$, is the set of all $n$-tuples of elements of $k$.  
-\end{definition}
-
-\begin{remark}
-	An element $P$ of $\mathbb{A}^n$ will be called a point. \\
-	If $P = (a_1, \dots, a_n)$ with $a_i \in k$, then $a_i$ will be called the $i$th coordinate of $P$.
-\end{remark}
-
-\begin{notation}
-	if $P = (a_1, \dots, a_n)$ (\textit{resp.} $f$) belongs to $\mathbb{A}^n$ (\textit{resp.} $A$), then $f(P)$ is $f(a_1, \dots, a_n)$.
-\end{notation}
-
-\begin{definition}[zero set]
-	If $T$ is any subset of $A$, one defines the zero set of $T$, denoted $Z(T)$, to be the common zeros of all the elements of $T$. \\
-	In other words one has
-	\[
-	Z(T) \coloneqq \lbrace P \in \mathbb{A}^n \mid f(P) = 0 \quad \text{for all}\, f \in T \rbrace \, . 
-	\]
-\end{definition}
-
-\begin{definition}[algebraic set]
-	A subset $Y$ of $\mathbb{A}^n$ is an algebraic set if there exists a subset $T \subseteq A$ such that $Y = Z(T)$. 
-\end{definition}
-
-\begin{ex}
-	Prove the empty space $\emptyset$ and the whole space $\mathbb{A}^n$ are algebraic sets.
-\end{ex}
-
-\begin{ex}
-	Prove the intersection of any family of algebraic sets is an algebraic set.
-\end{ex}
-
-\begin{ex}
-	Prove the union of two algebraic sets is an algebraic set.
-\end{ex}
-
-\begin{definition}[Zariski topology]
-	One defines the Zariski topology on $\mathbb{A}^n$ by taking the open sets to be the complements of the algebraic sets.
-\end{definition}
-
-\begin{ex}
-	Prove the Zariski topology is a topology. 
-\end{ex}
-
-\begin{definition}[irreducible subset]
-	A nonempty subset $Y$ of a topological space $X$ is irreducible if $Y$ cannot be expressed as the union of two proper closed subsets of $X$. 
-\end{definition}
-
-\begin{definition}[affine algebraic variety]
-	An affine algebraic variety or simply an affine variety is an irreducible closed subset of $\mathbb{A}^n$ endowed with the induced topology. 
-\end{definition}
-
-\begin{definition}[quasi-affine variety]
-	A quasi-affine variety is an open subset of an affine variety. 
-\end{definition}
-
 \begin{definition}[zero divisor]
@@
 
-Let $R$ be an entire ring.
+For the remainder of this text fix an entire ring $R$.
 
@@
 \begin{ex}
+Let $\mathfrak{a}$ and $\mathfrak{b}$ be two ideals of $R$. One defines $\mathfrak{a} \mathfrak{b}$ to be the set \[
+\lbrace a_1 b_1 + \dots + a_n b_n \mid a_i \in \mathfrak{a}, b_i \in \mathfrak{b}, n \in \mathbb{N} \rbrace.
+\]
+Check that $\mathfrak{a} \mathfrak{b}$ is an ideal of $R$.
+\end{ex}
+
+\begin{ex}
 Prove the equality $V(\mathfrak{a} \mathfrak{b}) = V(\mathfrak{a}) \cup V(\mathfrak{b})$.	
+\end{ex}
+
+\begin{ex}
+	Let $\lbrace \mathfrak{a}_i \rbrace$ be a family of ideals of $R$ indexed by a set $I$. One defines the set $\sum \mathfrak{a}_i$ to be the set 
+	\[
+	\lbrace \sum_{i \in I} a_i \mid a_i \in \mathfrak{a}_i \rbrace .
+	\]
+	Check that $\sum \mathfrak{a}_i$ is an ideal of $R$.  
 \end{ex}
@@
 
-%\section{Commutative Algebra}
-%\label{chap:commalg}
-
-%\subsection{Fields}
-%\label{sec:fields}
-
 \end{appendices}

### 2020-12-23 article.tex
Add files via upload
First draft.
- Snippets of code or sreenshots are missing, but their places are indiquated as comments in the source code.
- English should be checked.

\documentclass[12pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}

\usepackage{amscd, amssymb, mathtools, amsthm, amsmath, mathrsfs}
\usepackage{enumerate}

% Palatino for main text and math
\usepackage[osf,sc]{mathpazo}

% Helvetica for sans serif
% (scaled to match size of Palatino)
\usepackage[scaled=0.90]{helvet}

% Bera Mono for monospaced
% (scaled to match size of Palatino)
\usepackage[scaled=0.85]{beramono}

\usepackage{hyperref}

% To write appendixes
\usepackage[page]{appendix}

\renewcommand{\thesubsection}{\arabic{subsection}}
%
%
\newenvironment{eq}{\begin{equation}}{\end{equation}}
%
\newenvironment{remarks}{{\bf Remarks}:\begin{enumerate}}{\end{enumerate}}
\newenvironment{examples}{{\bf Examples}:\begin{enumerate}}{\end{enumerate}}  
%
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}[proposition]{Lemma}
\newtheorem{definition}[proposition]{Definition}
\newtheorem{theorem}[proposition]{Theorem}
\newtheorem{cor}[proposition]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{pretheorem}[proposition]{Pretheorem}
\newtheorem{hypothesis}[proposition]{Hypothesis}
\newtheorem{example}[proposition]{Example}
\newtheorem*{rem}{Remark}
\newtheorem{remark}[proposition]{Remark}
\newtheorem{ex}[proposition]{Exercise}
\newtheorem*{hint}{Hint}
\newtheorem{cond}[proposition]{Conditions}
\newtheorem{cons}[proposition]{Construction}
%
\newtheorem{problem}[proposition]{Problem}
\newtheorem{construction}[proposition]{Construction}
%
\newtheorem*{nota}{Notation}
\newtheorem{notation}{Notation}
\newtheorem*{axiom}{Axiom}

% For diagrams:
\usepackage{tikz-cd}
\usetikzlibrary{cd}

% To avoid automatic identation of paragraphs:
\usepackage[parfill]{parskip}

% To create an index:
\usepackage{makeidx}

% To make the index and bibliography appear in the table of contents:
\usepackage[nottoc]{tocbibind}

\makeindex

\begin{document}

\title{Simple Type Theory is not too Simple}
\subtitle{Grothendieck's Schemes in the Proof Assistant Isabelle}
\author{}
\date{\today}
\maketitle

\begin{abstract}
 	We report on a formalization of Grothendieck's schemes in the proof assistant Isabelle and we discuss in the process the design choices made. Schemes being sophisticated mathematical objects in algebraic geometry introduced by the mathematician Alexander Grothendieck in 1960, this experiment shows that the simple type theory implemented in Isabelle can easily handle such sophisticated objects despite doubts raised about Isabelle capability in that direction.   
\end{abstract}

\section{Motivation and Problems}
\label{sec:intro}

It is well-known in the Isabelle community that the algebra library should be rebuilt from scratch. First, I should say the algebra libraries. Indeed, there are many libraries for algebra in Isabelle, the \textit{HOL-Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Algebra/index.html}} started in the previous millennium (1999), the more recent \textit{HOL-Computational\_Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Computational_Algebra/index.html}}, the oldest formalization of algebraic structures (groups, rings, modules, fields, vector spaces \dots) being found in the main library \textit{HOL}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/index.html}}, and this is in addition to some entries in the Archive of Formal Proofs\footnote{https://www.isa-afp.org/} like \textit{Groups, Rings and Modules} \cite{Group-Ring-Module-AFP} and \textit{Vector Spaces} \cite{VectorSpace-AFP} to cite a few. As a result, there is an important amount of duplicated code and it makes the situation unclear regarding the status of algebra for the newcomer in the Isabelle world. Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the powerful locales, a module system in Isabelle for managing theory hierarchies \cite{ballarin2014}. A successful experiment was conducted recently in \cite{ballarin20} showing that locales allow for a smooth handling of basic algebraic structures in Isabelle. So, hopefully, the situation should improved in the near future. \\
In the same time, some proof assistants have made impressive progress on the algebra front. Indeed, in 2003 Laurent Chicli formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}. More recently, in 2019 Grothendieck's schemes have been formalized by the mathematician Kevin Buzzard and three students using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}}. \\
For the reader unfamiliar with schemes I will quote Kevin Buzzard.
\begin{quote}
	Schemes are the fundamental objects of study in algebraic geometry. They were discovered (in their current form) by Grothendieck in the late 1950s and early 1960s and they revolutionised the theory of algebraic geometry.\footnote{\url{https://github.com/leanprover-community/mathlib/issues/26}} 
\end{quote}
and
\begin{quote}
	A scheme is a mathematical object whose definition and basic properties are usually taught at MSc or early PhD level in a typical mathematics department.
\end{quote}	
Kevin Buzzard in 2017 proposed the formalization of schemes 
\begin{quote}
	as basically a challenge to see if Lean can handle such a complex definition.\footnote{\url{https://github.com/leanprover-community/mathlib/issues/26}} 
\end{quote}
We should note that the Isabelle proof assistant is based on a much more minimalist type theory, known as a simple type theory. As a consequence, many users of dependent type theories see Isabelle's type theory has a far less expressive system for formalizing advanced mathematics.  These doubts have been vocally expressed by Kevin Buzzard on his blog:
\begin{quote}
	What can Isabelle/HOL actually do before it breaks? Nobody knows. [\dots] But do you people want to attract “working mathematicians”? Then where are the schemes? Can your system even do schemes? I don’t know. Does anyone know? If it cannot then this would be very valuable to know because it will help mathematician early adopters to make an informed decision about which system to use.\footnote{\url{https://xenaproject.wordpress.com/2020/02/09/where-is-the-fashionable-mathematics/}}
\end{quote}
In this article we present a concise and elegant formalization of schemes in Isabelle/HOL following the classic graduate textbook of Hartshorne \cite{hartshorne}.

\section{Schemes in Isabelle/HOL}
\label{sec:schemes}

For the remainder of this text fix a commutative ring $R$. \\
The definition of an ideal of $R$ was introduced in Isabelle in \cite{ballarin20}.

\begin{definition}[ideal]
	An ideal $\mathfrak{a}$ of $R$ is a subset of $R$ which is an additive subgroup such that $R\mathfrak{a} = \mathfrak{a}$.
\end{definition}

% Snippet of code to be inserted

One easily checks that $\lbrace 0 \rbrace$ and $R$ are ideals of $R$. In our formalization this translates as follows.

% snippet of code to be inserted for `lemma ideal_R_R` and `lemma ideal_0_R`

% ajouter une remarque ici pour expliquer pourquoi `lemma ideal_R_R` should be named `lemma ideal_ring_ring` instead, cf discussion ta remarque a ce sujet https://isabelle.zulipchat.com/#narrow/stream/234961-alexandria/topic/SEraPIS

Given $\mathfrak{a}$ and $\mathfrak{b}$ be two ideals of $R$, one defines $\mathfrak{a} \mathfrak{b}$ to be the ideal whose underlying set is 
\[
	\lbrace a_1 b_1 + \dots + a_n b_n \mid a_i \in \mathfrak{a}, b_i \in \mathfrak{b}, n \in \mathbb{N} \rbrace.
\]

Actually, $\mathfrak{a} \mathfrak{b}$ is the smallest ideal generated by the set 
	\[
	\lbrace a b \mid a \in \mathfrak{a}, b \in \mathfrak{b} \rbrace
	\]

% snippet of code to be inserted for `ideal_gen_by_prod` ``

and one easily checks it is an ideal.

% snippet of code to be inserted for `ideal_subgroup_generated`

The ideal $\mathfrak{a} \mathfrak{b}$ is in fact the intersection of all ideals of $R$ containing the set
	\[
	\lbrace a b \mid a \in \mathfrak{a}, b \in \mathfrak{b} \rbrace .
	\]

% snippet of code to be inserted for `ideal_gen_by_prod_is_Inter`

Given $\lbrace \mathfrak{a}_i \rbrace$ a family of ideals of $R$ indexed by an arbitrary set $I$, one defines the set $\displaystyle \sum_{i \in I} \mathfrak{a}_i$ to be the set 
	\[
	\lbrace a_1 + \dots + a_n \mid n \in \mathbb{N}, a_i \in \mathfrak{a}_i \rbrace .
	\]

The set $\displaystyle \sum_{i \in I} \mathfrak{a}_i$ is again an ideal of $R$.

% snippet of code to be inserted

The so-called prime ideals are an important class of ideals. A prime ideal $\mathfrak{p}$ of $R$ is an ideal $\mathfrak{p} \neq R$ such that $R/\mathfrak{p}$ is an entire ring. However, in a formal context we prefer the following equivalent definition which is more effective.

\begin{definition}[prime ideal]
	A prime ideal is an ideal $\mathfrak{p} \neq R$ such that $x y \in \mathfrak{p}$ implies $x \in \mathfrak{p}$ or $y \in \mathfrak{p}$ for every elements $x$ and $y$ in $R$.
\end{definition}

% snippet of code to be inserted `locale prime_ideal`

Note that if $\mathfrak{p}$ is a prime ideal, then $1 \notin \mathfrak{p}$.

% snippet of code to be inserted for the proof of this last statement

Let $\mathfrak{p}$ be a prime ideal and $S$ be the complement of $\mathfrak{p}$ in $R$,  we prove $S$ is a multiplicative submonoid of $R$.

% snippet of code to be inserted for this last fact

If $\mathfrak{a}$ is an ideal of $R$, $V(\mathfrak{a})$ will denote the set of all prime ideals of $R$ which contain $\mathfrak{a}$.

% snippet of code to be inserted `definition closed_subsets`

Note that $V(R) = \emptyset$ and $V(\lbrace 0 \rbrace)$ is the set of all prime ideals of $R$.

% snippet of code to be inserted `lemma closed_subsets_empty` and `lemma closed_subsets_R`

%\begin{ex}
%	Prove the equality $V(\mathfrak{a} \mathfrak{b}) = V(\mathfrak{a}) \cup V(\mathfrak{b})$.	
%\end{ex}

%\begin{ex}
%	Prove the equality $\displaystyle V(\sum_{i \in I} \mathfrak{a}_i) = \bigcap_{i \in I} V(\mathfrak{a}_i)$ for any family of prime ideals indexed by a set $I$.
%\end{ex}

Then, one proves in Isabelle the subsets of the form $V(\mathfrak{a})$ as the closed subsets define a topology, the so-called \emph{Zariski topology}\label{zariskitop}, on the set of all primes ideals of $R$. In the rest of this text \emph{Spec $R$} will denote the set of all prime ideals of $R$ equipped with its Zariski topology.

% snippets of code to be inserted here `definition is_zariski_open` and `zariski_is_topological_space`

We now teach Isabelle what \emph{presheaves of rings} are.

\begin{definition}[presheaf of rings]
	Let $X$ be a topological space. A presheaf $\mathscr{F}$ of rings on $X$ consists of the following data:
	\begin{itemize}
		\item for every open set $U$, a ring $\mathscr{F}(U)$
		\item for every inclusion $V \subseteq U$ of open subsets, a morphism of rings $\rho_{UV}: \mathscr{F}(U) \rightarrow \mathscr{F}(V)$  
	\end{itemize}
satisfying 
	\begin{enumerate}
		\item $\mathscr{F}(\emptyset) = \lbrace 0 \rbrace$
		\item $\rho_{UU}$ is the identity map for every open subset $U$
		\item  If $W \subseteq V \subseteq U$ are three open subsets, then $\rho_{UW} = \rho_{VW} \circ \rho_{UV}$.
	\end{enumerate}
\end{definition}

% snippet of code to be inserted `locale presheaf_of_rings`

Given the condition \textit{is\_ring\_morphism} within the locale, notice it is possible to prove that the $\mathscr{F}(U)$'s are rings for every open subset $U$ of the underlying topological space.

% snippet of code to be inserted `is_ring_from_is_homomorphism`

\begin{notation}
	The elements of $\mathscr{F}(U)$ are sometimes called the sections of the presheaf $\mathscr{F}$ and given $s \in \mathscr{F}(U)$, $s\restriction V$ denotes the element $\rho_{UV}(s)$.
\end{notation}

Of course, we have the corresponding notion of morphisms.

\begin{definition}[morphism of presheaves of rings]
	A morphism $\phi: \mathscr{F} \rightarrow \mathscr{F}'$ of sheaves of rings on a topological space $X$ is given by a morphism $\phi_U: \mathscr{F}(U) \rightarrow \mathscr{F}'(U)$ for each open subset $U$ of $X$ such that  the following diagram commutes
	\[
	\begin{tikzcd}
	\mathscr{F}(U) \arrow[r, "\phi_U"] \arrow[d, "\rho_{UV}"] & \mathscr{F}'(U) \arrow[d, "\rho'_{UV}"] \\
	\mathscr{F}(V) \arrow[r, "\phi_V"] & \mathscr{F}'(V) 
	\end{tikzcd}
	\]
	for every inclusion $V \subseteq U$.
\end{definition}

% snippet of code to be inserted `locale morphism_presheaves_of_rings`

The notion of composition between presheaves is straightforward and we check in Isabelle without any difficulty that the composition is again a presheaf of rings. \\
Indeed,	let $\phi: \mathscr{F} \rightarrow \mathscr{G}$ (\textit{resp.} $\psi: \mathscr{G} \rightarrow \mathscr{H}$) be a morphism of presheaves of rings on a topological space $X$. One defines the composition $\psi \circ \phi$ from $\mathscr{F}$ to $\mathscr{H}$ as 
	\[
	(\psi \circ \phi)_U \coloneqq \psi_U \circ \phi_U
	\]
	for every open subset $U$ of $X$. Prove $\psi \circ \phi$ is again a presheaf of rings on $X$.

% snippet of code to be inserted here for the lemma that states the composition is again a presheaf

\begin{remark}
	Given a presheaf $\mathscr{F}$ on $X$, let us define $(1_{\mathscr{F}})_U$ as the identity morphism of $\mathscr{F}(U)$ for every open subset $U$ of $X$. $1_{\mathscr{F}}$ is obviously a morphism of presheaves from $\mathscr{F}$ to itself. A morphism $\phi: \mathscr{F} \rightarrow \mathscr{G}$ of presheaves of rings is an isomorphism if and only if there exists a morphism $\psi: \mathscr{G} \rightarrow \mathscr{F}$ such that $\psi \circ \phi = 1_{\mathscr{F}}$ and $\phi \circ \psi = 1_{\mathscr{G}}$.  
\end{remark}

% snippet of code to be inserted `locale iso_presheaves_of_rings`

Now, we introduce the notion of a \emph{sheaf of rings}.

\begin{definition}[sheaf of rings]
	A sheaf of rings on a topological space $X$ is a presheaf on $X$ that satisfies the following additional properties:
	\begin{enumerate}
	%\setcounter{enumi}{3}
		\item[(locality)] Given an open set $U$, $\lbrace V_i \rbrace$ an open covering of $U$ and $s \in \mathscr{F}(U)$ such that $s \restriction V_i = 0$ for all $i$, then one has $s = 0$.
		\item[(glueing)] Given an open set $U$, $\lbrace V_i \rbrace$ an open covering of $U$ and elements $s_i \in \mathscr{F}(V_i)$ satisfying the property $s_i \restriction V_i \cap V_j = s_j \restriction V_i \cap V_j$ for all $i$ and $j$, then there exists an element $s \in \mathscr{F}(U)$ such that $s \restriction V_i = s_i$ for all $i$.  
	\end{enumerate}	
\end{definition}

% snippet of code to be inserted for `locale sheaf_of_rings`

At this point, let me quote the mathematician Kevin Buzzard:
\begin{quote}
	I am not sure that it is even possible to write this code in Isabelle/HOL in such a way that it will run in finite time, [\dots], and a sheaf is a dependent type, and your clever HOL workarounds will not let you use typeclasses [\dots]\footnote{\url{https://xenaproject.wordpress.com/2020/02/09/where-is-the-fashionable-mathematics/}. See the section entitled \textit{Isabelle/HOL users}.}
\end{quote}

We do not use typeclasses, we do use locales. We encapsulated within the locale dedicated to a preasheaf of rings $\mathscr{F}$ the ring structures on the underlying sets $\mathscr{F}(U)$'s simply using the functional \textit{add\_str} (\textit{resp.} \textit{mult\_str}, \textit{zero\_str}, \textit{one\_str}) that takes an open subset $U$ and outputs the multiplication (\textit{resp.} the addition, the additive unit, the multiplicative unit) on the set $\mathscr{F}(U)$. The resulting formalization of sheaves of rings in Isabelle is not only possible, but it is concise (6 lines), very neat and tidy, almost transparent with respect to the pen-and-paper definition. \\
It will not be any more difficult to define (pre)sheaves valued in any category of structured sets (groups, modules \dots) or even to define in Isabelle a general notion of $\mathscr{C}$-valued (pre)sheaves by embarking the category $\mathscr{C}$ as part of the data within the locale.

A morphism (\textit{resp.} an isomorphism) of sheaves of rings is nothing but a morphism (\textit{resp.} an isomorphism) of presheaves of rings, hence the following locale in Isabelle.

% snippet of code to be inserted `locale morphism_sheaves_of_rings`

Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $U$ an open subset of $X$,  one proves that $\mathscr{F}|_U$, defined by $\mathscr{F}|_U(V) \coloneqq \mathscr{F}(U \cap V)$, is a sheaf of rings on $U$ for the induced topology. \\
We encapsulate the relevant mathematical context (the ``let be'' part) in a dedicated locale and formalize within this locale the relevant definitions and we eventually prove  that the \emph{induced sheaf $\mathscr{F}|_U$} is indeed a sheaf of rings.

% snippet of code to be inserted here `locale cxt_ind_sheaf` and the following definitions and lemma

We introduce a second construction that takes as input a given sheaf of rings and outputs a new sheaf of rings. Let $f: X \rightarrow Y$ be a continuous map between topological spaces and $\mathscr{F}$ a sheaf of rings on $X$. Given an open subset $V$ of $Y$, define $(f_{*} \mathscr{F})(V)$ to be $\mathscr{F} (f^{-1}(V))$. We then prove $f_{*} \mathscr{F}$, the so-called \emph{direct image of  $\mathscr{F}$}, is a sheaf of rings on the topological space $Y$.

% snippet of code to be inserted `locale cxt_direct_im_sheaf`

As can been seen in the snippet of code above, we encapsulate again the context of the construction in a dedicated locale and this lets us formalize the relevant definitions in this context and we eventually prove the direct image of a sheaf is again a sheaf.

Next, we take a detour into the localization of commutative rings. This construction was already formalized by the first author in \cite{bordg18}, but we give a more concise formalization here since the first author gained a better knowledge of the locale mechanism in the meantime. \\
Let $S$ be a multiplicative submonoid of $R$. We consider pairs $(r, s)$ with $r \in R$ and $s \in S$ and we define the following relation on them
	\[
	(r, s) \sim (r', s')
	\]
if and only if there exists $s_1 \in S$ such that $s_1(s' r - s r') = 0$. One checks that the relation $\sim$ is an equivalence relation. The equivalence class of a pair $(r, s)$ is denoted by $r/s$ and the set of equivalence classes is denoted by $S^{-1} R$. \\
We define the following addition on $S^{-1} R$.
	\[
	\frac{r}{s} + \frac{r'}{s'} = \frac{r s' + r' s}{s s'}
	\]
We also define the following multiplication on $S^{-1} R$. 
	\[
	\frac{r}{s} \times \frac{r'}{s'} = \frac{r r'}{s s'}
	\]
One checks $(S^{-1} R, 0/1, +, 1/1, \times)$ is a ring. The new ring $S^{-1} R$ is called the \emph{quotient ring of $R$ by $S$}. \\
This construction translates into the following very legible locale.

% snippet of code to be inserted for `locale cxt_quotient_ring`

Remember that the complement of a prime ideal $\mathfrak{p}$ in $R$ is a multiplicative submonoid, hence we can apply the previous construction with $S \coloneqq R - \mathfrak{p}$. The resulting ring  $S^{-1} R$ is called the \emph{local ring of $R$ at $\mathfrak{p}$}. \\

% snippet of code to be inserted for the subsection <Local Rings at Prime Ideals>

This allows us to introduce the next construction.	\\
Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}_R(U)$ to be the set of all functions 
	\[
	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
	\]
such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$. \\
We endow $\mathscr{O}_R(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$. \\
Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_R(U) \rightarrow \mathscr{O}_R(V)$ maps each $s \in \mathscr{O}_R(U)$ on its restriction to $V$. \\
One checks $\mathscr{O}_R$ is a sheaf of rings on Spec $R$ and the pair $(\text{Spec}\, R, \mathscr{O}_R)$	is called the \emph{spectrum of the ring $R$}. \\
This last construction translates smoothly in Isabelle. 
% snippet of code corresponding to the subsection <Spectrum of a ring> to be inserted here.

Next, we introduce ringed spaces and their morphisms.

\begin{definition}[ringed space]
	A ringed space is a pair $(X, \mathscr{O}_X)$, where $X$ is a topological space and $\mathscr{O}_X$ is a sheaf of rings on $X$.
\end{definition}

% snippet of code `locale ringed_space` to be inserted here.

\begin{definition}[morphism of ringed spaces]
	A morphism of ringed spaces from $(X, \mathscr{O}_X)$ to $(Y, \mathscr{O}_Y)$ is a pair $(f, \phi_f)$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $\phi_f: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.   
\end{definition}

% snippet of code `locale morphism_ringed-spaces` to be inserted here

A classic and ubiquitous notion in mathematics is the \emph{direct limit} of a family of structured sets, here a family of rings. \\
Let $X$ be a topological space and $\mathscr{F}$ a presheaf of rings on $X$. The set $I$ will denote a subset of the set of all open subsets of $X$ such that for every $U$ and $V$ in $I$ there exists $W$ in $I$ with $W \subseteq U \cap V$. \\
Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we says that 
$s \sim t$ if and only if there exists $W \in I$ such that $W \subseteq U \cap V$ and $s \restriction W = t \restriction W$. One checks that $\sim$ is an equivalence relation. \\
Now, we consider the quotient of the disjoint union of the $\mathscr{F}(U)$'s.
	\[
	\varinjlim_I \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
	\]
Last, we define the following binary operations on $\displaystyle \varinjlim_{I} \mathscr{F}(U)$:
	\begin{align*}
	[(U, s)] + [(V, t)] & = [(W, s \restriction W + t \restriction W)] \\
	[(U, s)] \times [(V, t)] & = [(W, s \restriction W \times t \restriction W)]
	\end{align*}
for some $W \in I$ such that $W \subseteq U \cap V$ and where the symbol $[\_]$ denotes the equivalence class of an element. \\
Assuming $I \neq \emptyset$ and $V \in I$, as an exercise one may want to prove that  
	\[
	(\varinjlim_I \mathscr{F}(U), [(V, 0_V)], +, [(V, 1_V)], \times)
	\]
is a ring.

\begin{definition}[direct limit]
	Let $X$ be a topological space, $\mathscr{F}$ a presheaf of rings on $X$ and $I$ a set of open subsets of $X$. The direct limit of $\mathscr{F}$ over $I$ is the ring $\displaystyle \varinjlim_I \mathscr{F}(U)$, denoted simply $\varinjlim \mathscr{F}(U)$ if $I$ is clear from the context.
\end{definition}

The definition above which could naively appear as a dependent type gives raise to a smooth translation in Isabelle using the locale mechanism.

% snippet of code to be inserte here for the subsection <Direct Limits of Rings>

One can instantiate direct limits in the following particular case.

\begin{definition}[stalks of a presheaf]
	Let $X$ be a topological space, $\mathscr{F}$ a presheaf of rings on $X$ and $x$ an element of $X$. \\
	The stalk $\mathscr{F}_x$ of $\mathscr{F}$ at $x$ is the direct limit over the set of all the open neighborhoods of $x$.   
\end{definition}

% snippet of code to be inserted here for subsubsection <Stalks of a Presheaf>

One further step towards schemes consists in introducing local rings, but first one needs to teach Isabelle simple facts about \emph{maximal ideals} starting with their definition.

\begin{definition}[maximal ideal]
	Let $\mathfrak{m}$ be an ideal of $R$. The ideal $\mathfrak{m}$ is maximal if $\mathfrak{m} \neq R$ and there is no ideal $\mathfrak{a} \neq R$ such that $\mathfrak{m} \subset \mathfrak{a}$.
\end{definition}

% snippet of code to be inserted here for `locale max_ideal`

Classic facts about maximal ideals include the fact that every maximal ideal is prime and the fact that given any ideal $\mathfrak{a}$ of $R$ there exists a maximal ideal containing $\mathfrak{a}$.

% snippets of code to be included for the two facts above?

We then introduce the notion of a \emph{local ring}.

\begin{definition}[local ring]
	A ring is a local ring if it is commutative and it has a unique maximal ideal. 	
\end{definition}

% snippet of code to be included here for `locale local_ring`

In particular, we prove as expected that the local ring of $R$ at $\mathfrak{p}$, previously denoted $R_{\mathfrak{p}}$, is a local ring.

% snippet of code to be included for the corresponding lemma.

Local rings have their corresponding notion of morphisms.

\begin{definition}[local homomorphism]
	Let $A$ and $B$ be two local rings and $\mathfrak{m}_A$, $\mathfrak{m}_B$ their respective maximal ideals. \\
	A local homomorphism $f: A \rightarrow B$ is a morphism of rings such that $f^{-1} (\mathfrak{m}_B) = \mathfrak{m}_A$. 
\end{definition}

% snippet of code to be inserted here `locale local_ring_morphism`

Finally, we are able to introduce \emph{locally ringed spaces}.

\begin{definition}[locally ringed space]
	A locally ringed space is a ringed space $(X, \mathscr{O}_X)$ such that the stalk $(\mathscr{O}_X)_x$ is a local ring for every $x \in X$.
\end{definition}

% snippet of code to be introduced here for `locale locally_ringed_space`

Moreover, on has the following result.

\begin{proposition}
	Prove $(Spec R, \mathscr{O}_R)$ is a locally ringed space.
\end{proposition}

% snippet of code to be inserted here for the corresponding lemma in Isabelle

Now, we introduce our last construction. \\
	Let $(X, \mathscr{O}_X)$, $(Y, \mathscr{O}_Y)$ be two ringed spaces and $(f, \phi_f)$ a morphism between them. Given $x \in X$, consider 
	\[
	I \coloneqq \lbrace V \mid V \, \text{is an open neighborhhood of}\, f(x) \rbrace .
	\]
	Since we have a morphism $\phi_f: \mathscr{O}_Y \rightarrow f_* \mathscr{O}_X $ of sheaves on $Y$, we get a map between the direct limits over $I$. 
	\[
	(\mathscr{O}_Y)_{f(x)} \rightarrow \displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)
	\]
	Last, there is a natural inclusion from $\displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)$ to $(\mathscr{O}_X)_x$, so eventually we get an induced morphism of rings from $(\mathscr{O}_Y)_{f(x)}$ to $(\mathscr{O}_X)_x$ which we will denote $\phi_{f, x}$. \\	
As usual we embed this construction into a dedicated locale in Isabelle.

% snippet of code to be inserted here for `locale cxt_ind_morphism_bwt_lim`

This last construction is required to define morphisms between locally ringed spaces.

\begin{definition}[morphism of locally ringed spaces]
	A morphism of locally ringed spaces from $(X, \mathscr{O}_X)$ to $(Y, \mathscr{O}_Y)$ is a morphism $(f, \phi_f)$ between locally ringed spaces such that the induced map of local rings $\phi_{f, x}: (\mathscr{O}_Y)_{f(x)} \rightarrow (\mathscr{O}_X)_x$ is a local homomorphism for every $x \in X$.  
\end{definition}

% snippet of code to be introduced here for `locale morphism_locally_ringed_spaces`

\begin{remark}
	A morphism $(f, \phi_f)$ between locally ringed spaces is an isomorphism if and only if $f$ is an isomorphism between topological spaces, \textit{i.e.} a homeomorphism, and $\phi_f$ is an isomorphism between sheaves of rings.
\end{remark}

% snippet of code to be introduced for `iso_locally_ringed_spaces`

Ultimately, we reach our goal: teaching schemes to Isabelle.

\begin{definition}[affine scheme]
	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(Spec R, \mathscr{O}_R)$ for some commutative ring $R$. 
\end{definition}

% snippet of code to be introduced for `locale affine_scheme`

\begin{definition}[scheme]
	A scheme is a locally ringed space $(X, \mathscr{O}_X)$ in which every point has an open neighborhood $U$ such that the topological space $U$, together with the sheaf $\mathscr{O}_X | _U$, is an affine scheme.
\end{definition}

% snippet of code to be inserted here for `locale schemes`

As sanity checks and to catch on the state of the art in the Lean theorem prover, we prove in Isabelle that an affine scheme is a scheme and we give the example of the empty scheme $(\emptyset, \mathscr{O}_\emptyset)$, where $\mathscr{O}_\emptyset(\emptyset)$ is the zero ring $\lbrace 0 \rbrace$.

% snippets of code to be inserted here for `lemma affine_scheme_is_scheme` and for `empty_scheme_is_affine_scheme`

\section{Concluding Thoughts}

For our formalization we built upon Ballarin's work \cite{ballarin20} formalizing parts of Jacobson's \textit{Basic Algebra} textbook. We believe Ballarin's nice formalization could serve as a first stepping stone to a new algebra library for Isabelle. We also hope the present work could serve as a second stepping stone in that direction. Our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle. 
Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
\begin{quote}
	The project is completely incompatible with modern Lean and mathlib, but if you compile it then you get a sorry-free proof that an affine scheme is a scheme. During our proof we ran into a huge problem because our blueprint, the Stacks Project, assumed that $R[1/f][1/g]=R[1/fg]$, and this turns out to be unprovable for Lean’s version of equality [\dots]. The Lean community wrestled with this idea, and has ultimately come up with a beefed-up notion of equality for which the identity is now true.\footnote{\url{https://xenaproject.wordpress.com/2020/06/05/the-sphere-eversion-project/}}
\end{quote}	
For the first author of the present work, well-versed in dependent type theory, it raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage. Indeed, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants. A dual question is to know how deep one can go formalizing mathematics in a simple type theory. This work provides a first hint at an answer that should not be ruled out: simple type theory is not too simple.

\section*{Acknowledgments}

\begin{thebibliography}{}

	\bibitem{Group-Ring-Module-AFP}
	Kobayashi H., Chen L. and Murao H.:
	\newblock \textit{Groups, Rings and Modules}.
	\newblock Archive of Formal Proofs (2004)

	\bibitem{VectorSpace-AFP}
	Lee H.:
	\newblock \textit{Vector Spaces}.
	\newblock Archive of Formal Proofs (2014)

	\bibitem{ballarin2014}
	Ballarin, C.: 
	\newblock \textit{Locales: A Module System for Mathematical Theories}.
	\newblock J. Autom. Reason. 52, 123–153 (2014)

	\bibitem{ballarin20}
	Ballarin, C.:
	\newblock \textit{Exploring the Structure of an Algebra Text with Locales}. 
	\newblock J. Autom. Reason. 64(6), 1093–1121 (2020)

	\bibitem{chiclithesis}
	Chicli L.:
	\newblock \textit{Sur la formalisation des math\'ematiques dans le Calcul des Constructions Inductives}.
	\newblock doctoral thesis (2003)

	\bibitem{hartshorne}
	Hartshorne, R.:
	\newblock \textit{Algebraic Geometry}.
	\newblock Graduate Texts in Mathematics, Springer (1977)

	\bibitem{bordg18}
	Bordg A.:
	\newblock \textit{The Localization of a Commutative Ring}.
	\newblock Archive of Formal Proofs (2018)

\end{thebibliography}

\end{document}

### 2020-12-23 article.tex
improved introduction

@@
 As a result, there is an important amount of duplicated code and it makes the situation unclear regarding the status of algebra for the newcomer in the Isabelle world.
-Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the powerful locales, a module system in Isabelle for managing theory hierarchies \cite{ballarin2014}.
-A successful experiment was conducted recently in \cite{ballarin20} showing that locales allow for a smooth handling of basic algebraic structures in Isabelle.
-So, hopefully, the situation should improved in the near future.
+Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the modern locales, a powerful module system in Isabelle for managing theory hierarchies \cite{ballarin2014}.
+Therefore, HOL-Algebra contains some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
+Indeed, this last locale uses records and there does not exist multiple inheritances for records, hence the awkward use of the ring record for abelian groups.
+However, a successful experiment was conducted recently in \cite{ballarin20} showing that modern locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
+So, hopefully, the situation should dramatically improved in the near future.
 \\
@@
 \end{quote}
-In this article we present a concise and elegant formalization of schemes in Isabelle/HOL following the classic graduate textbook of Hartshorne \cite{hartshorne}.
+In this article we present a concise and elegant formalization of schemes in Isabelle/HOL based on state-of-the-art locales, without using any record.
+Our presentation follows the classic graduate textbook of Hartshorne \cite{hartshorne}.
 
@@
 
-We do not use typeclasses, we do use locales.
+We do not use old-fashioned typeclasses, we do use modern locales.
 We encapsulated within the locale dedicated to a preasheaf of rings $\mathscr{F}$ the ring structures on the underlying sets $\mathscr{F}(U)$'s simply using the functional \textit{add\_str} (\textit{resp.} \textit{mult\_str}, \textit{zero\_str}, \textit{one\_str}) that takes an open subset $U$ and outputs the multiplication (\textit{resp.} the addition, the additive unit, the multiplicative unit) on the set $\mathscr{F}(U)$.

### 2021-01-07 article.tex
Minor update

@@
  	We report on a formalization of Grothendieck's schemes in the proof assistant Isabelle and we discuss in the process the design choices made.
-Schemes being sophisticated mathematical objects in algebraic geometry introduced by the mathematician Alexander Grothendieck in 1960, this experiment shows that the simple type theory implemented in Isabelle can easily handle such sophisticated objects despite doubts raised about Isabelle capability in that direction.
+Schemes being sophisticated mathematical objects in algebraic geometry introduced by the mathematician Alexander Grothendieck in 1960, this experiment shows that the simple type theory implemented in Isabelle can handle such sophisticated objects despite doubts raised about Isabelle capability in that direction.
 \end{abstract}
@@
 
-% snippet of code to be inserted here for the corresponding lemma in Isabelle
+As a sanity check for our formal definitions, we prove in Isabelle that the spectrum of a commutative ring is indeed a locally ringed space, a result that requires a large amount of formal machinery.
+
+% snippet of code to be inserted here for the corresponding lemma in Isabelle `lemma spec_is_locally_ringed_space`
 
@@
 
+Of course, spectra of commutative rings being locally ringed spaces provide a class of affine schemes.
+
+% snippet of code to be introduced here for `spec_is_affine_scheme`
+
 \begin{definition}[scheme]
@@
 
-As sanity checks and to catch on the state of the art in the Lean theorem prover, we prove in Isabelle that an affine scheme is a scheme and we give the example of the empty scheme $(\emptyset, \mathscr{O}_\emptyset)$, where $\mathscr{O}_\emptyset(\emptyset)$ is the zero ring $\lbrace 0 \rbrace$.
+To catch on the state of the art in the Lean theorem prover, we finally prove in Isabelle that an affine scheme is a scheme and we give the example of the empty scheme $(\emptyset, \mathscr{O}_\emptyset)$, where $\mathscr{O}_\emptyset(\emptyset)$ is the zero ring $\lbrace 0 \rbrace$.
 
@@
 Our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
-Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
+Actually, it seems that our experience in Isabelle to formalize schemes was smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
 \begin{quote}

### 2021-01-08 article.tex
minor update of article

@@
  	We report on a formalization of Grothendieck's schemes in the proof assistant Isabelle and we discuss in the process the design choices made.
-Schemes being sophisticated mathematical objects in algebraic geometry introduced by the mathematician Alexander Grothendieck in 1960, this experiment shows that the simple type theory implemented in Isabelle can handle such sophisticated objects despite doubts raised about Isabelle capability in that direction.
+Schemes being sophisticated mathematical objects in algebraic geometry introduced by the mathematician Alexander Grothendieck in 1960, this experiment shows that the simple type theory implemented in Isabelle can easily handle such sophisticated objects despite doubts raised about Isabelle capability in that direction.
 \end{abstract}
@@
 Our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
-Actually, it seems that our experience in Isabelle to formalize schemes was smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
+Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
 \begin{quote}

### 2021-01-08 article.tex
improve article's conclusion + add one paragraph about the interpretation mechanism
- concluding thoughts now touch upon the new topology library.

@@
 We should note that the Isabelle proof assistant is based on a much more minimalist type theory, known as a simple type theory.
-As a consequence, many users of dependent type theories see Isabelle's type theory has a far less expressive system for formalizing advanced mathematics.
+As a consequence, many users of dependent type theories see Isabelle's type theory as a far less expressive system for formalizing advanced mathematics.
 These doubts have been vocally expressed by Kevin Buzzard on his blog:
@@
 
+The required formal machinery and our formalization as a whole benefit from the interpretation mechanism that allows to keep statements and proof scripts concise.
+Without this mechanism the terms involved in the statements and proof scripts of such an intricate hierarchy of nested algebraic structures would have to be fed with many arguments, cluttering these statements and proof scripts to the point where they would become unreadable and difficult to use.
+Fortunately, the interpretation mechanism that goes along with locales allows for concise and manageable terms with many invisible arguments which are declared beforehand using the interpretation mechanism.
+\\
 Now, we introduce our last construction. \\
@@
 We also hope the present work could serve as a second stepping stone in that direction.
+Also, we seized the opportunity of formalizing schemes to partly rebuild the topology library.
+Our new topology library is entirely built on modern locales instead of using type classes like it is the case in \textit{HOL-Topological\_Spaces.thy}, allowing more abstraction.
+In particular, our topological spaces have explicit carrier sets instead of using \textit{UNIV}.
+\\
 Our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle. 

### 2021-01-12 article.tex
Add one reference and add comments on topological spaces in conclusion

@@
 Indeed, in 2003 Laurent Chicli formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
-More recently, in 2019 Grothendieck's schemes have been formalized by the mathematician Kevin Buzzard and three students using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}}.
+More recently, in 2019 Grothendieck's schemes have been formalized by the mathematician Kevin Buzzard and three students using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
 \\
@@
 Also, we seized the opportunity of formalizing schemes to partly rebuild the topology library.
-Our new topology library is entirely built on modern locales instead of using type classes like it is the case in \textit{HOL-Topological\_Spaces.thy}, allowing more abstraction.
+Our new topology library is entirely built on modern locales instead of using type classes like it is the case in \textit{HOL-Topological\_Spaces.thy}, allowing for more abstraction.
 In particular, our topological spaces have explicit carrier sets instead of using \textit{UNIV}.
+% snippet of code to be included here for `locale topological_space`
+Within the locale for topological spaces the axiom \textit{open\_imp\_subset} enforces that an open is automatically a subset of the ambient space.
+This is a nice addition to the former definition, since it avoids having to add this assumption in every lemma including an open among its assumptions.
+Our library rebuilds basic facts about topological spaces, including for instance the definition of a topology generated by a basis, without using type classes or any deprecated feature of Isabelle.
+% snippets of code to be included here for `inductive generated_topology` and the `lemma generated_topology_is_topology` 
 \\
-Our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle. 
+To summarize, our work makes a triple contribution to Isabelle/HOL: a first stepping stone towards a new topology library, a second stepping stone towards a new algebra library and a formalization of schemes in algebraic geometry.
+In particular, our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
 Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
@@
 
+	\bibitem{schemesinLean}
+	Buzzard K., Hughes C., Lau K., Livingston A., Mir R. and Morrison S.:
+	\newblock \textit{Schemes in Lean}.
+	\newblock arXiv:2101.02602
+
 	\bibitem{hartshorne}

### 2021-01-12 article.tex
Update explanation on the structure sheaf of the spectrum of a ring

@@
 	\[
-	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
+	s: U \rightarrow \coprod \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
 	\]
@@
 \\
-We endow $\mathscr{O}_R(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$.
+We endow $\mathscr{O}_R(U)$ with the sum and product of such functions and we take for the additive unit (\textit{resp.} multiplicative unit) the function that maps each $\mathfrak{p}$ on the additive unit (\textit{resp.} multiplicative unit) of $R_{\mathfrak{p}}$.
 \\

### 2021-01-12 article.tex
Improve some notations and correct an English mistake

@@
 \usepackage[nottoc]{tocbibind}
+
+% notations:
+\def\spec{\text{Spec}\,R}
 
@@
 
-% ajouter une remarque ici pour expliquer pourquoi `lemma ideal_R_R` should be named `lemma ideal_ring_ring` instead, cf discussion ta remarque a ce sujet https://isabelle.zulipchat.com/#narrow/stream/234961-alexandria/topic/SEraPIS
-
 Given $\mathfrak{a}$ and $\mathfrak{b}$ be two ideals of $R$, one defines $\mathfrak{a} \mathfrak{b}$ to be the ideal whose underlying set is 
@@
 
-%\begin{ex}
-%	Prove the equality $V(\mathfrak{a} \mathfrak{b}) = V(\mathfrak{a}) \cup V(\mathfrak{b})$.	
-%\end{ex}
-
-%\begin{ex}
-%	Prove the equality $\displaystyle V(\sum_{i \in I} \mathfrak{a}_i) = \bigcap_{i \in I} V(\mathfrak{a}_i)$ for any family of prime ideals indexed by a set $I$.
-%\end{ex}
-
 Then, one proves in Isabelle the subsets of the form $V(\mathfrak{a})$ as the closed subsets define a topology, the so-called \emph{Zariski topology}\label{zariskitop}, on the set of all primes ideals of $R$.
-In the rest of this text \emph{Spec $R$} will denote the set of all prime ideals of $R$ equipped with its Zariski topology.
+In the rest of this text $\text{Spec}\,R$ will denote the set of all prime ideals of $R$ equipped with its Zariski topology.
 
@@
 This allows us to introduce the next construction.	\\
-Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}_R(U)$ to be the set of all functions 
+Let $U$ be an open subset of $\text{Spec}\,R$. We define $\mathscr{O}_{\spec}(U)$ to be the set of all functions 
 	\[
@@
 \\
-We endow $\mathscr{O}_R(U)$ with the sum and product of such functions and we take for the additive unit (\textit{resp.} multiplicative unit) the function that maps each $\mathfrak{p}$ on the additive unit (\textit{resp.} multiplicative unit) of $R_{\mathfrak{p}}$.
+We endow $\mathscr{O}_{\spec}(U)$ with the sum and product of such functions and we take for the additive unit (\textit{resp.} multiplicative unit) the function that maps each $\mathfrak{p}$ on the additive unit (\textit{resp.} multiplicative unit) of $R_{\mathfrak{p}}$.
 \\
-Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_R(U) \rightarrow \mathscr{O}_R(V)$ maps each $s \in \mathscr{O}_R(U)$ on its restriction to $V$. \\
-One checks $\mathscr{O}_R$ is a sheaf of rings on Spec $R$ and the pair $(\text{Spec}\, R, \mathscr{O}_R)$	is called the \emph{spectrum of the ring $R$}. \\
+Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_{\spec}(U) \rightarrow \mathscr{O}_{\spec}(V)$ maps each $s \in \mathscr{O}_{\spec}(U)$ on its restriction to $V$. \\
+One checks $\mathscr{O}_{\spec}$ is a sheaf of rings on $\text{Spec}\,R$ and the pair $(\text{Spec}\,R, \mathscr{O}_{\spec})$ is called the \emph{spectrum of the ring $R$}. \\
 This last construction translates smoothly in Isabelle.
+
 % snippet of code corresponding to the subsection <Spectrum of a ring> to be inserted here.
@@
 \begin{proposition}
-	Prove $(Spec R, \mathscr{O}_R)$ is a locally ringed space.
+	Prove $(\text{Spec}\,R, \mathscr{O}_{\spec})$ is a locally ringed space.
 \end{proposition}
@@
 Without this mechanism the terms involved in the statements and proof scripts of such an intricate hierarchy of nested algebraic structures would have to be fed with many arguments, cluttering these statements and proof scripts to the point where they would become unreadable and difficult to use.
-Fortunately, the interpretation mechanism that goes along with locales allows for concise and manageable terms with many invisible arguments which are declared beforehand using the interpretation mechanism.
+Fortunately, the interpretation mechanism that comes with locales allows for concise and manageable terms with many invisible arguments which are declared beforehand using the interpretation mechanism.
 \\
@@
 \begin{definition}[affine scheme]
-	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(Spec R, \mathscr{O}_R)$ for some commutative ring $R$. 
+	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(\text{Spec}\,R, \mathscr{O}_{\spec})$ for some commutative ring $R$. 
 \end{definition}

### 2021-01-14 article.tex
Update
- Add an intermediate proposition
- Improve notations
- Catch a typo

@@
 \begin{definition}[locally ringed space]
-	A locally ringed space is a ringed space $(X, \mathscr{O}_X)$ such that the stalk $(\mathscr{O}_X)_x$ is a local ring for every $x \in X$.
+	A locally ringed space is a ringed space $(X, \mathscr{O}_X)$ such that the stalk $\mathscr{O}_{X, x}$ at $x$ is a local ring for every $x \in X$.
 \end{definition}
@@
 
-Moreover, on has the following result.
+Moreover, one has the following results.
 
 \begin{proposition}
-	Prove $(\text{Spec}\,R, \mathscr{O}_{\spec})$ is a locally ringed space.
+	For every $\mathfrak{p} \in \text{Spec}\,R$, the stalk $\mathscr{O}_{\spec, \mathfrak{p}}$ is isomorphic as a ring to $R_{\mathfrak{p}}$.	
 \end{proposition}
 
-As a sanity check for our formal definitions, we prove in Isabelle that the spectrum of a commutative ring is indeed a locally ringed space, a result that requires a large amount of formal machinery.
+% snippet of code to be inserted here for `lemma stalk_at_prime_is_iso_to_local_ring_at_prime`
+
+\begin{cor}
+	$(\text{Spec}\,R, \mathscr{O}_{\spec})$ is a locally ringed space.
+\end{cor}
+
+As a sanity check for our formal definitions, we prove in Isabelle that the spectrum of a commutative ring is indeed a locally ringed space, a result that requires some amount of formal machinery.
 
@@
 	\[
-	(\mathscr{O}_Y)_{f(x)} \rightarrow \displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)
+	\mathscr{O}_{Y, f(x)} \rightarrow \displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)
 	\]
-	Last, there is a natural inclusion from $\displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)$ to $(\mathscr{O}_X)_x$, so eventually we get an induced morphism of rings from $(\mathscr{O}_Y)_{f(x)}$ to $(\mathscr{O}_X)_x$ which we will denote $\phi_{f, x}$.
+	Last, there is a natural inclusion from $\displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)$ to $\mathscr{O}_{X, x}$, so eventually we get an induced morphism of rings from $\mathscr{O}_{Y, f(x)}$ to $\mathscr{O}_{X, x}$ which we will denote $\phi_{f, x}$.
 \\
@@
 \begin{definition}[morphism of locally ringed spaces]
-	A morphism of locally ringed spaces from $(X, \mathscr{O}_X)$ to $(Y, \mathscr{O}_Y)$ is a morphism $(f, \phi_f)$ between locally ringed spaces such that the induced map of local rings $\phi_{f, x}: (\mathscr{O}_Y)_{f(x)} \rightarrow (\mathscr{O}_X)_x$ is a local homomorphism for every $x \in X$.
+	A morphism of locally ringed spaces from $(X, \mathscr{O}_X)$ to $(Y, \mathscr{O}_Y)$ is a morphism $(f, \phi_f)$ between locally ringed spaces such that the induced map of local rings $\phi_{f, x}: \mathscr{O}_{Y, f(x)} \rightarrow \mathscr{O}_{X, x}$ is a local homomorphism for every $x \in X$.
 \end{definition}

### 2021-03-28 article.tex
Updated article

@@
 In the same time, some proof assistants have made impressive progress on the algebra front.
-Indeed, in 2003 Laurent Chicli formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
-More recently, in 2019 Grothendieck's schemes have been formalized by the mathematician Kevin Buzzard and three students using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
+Indeed, in 2003 Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
+More recently, in 2019 Grothendieck's schemes have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
 \\
@@
 
-% Snippet of code to be inserted
+% Snippet of code to be inserted here for `locale ideal` in Jacobson_Basic_Algebra.Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for `lemma ideal_R_R` and `lemma ideal_0_R`
+% snippet of code to be inserted for `lemma ideal_R_R` and `lemma ideal_0_R` of Comm_Ring_Theory.thy
 
-Given $\mathfrak{a}$ and $\mathfrak{b}$ be two ideals of $R$, one defines $\mathfrak{a} \mathfrak{b}$ to be the ideal whose underlying set is 
+Given $\mathfrak{a}$ and $\mathfrak{b}$ two ideals of $R$, one defines $\mathfrak{a} \mathfrak{b}$ to be the ideal whose underlying set is 
 \[
@@
 
-% snippet of code to be inserted for `ideal_gen_by_prod` ``
+% snippet of code to be inserted for `ideal_gen_by_prod` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for `ideal_subgroup_generated`
+% snippet of code to be inserted for `lemma ideal_subgroup_generated` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for `ideal_gen_by_prod_is_Inter`
+% snippet of code to be inserted for `lemma ideal_gen_by_prod_is_Inter`	of Comm_Ring_Theory.thy
 
@@
 The set $\displaystyle \sum_{i \in I} \mathfrak{a}_i$ is again an ideal of $R$.
-
-% snippet of code to be inserted
 
@@
 
-% snippet of code to be inserted `locale prime_ideal`
+% snippet of code to be inserted `locale pr_ideal` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for the proof of this last statement
+% snippet of code to be inserted for the statement and proof of `lemma not_1` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for this last fact
+% snippet of code to be inserted for `lemma submonoid_notin` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `definition closed_subsets`
+% snippet of code to be inserted `definition closed_subsets` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `lemma closed_subsets_empty` and `lemma closed_subsets_R`
+% snippet of code to be inserted for `lemma closed_subsets_empty` and `lemma closed_subsets_R` of Comm_Ring_Theory.thy
 
@@
 
-% snippets of code to be inserted here `definition is_zariski_open` and `zariski_is_topological_space`
+% snippets of code to be inserted here `definition is_zariski_open` and `zariski_is_topological_space` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `locale presheaf_of_rings`
+% snippet of code to be inserted `locale presheaf_of_rings` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `is_ring_from_is_homomorphism`
+% snippet of code to be inserted `is_ring_from_is_homomorphism` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `locale morphism_presheaves_of_rings`
+% snippet of code to be inserted `locale morphism_presheaves_of_rings`  of Comm_Ring_Theory.thy
 
@@
 	\]
-	for every open subset $U$ of $X$. Prove $\psi \circ \phi$ is again a presheaf of rings on $X$.
+	for every open subset $U$ of $X$.
 
-% snippet of code to be inserted here for the lemma that states the composition is again a presheaf
+% snippet of code to be inserted here for the lemma that states the composition is again a presheaf, namely the statement of `lemma comp_of_presheaves` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `locale iso_presheaves_of_rings`
+% snippet of code to be inserted `locale iso_presheaves_of_rings` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for `locale sheaf_of_rings`
+% snippet of code to be inserted for `locale sheaf_of_rings` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted `locale morphism_sheaves_of_rings`
+% snippet of code to be inserted `locale morphism_sheaves_of_rings` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted here `locale cxt_ind_sheaf` and the following definitions and lemma
+% snippet of code to be inserted here `locale ind_sheaf` and the following interpretation and definitions up to `definition ind_one_str` and then the statement of `lemma ind_sheaf_is_sheaf`
 
@@
 
-% snippet of code to be inserted `locale cxt_direct_im_sheaf`
+% snippet of code to be inserted `im_sheaf` of Comm_Ring_Theory.thy plus the following definitions up to `one_im_sheaf` and then the `lemma im_sheaf_is_sheaf` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be inserted for `locale cxt_quotient_ring`
+% snippet of code to be inserted for `locale quotient_ring`	of Comm_Ring_Theory.thy including the definitions `rel`, `frac`, the lemma `add_rel_frac`, `mult_rel_frac`, the definitions `zero_rel`, `one_rel`
+% and the sublocale that proves the quotient ring is a commutative ring.
 
@@
 
-% snippet of code to be inserted for the subsection <Local Rings at Prime Ideals>
+% snippet of code to be inserted for the subsection <Local Rings at Prime Ideals> up to the definition `one_local_ring_at`
 
@@
 
-% snippet of code corresponding to the subsection <Spectrum of a ring> to be inserted here.
+% snippet of code here for the defintions `is_locally_frac`, `is_regular`, `sheaf_spec`, `add_sheaf_spec`, `mult_sheaf_spec`, `zero_sheaf_spec`, `one_sheaf_spec`, `sheaf_spec_morphisms` and finally the statement of `lemma sheaf_spec_is_sheaf`.
 
@@
 
-% snippet of code `locale morphism_ringed-spaces` to be inserted here
+% snippet of code `locale morphism_ringed-spaces` of Comm_Ring_Theory.thy to be inserted here
 
@@
 \\
-Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we says that 
+Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we say that 
 $s \sim t$ if and only if there exists $W \in I$ such that $W \subseteq U \cap V$ and $s \restriction W = t \restriction W$. One checks that $\sim$ is an equivalence relation. \\
@@
 for some $W \in I$ such that $W \subseteq U \cap V$ and where the symbol $[\_]$ denotes the equivalence class of an element. \\
-Assuming $I \neq \emptyset$ and $V \in I$, as an exercise one may want to prove that  
+Assuming $I \neq \emptyset$ and $V \in I$, one can prove that  
 	\[
@@
 
-% snippet of code to be inserte here for the subsection <Direct Limits of Rings>
+% snippet of code to be inserted here for `locale direct_lim` and the definitions `rel`, `add_rel`, `mult_rel` and the statement of `lemma exercise_0_35`
 
@@
 
-% snippet of code to be inserted here for subsubsection <Stalks of a Presheaf>
+% snippet of code to be inserted here for `locale stalk` and the definitions `carrier_stalk`, `add_stalk`, `mult_stalk`, `zero_stalk`, `one_stalk`
 
@@
 
-Classic facts about maximal ideals include the fact that every maximal ideal is prime and the fact that given any ideal $\mathfrak{a}$ of $R$ there exists a maximal ideal containing $\mathfrak{a}$.
+Classic facts about maximal ideals include the fact that every maximal ideal is prime.
 
-% snippets of code to be included for the two facts above?
+% snippet of code to be included for `proposition is_pr_ideal` of Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be included for the corresponding lemma.
+% snippet of code to be included for `lemma local_ring_at_is_local` of Comm_Ring_Theory.thy.
 
@@
 
-% snippet of code to be inserted here for the corresponding lemma in Isabelle `lemma spec_is_locally_ringed_space`
+% snippet of code to be inserted here for the corresponding statement in Isabelle `lemma spec_is_locally_ringed_space`
 
@@
 Without this mechanism the terms involved in the statements and proof scripts of such an intricate hierarchy of nested algebraic structures would have to be fed with many arguments, cluttering these statements and proof scripts to the point where they would become unreadable and difficult to use.
-Fortunately, the interpretation mechanism that comes with locales allows for concise and manageable terms with many invisible arguments which are declared beforehand using the interpretation mechanism.
-\\
+Fortunately, the interpretation mechanism that comes with locales allows for concise and manageable terms with many implicit arguments which are declared beforehand using the interpretation mechanism.
+
 Now, we introduce our last construction. \\
@@
 
-% snippet of code to be inserted here for `locale cxt_ind_morphism_bwt_lim`
+% snippet of code to be inserted here for `locale ind_morphism_bwt_lim`	up to `definition induced_morphism`
 
@@
 
-% snippet of code to be introduced here for `locale morphism_locally_ringed_spaces`
+% snippet of code to be introduced here for `locale morphism_locally_ringed_spaces`, still in Comm_Ring_Theory.thy
 
@@
 
-% snippet of code to be introduced for `locale affine_scheme`
+% snippet of code to be introduced for `locale affine_scheme` in Scheme_Theory.thy
 
@@
 
-% snippet of code to be introduced here for `spec_is_affine_scheme`
+% snippet of code to be introduced here for `lemma spec_is_affine_scheme`
 
@@
 
-% snippet of code to be inserted here for `locale schemes`
+% snippet of code to be inserted here for `locale scheme`
 
@@
 
-% snippets of code to be inserted here for `lemma affine_scheme_is_scheme` and for `empty_scheme_is_affine_scheme`
+% snippets of code to be inserted here for `lemma affine_scheme_is_scheme` and for `empty_scheme_is_scheme`
 
@@
 In particular, our topological spaces have explicit carrier sets instead of using \textit{UNIV}.
-% snippet of code to be included here for `locale topological_space`
+% snippet of code to be included here for `locale topological_space` of Topological_Space_Theory.thy
 Within the locale for topological spaces the axiom \textit{open\_imp\_subset} enforces that an open is automatically a subset of the ambient space.
 This is a nice addition to the former definition, since it avoids having to add this assumption in every lemma including an open among its assumptions.
-Our library rebuilds basic facts about topological spaces, including for instance the definition of a topology generated by a basis, without using type classes or any deprecated feature of Isabelle.
-% snippets of code to be included here for `inductive generated_topology` and the `lemma generated_topology_is_topology` 
+Our library rebuilds basic facts about topological spaces without using type classes or any deprecated feature of Isabelle and it includes among other things material about the topology generated by a basis, covers, the induced topology on a subset and homeomorphisms.
+% snippets of code to be included here for `inductive generated_topology`, `lemma generated_topology_is_topology`  and `locale homeomorphism`
+\\
+The formalized material has a size of roughly 7300-line of code including some prerequisites in commutative  algebra and our partial reconstruction of the topology library.
+Given the output of this work, a formalization of schemes in Isabelle, such a relatively short formalization conveys the power of Isabelle module systems.
 \\
 To summarize, our work makes a triple contribution to Isabelle/HOL: a first stepping stone towards a new topology library, a second stepping stone towards a new algebra library and a formalization of schemes in algebraic geometry.
-In particular, our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
+Most importantly, our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
 Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
@@
 \end{quote}	
-For the first author of the present work, well-versed in dependent type theory, it raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage.
+This raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage.
 Indeed, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
@@
 \section*{Acknowledgments}
+
+Work on this paper was supported by the European Research Council Advanced Grant ALEXANDRIA (Project 742178).
 

### 2021-03-28 article.tex
Updated article

@@
 
+For every $U \in I$, there is a canonical inclusion from $\mathscr{F}(U)$ to $\varinjlim \mathscr{F}(U)$.
+
+% snippet of code to be inserted here for `definition canonical_fun` of Comm_Ring_Theory.thy
+
+The direct limit satisfies a useful universal property.
+Indeed, for every ring $A$ equipped with ring morphisms $\psi_U: \mathscr{F}(U) \rightarrow A$ satisfying $\psi_V \circ \rho_{UV} = \psi_U$ for every inclusion $V \subseteq U$, there exists a unique ring morphism $u$ making the following diagram commutes.
+\[
+\begin{tikzcd}
+\mathscr{F}(U)  \arrow[rr, "\rho_{UV}"] \arrow[rd] \arrow[rdd, bend right, "\psi_U"'] & & \mathscr{F}(V) \arrow[ld]	\arrow[ldd, bend left, "\psi_V"]	\\
+						& \varinjlim \mathscr{F}(U) \arrow[d, "u", dashed] &	\\
+						& A &  
+\end{tikzcd}
+\] 
+The counterpart in Isabelle is as follows.
+
+% snippet of code to be inserted here for `proposition (in direct_lim) universal_property`
+
 One can instantiate direct limits in the following particular case.

### 2021-03-29 article.tex
Added isabelle.sty & inserted some of snippets

@@
 
+\usepackage{isabelle,isabellesym}
+
 \begin{document}
@@
 
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ ideal\ {\isacharequal}{\kern0pt}\ subgroup{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}additive{\isacharunderscore}{\kern0pt}group{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}ring\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ ideal{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymlbrakk}\ a\ {\isasymin}\ R{\isacharsemicolon}{\kern0pt}\ b\ {\isasymin}\ I\ {\isasymrbrakk}\ {\isasymLongrightarrow}\ a\ {\isasymcdot}\ b\ {\isasymin}\ I{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymlbrakk}\ a\ {\isasymin}\ R{\isacharsemicolon}{\kern0pt}\ b\ {\isasymin}\ I\ {\isasymrbrakk}\ {\isasymLongrightarrow}\ b\ {\isasymcdot}\ a\ {\isasymin}\ I{\isachardoublequoteclose}
+\end{isabelle}
+
 One easily checks that $\lbrace 0 \rbrace$ and $R$ are ideals of $R$. In our formalization this translates as follows.
@@
 % snippet of code to be inserted for `lemma ideal_R_R` and `lemma ideal_0_R` of Comm_Ring_Theory.thy
+
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}R{\isacharunderscore}{\kern0pt}R{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}ideal\ R\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}{\isadigit{0}}{\isacharunderscore}{\kern0pt}R{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}ideal\ {\isacharbraceleft}{\kern0pt}{\isasymzero}{\isacharbraceright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 
+\begin{isabelle}
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ {\isasymaa}\ {\isasymbb}\ {\isasymequiv}\ additive{\isachardot}{\kern0pt}subgroup{\isacharunderscore}{\kern0pt}generated\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharbraceleft}{\kern0pt}x{\isachardot}{\kern0pt}\ {\isasymexists}a\ b{\isachardot}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ a\ {\isasymcdot}\ b\ {\isasymand}\ a\ {\isasymin}\ {\isasymaa}\ {\isasymand}\ b\ {\isasymin}\ {\isasymbb}{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
+
 and one easily checks it is an ideal.
@@
 % snippet of code to be inserted for `lemma ideal_subgroup_generated` of Comm_Ring_Theory.thy
+
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}subgroup{\isacharunderscore}{\kern0pt}generated{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}ideal\ {\isasymbb}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ideal\ {\isacharparenleft}{\kern0pt}ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ {\isasymaa}\ {\isasymbb}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted for `lemma ideal_gen_by_prod_is_Inter`	of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}inter{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}ideal\ {\isasymbb}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ {\isasymaa}\ {\isasymbb}\ {\isacharequal}{\kern0pt}\ {\isasymInter}\ {\isacharbraceleft}{\kern0pt}I{\isachardot}{\kern0pt}\ ideal\ I\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharbraceleft}{\kern0pt}a\ {\isasymcdot}\ b\ {\isacharbar}{\kern0pt}a\ b{\isachardot}{\kern0pt}\ a\ {\isasymin}\ {\isasymaa}\ {\isasymand}\ b\ {\isasymin}\ {\isasymbb}{\isacharbraceright}{\kern0pt}\ {\isasymsubseteq}\ I{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted `locale pr_ideal` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ pr{\isacharunderscore}{\kern0pt}ideal\ {\isacharequal}{\kern0pt}\ comm{\isacharcolon}{\kern0pt}comm{\isacharunderscore}{\kern0pt}ring\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ ideal\ I\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{for}\ R\ \isakeyword{and}\ I\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ multiplication\ \isanewline
+\ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ {\isacharplus}{\kern0pt}\ \isakeyword{assumes}\ carrier{\isacharunderscore}{\kern0pt}neq{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}I\ {\isasymnoteq}\ R{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ absorbent{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymlbrakk}x\ {\isasymin}\ R{\isacharsemicolon}{\kern0pt}\ y\ {\isasymin}\ R{\isasymrbrakk}\ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}x\ {\isasymcdot}\ y\ {\isasymin}\ I{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}x\ {\isasymin}\ I\ {\isasymor}\ y\ {\isasymin}\ I{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ not{\isacharunderscore}{\kern0pt}{\isadigit{1}}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymone}\ {\isasymnotin}\ I{\isachardoublequoteclose}\isanewline
+\isacommand{proof}\isamarkupfalse%
+\isanewline
+\ \ \isacommand{assume}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymone}\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
+\ \ \isacommand{then}\isamarkupfalse%
+\ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymAnd}x{\isachardot}{\kern0pt}\ {\isasymlbrakk}{\isasymone}\ {\isasymin}\ I{\isacharsemicolon}{\kern0pt}\ x\ {\isasymin}\ R{\isasymrbrakk}\ {\isasymLongrightarrow}\ x\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}metis\ ideal{\isacharparenleft}{\kern0pt}{\isadigit{1}}{\isacharparenright}{\kern0pt}\ comm{\isachardot}{\kern0pt}multiplicative{\isachardot}{\kern0pt}right{\isacharunderscore}{\kern0pt}unit{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isacommand{with}\isamarkupfalse%
+\ {\isacartoucheopen}{\isasymone}\ {\isasymin}\ I{\isacartoucheclose}\ \isacommand{have}\isamarkupfalse%
+\ {\isachardoublequoteopen}I\ {\isacharequal}{\kern0pt}\ R{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{by}\isamarkupfalse%
+\ auto\isanewline
+\ \ \isacommand{then}\isamarkupfalse%
+\ \isacommand{show}\isamarkupfalse%
+\ False\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ carrier{\isacharunderscore}{\kern0pt}neq\ \isacommand{by}\isamarkupfalse%
+\ blast\isanewline
+\isacommand{qed}
+\end{isabelle}
+
 Let $\mathfrak{p}$ be a prime ideal and $S$ be the complement of $\mathfrak{p}$ in $R$,  we prove $S$ is a multiplicative submonoid of $R$.
@@
 % snippet of code to be inserted for `lemma submonoid_notin` of Comm_Ring_Theory.thy	
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ submonoid{\isacharunderscore}{\kern0pt}notin{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}S\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}x\ {\isasymin}\ R{\isachardot}{\kern0pt}\ x\ {\isasymnotin}\ I{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}submonoid\ S\ R\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymone}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted `definition closed_subsets` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ closed{\isacharunderscore}{\kern0pt}subsets\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymV}\ {\isacharunderscore}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbrackleft}{\kern0pt}{\isadigit{9}}{\isadigit{0}}{\isadigit{0}}{\isacharbrackright}{\kern0pt}\ {\isadigit{9}}{\isadigit{0}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymV}\ {\isasymaa}\ {\isasymequiv}\ {\isacharbraceleft}{\kern0pt}I{\isachardot}{\kern0pt}\ pr{\isacharunderscore}{\kern0pt}ideal\ R\ I\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymand}\ {\isasymaa}\ {\isasymsubseteq}\ I{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted for `lemma closed_subsets_empty` and `lemma closed_subsets_R` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ closed{\isacharunderscore}{\kern0pt}subsets{\isacharunderscore}{\kern0pt}empty{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymV}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ Spec{\isachardoublequoteclose}
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ closed{\isacharunderscore}{\kern0pt}subsets{\isacharunderscore}{\kern0pt}R{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymV}\ R\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippets of code to be inserted here `definition is_zariski_open` and `zariski_is_topological_space` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
+\ \ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ U\ {\isasymequiv}\ generated{\isacharunderscore}{\kern0pt}topology\ Spec\ \isanewline
+\ \ \ \ \ \ \ \ {\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymexists}{\isasymaa}{\isachardot}{\kern0pt}\ ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymand}\ U\ {\isacharequal}{\kern0pt}\ Spec\ {\isacharminus}{\kern0pt}\ {\isasymV}\ {\isasymaa}{\isacharparenright}{\kern0pt}{\isacharbraceright}{\kern0pt}\ U{\isachardoublequoteclose}
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ zariski{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}topological{\isacharunderscore}{\kern0pt}space{\isacharcolon}{\kern0pt}\isanewline
+\ \ {\isachardoublequoteopen}topological{\isacharunderscore}{\kern0pt}space\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\ topological{\isacharunderscore}{\kern0pt}space\isanewline
+\ \ {\isacharplus}{\kern0pt}\ \isakeyword{fixes}\ {\isasymFF}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{and}\ {\isasymrho}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isakeyword{and}\ b{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isacharplus}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymcdot}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphism{\isacharcolon}{\kern0pt}\isanewline
+\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ V{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ V\ {\isasymLongrightarrow}\ V\ {\isasymsubseteq}\ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub V\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub V\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub V\isactrlesub \ {\isasymone}\isactrlbsub V\isactrlesub {\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{and}\ ring{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}empty{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymFF}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}b{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{and}\ identity{\isacharunderscore}{\kern0pt}map\ {\isacharbrackleft}{\kern0pt}simp{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ {\isasymFF}\ U\ {\isasymLongrightarrow}\ {\isasymrho}\ U\ U\ x\ {\isacharequal}{\kern0pt}\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{and}\ assoc{\isacharunderscore}{\kern0pt}comp{\isacharcolon}{\kern0pt}\ \isanewline
+\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ V\ W\ x{\isachardot}{\kern0pt}\ {\isasymlbrakk}is{\isacharunderscore}{\kern0pt}open\ U{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ V{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ W{\isacharsemicolon}{\kern0pt}V\ {\isasymsubseteq}\ U{\isacharsemicolon}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ W\ {\isasymsubseteq}\ V{\isacharsemicolon}{\kern0pt}x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isasymrbrakk}\ {\isasymLongrightarrow}\ {\isasymrho}\ U\ W\ x\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ V\ W\ {\isasymcirc}\ {\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\ x{\isachardoublequoteclose}
+\end{isabelle}
+
 Given the condition \textit{is\_ring\_morphism} within the locale, notice it is possible to prove that the $\mathscr{F}(U)$'s are rings for every open subset $U$ of the underlying topological space.
@@
 % snippet of code to be inserted `is_ring_from_is_homomorphism` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}from{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}homomorphism{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ U{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ U{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ring\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub {\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted `locale morphism_presheaves_of_rings`  of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\isanewline
+\ \ \ \ source{\isacharcolon}{\kern0pt}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\isanewline
+\ \ {\isacharplus}{\kern0pt}\ target{\isacharcolon}{\kern0pt}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\isanewline
+\ \ \isakeyword{for}\ X\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isanewline
+\ \ \ \ \isakeyword{and}\ {\isasymFF}\ \isakeyword{and}\ {\isasymrho}\ \isakeyword{and}\ b\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isacharplus}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymcdot}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ {\isasymFF}{\isacharprime}{\kern0pt}\ \isakeyword{and}\ {\isasymrho}{\isacharprime}{\kern0pt}\ \isakeyword{and}\ b{\isacharprime}{\kern0pt}\ \isanewline
+\ \ \ \ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ fam{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphism{\isacharcolon}{\kern0pt}\ \isanewline
+\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ {\isacharparenleft}{\kern0pt}fam{\isacharunderscore}{\kern0pt}morphisms\ U{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}{\isacharprime}{\kern0pt}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub \ {\isasymone}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub {\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ comm{\isacharunderscore}{\kern0pt}diagrams{\isacharcolon}{\kern0pt}\ \isanewline
+\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ V\ x{\isachardot}{\kern0pt}\ {\isasymlbrakk}is{\isacharunderscore}{\kern0pt}open\ U{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ V{\isacharsemicolon}{\kern0pt}\ V\ {\isasymsubseteq}\ U{\isacharsemicolon}{\kern0pt}x\ {\isasymin}\ {\isasymFF}\ U\ {\isasymrbrakk}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymrho}{\isacharprime}{\kern0pt}\ U\ V\ {\isasymcirc}\ fam{\isacharunderscore}{\kern0pt}morphisms\ U{\isacharparenright}{\kern0pt}\ x\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fam{\isacharunderscore}{\kern0pt}morphisms\ V\ {\isasymcirc}\ {\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\ x{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here for the lemma that states the composition is again a presheaf, namely the statement of `lemma comp_of_presheaves` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ comp{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}presheaves{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ b\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isasymFF}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ b{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isasymphi}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\isanewline
+\ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isasymFF}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymphi}{\isacharprime}{\kern0pt}\ U\ {\isasymcirc}\ {\isasymphi}\ U\ {\isasymdown}\ {\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted `locale iso_presheaves_of_rings` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ iso{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ \isanewline
+\ \ {\isacharequal}{\kern0pt}\ mor{\isacharcolon}{\kern0pt}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\ \isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}inv{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymexists}{\isasympsi}{\isachardot}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ \isanewline
+\ \ \ \ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isasymFF}\ {\isasymrho}\ b\ \isanewline
+\ \ \ \ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isasympsi}\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ {\isasymlongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymforall}x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}{\isacharprime}{\kern0pt}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fam{\isacharunderscore}{\kern0pt}morphisms\ U\ {\isasymcirc}\ {\isasympsi}\ U{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ x{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasympsi}\ U\ {\isasymcirc}\ fam{\isacharunderscore}{\kern0pt}morphisms\ U{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ x{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted for `locale sheaf_of_rings` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ locality{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U\ I\ V\ s{\isachardot}{\kern0pt}\ open{\isacharunderscore}{\kern0pt}cover{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}open{\isacharunderscore}{\kern0pt}subset\ S\ \isanewline
+\ \ \ \ \ \ \ \ \ \ is{\isacharunderscore}{\kern0pt}open\ U\ I\ V\ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymLongrightarrow}\ V\ i\ {\isasymsubseteq}\ U{\isacharparenright}{\kern0pt}\ {\isasymLongrightarrow}\ s\ {\isasymin}\ {\isasymFF}\ U\isanewline
+\ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymLongrightarrow}\ {\isasymrho}\ U\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\ s\ {\isacharequal}{\kern0pt}\ {\isasymzero}\isactrlbsub {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymLongrightarrow}\ s\ {\isacharequal}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub {\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ glueing{\isacharcolon}{\kern0pt}\ \ \isanewline
+\ \ \ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ I\ V\ s{\isachardot}{\kern0pt}\ open{\isacharunderscore}{\kern0pt}cover{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}open{\isacharunderscore}{\kern0pt}subset\ S\ is{\isacharunderscore}{\kern0pt}open\ U\ I\ V\ \isanewline
+\ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymforall}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymlongrightarrow}\ V\ i\ {\isasymsubseteq}\ U\ {\isasymand}\ s\ i\ {\isasymin}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}i\ j{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymLongrightarrow}\ j{\isasymin}I\ {\isasymLongrightarrow}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}V\ i\ {\isasyminter}\ V\ j{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s\ i{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharequal}{\kern0pt}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}V\ j{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}V\ i\ {\isasyminter}\ V\ j{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s\ j{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymexists}t{\isachardot}{\kern0pt}\ t\ {\isasymin}\ {\isasymFF}\ U\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymlongrightarrow}\ {\isasymrho}\ U\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\ t\ {\isacharequal}{\kern0pt}\ s\ i{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted `locale morphism_sheaves_of_rings` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ morphism{\isacharunderscore}{\kern0pt}sheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings
+\end{isabelle}
 
@@
 % snippet of code to be inserted here `locale ind_sheaf` and the following interpretation and definitions up to `definition ind_one_str` and then the statement of `lemma ind_sheaf_is_sheaf` 		
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}sheaf\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ U{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}open{\isacharunderscore}{\kern0pt}subset{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ U{\isachardoublequoteclose}\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ it{\isacharcolon}{\kern0pt}\ ind{\isacharunderscore}{\kern0pt}topology\ S\ is{\isacharunderscore}{\kern0pt}open\ U\isanewline
+
+\isacommand{definition}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}sheaf\ V\ {\isasymequiv}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms\ V\ W\ {\isasymequiv}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ W{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isacharplus}{\kern0pt}\isactrlbsub {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isasymcdot}\isactrlbsub {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymzero}\isactrlbsub {\isacharparenleft}{\kern0pt}U{\isasyminter}V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymone}\isactrlbsub {\isacharparenleft}{\kern0pt}U{\isasyminter}V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
+\ \ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ U\ it{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}open\ ind{\isacharunderscore}{\kern0pt}sheaf\ ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ b\ ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str\ ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str\ ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str\ ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str{\isachardoublequoteclose}\isanewline
+
+\isacommand{end}
+\end{isabelle}
 
@@
 % snippet of code to be inserted `im_sheaf` of Comm_Ring_Theory.thy plus the following definitions up to `one_im_sheaf` and then the `lemma im_sheaf_is_sheaf` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ im{\isacharunderscore}{\kern0pt}sheaf\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\ continuous{\isacharunderscore}{\kern0pt}map\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isacharequal}{\kern0pt}{\isachargreater}{\kern0pt}\ {\isacharprime}{\kern0pt}b\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}im{\isacharunderscore}{\kern0pt}sheaf\ V\ {\isasymequiv}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\ U\ V\ {\isasymequiv}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V\ x\ y{\isachardot}{\kern0pt}\ {\isacharplus}{\kern0pt}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V\ x\ y{\isachardot}{\kern0pt}\ {\isasymcdot}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V{\isachardot}{\kern0pt}\ {\isasymzero}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V{\isachardot}{\kern0pt}\ {\isasymone}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
+\ \ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ S{\isacharprime}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open{\isacharprime}{\kern0pt}\ im{\isacharunderscore}{\kern0pt}sheaf\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\ b\isanewline
+\ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isachardoublequoteclose}\isanewline
+\isacommand{end}
+\end{isabelle}
 
@@
 % and the sublocale that proves the quotient ring is a commutative ring.
+
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ quotient{\isacharunderscore}{\kern0pt}ring\ {\isacharequal}{\kern0pt}\ comm{\isacharcolon}{\kern0pt}comm{\isacharunderscore}{\kern0pt}ring\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ submonoid\ S\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \isakeyword{for}\ S\ \isakeyword{and}\ R\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \isakeyword{and}\ multiplication\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infix}\ {\isachardoublequoteopen}{\isasymsim}{\isachardoublequoteclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isasymsim}\ y\ {\isasymequiv}\ {\isasymexists}s{\isadigit{1}}{\isachardot}{\kern0pt}\ s{\isadigit{1}}\ {\isasymin}\ S\ {\isasymand}\ s{\isadigit{1}}\ {\isasymcdot}\ {\isacharparenleft}{\kern0pt}snd\ y\ {\isasymcdot}\ fst\ x\ {\isacharminus}{\kern0pt}\ snd\ x\ {\isasymcdot}\ fst\ y{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isasymzero}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ frac{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}{\isacharslash}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}r\ {\isacharslash}{\kern0pt}\ s\ {\isasymequiv}\ rel{\isachardot}{\kern0pt}Class\ {\isacharparenleft}{\kern0pt}r{\isacharcomma}{\kern0pt}\ s{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ add{\isacharunderscore}{\kern0pt}rel{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharcomma}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharcomma}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}r{\isacharslash}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharslash}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isasymcdot}s{\isacharprime}{\kern0pt}\ {\isacharplus}{\kern0pt}\ r{\isacharprime}{\kern0pt}{\isasymcdot}s{\isacharparenright}{\kern0pt}\ {\isacharslash}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isasymcdot}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ mult{\isacharunderscore}{\kern0pt}rel{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharcomma}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharcomma}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}r{\isacharslash}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharslash}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isasymcdot}\ r{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharslash}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isasymcdot}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ zero{\isacharunderscore}{\kern0pt}rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
+\ \ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}rel\ {\isacharequal}{\kern0pt}\ frac\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ one{\isacharunderscore}{\kern0pt}rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
+\ \ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}rel\ {\isacharequal}{\kern0pt}\ frac\ {\isasymone}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{sublocale}\isamarkupfalse%
+\ comm{\isacharunderscore}{\kern0pt}ring\ carrier{\isacharunderscore}{\kern0pt}quotient{\isacharunderscore}{\kern0pt}ring\ add{\isacharunderscore}{\kern0pt}rel\ mult{\isacharunderscore}{\kern0pt}rel\ zero{\isacharunderscore}{\kern0pt}rel\ one{\isacharunderscore}{\kern0pt}rel\isanewline
+\isanewline
+\isacommand{end}
+\end{isabelle}
 

### 2021-03-29 article.tex
Update bibliography

@@
 Indeed, in 2003 Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
-More recently, in 2019 Grothendieck's schemes have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
+More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
 \\
@@
 
+	\bibitem{GrothendieckEGAI}
+	Grothendieck A.:
+	\newblock \textit{\'El\'ements de g\'eom\'etrie alg\'ebrique. I. Le langage des sch\'emas}.
+	\newblock Inst. Hautes \'Etudes Sci. Publ. Math., no. 4, 228. MR 217083 (1960)
+
 	\bibitem{schemesinLean}

### 2021-03-29 article.tex
Updates from Overleaf

--- 2021-03-29 article.tex
@@
 \isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ rel{\isacharcolon}{\kern0pt}\ equivalence\ {\isachardoublequoteopen}R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}{\isacharparenleft}{\kern0pt}x{\isacharcomma}{\kern0pt}y{\isacharparenright}{\kern0pt}\ {\isasymin}\ {\isacharparenleft}{\kern0pt}R{\isasymtimes}S{\isacharparenright}{\kern0pt}{\isasymtimes}{\isacharparenleft}{\kern0pt}R{\isasymtimes}S{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ x\ {\isasymsim}\ y{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
 \isacommand{definition}\isamarkupfalse%
@@
 % snippet of code to be inserted for the subsection <Local Rings at Prime Ideals> up to the definition `one_local_ring_at`
+\begin{isabelle}
+\isacommand{context}\isamarkupfalse%
+\ pr{\isacharunderscore}{\kern0pt}ideal\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ submonoid{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}submonoid\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\isacommand{proof}\isamarkupfalse%
+\isanewline
+\ \ \isacommand{show}\isamarkupfalse%
+\ {\isachardoublequoteopen}a\ {\isasymcdot}\ b\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ \isakeyword{if}\ {\isachardoublequoteopen}a\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ {\isachardoublequoteopen}b\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ \isakeyword{for}\ a\ b\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ that\ \isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}metis\ Diff{\isacharunderscore}{\kern0pt}iff\ absorbent\ comm{\isachardot}{\kern0pt}multiplicative{\isachardot}{\kern0pt}composition{\isacharunderscore}{\kern0pt}closed{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isacommand{show}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymone}\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isacommand{using}\isamarkupfalse%
+\ ideal{\isachardot}{\kern0pt}ideal{\isacharparenleft}{\kern0pt}{\isadigit{2}}{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}axioms\ pr{\isacharunderscore}{\kern0pt}ideal{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}neq\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharunderscore}{\kern0pt}axioms\ \isanewline
+\ \ \ \ \isacommand{by}\isamarkupfalse%
+\ fastforce\isanewline
+\isacommand{qed}\isamarkupfalse%
+\ auto%
+\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ local{\isacharcolon}{\kern0pt}quotient{\isacharunderscore}{\kern0pt}ring\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}\isanewline
+\ \ \isacommand{apply}\isamarkupfalse%
+\ intro{\isacharunderscore}{\kern0pt}locales\isanewline
+\ \ \isacommand{by}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}meson\ submonoid{\isacharunderscore}{\kern0pt}def\ submonoid{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}%
+
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}\isactrlsup {\isasyminverse}\ R\isactrlbsub {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ uminus{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}uminus{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}uminus{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{end}
+\end{isabelle}
 
@@
 
+\begin{isabelle}
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac\ s\ V\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}{\isasymexists}r\ f{\isachardot}{\kern0pt}\ r\ {\isasymin}\ R\ {\isasymand}\ f\ {\isasymin}\ R\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}{\isasymqq}\ {\isasymin}\ V{\isachardot}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ f\ {\isasymnotin}\ {\isasymqq}\ {\isasymand}\ s\ {\isasymqq}\ {\isacharequal}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}frac\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasymqq}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ r\ f{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}regular\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}regular\ s\ U\ {\isasymequiv}\ {\isasymforall}{\isasympp}{\isachardot}{\kern0pt}\ {\isasympp}\ {\isasymin}\ U\ {\isasymlongrightarrow}\ \isanewline
+\ \ {\isacharparenleft}{\kern0pt}{\isasymexists}V{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ V\ {\isasymand}\ V\ {\isasymsubseteq}\ U\ {\isasymand}\ {\isasympp}\ {\isasymin}\ V\ {\isasymand}\ {\isacharparenleft}{\kern0pt}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac\ s\ V{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymO}\ {\isacharunderscore}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbrackleft}{\kern0pt}{\isadigit{9}}{\isadigit{0}}{\isacharbrackright}{\kern0pt}\ {\isadigit{9}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymO}\ U\ {\isasymequiv}\ {\isacharbraceleft}{\kern0pt}s{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymPi}\isactrlsub E\ {\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}R\isactrlbsub {\isasympp}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}regular\ s\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ s\ s{\isacharprime}{\kern0pt}\ {\isasymequiv}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isacharparenleft}{\kern0pt}s\ {\isasympp}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isacharprime}{\kern0pt}\ {\isasympp}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ s\ s{\isacharprime}{\kern0pt}\ {\isasymequiv}\ \isanewline
+\ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isacharparenleft}{\kern0pt}s\ {\isasympp}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isacharprime}{\kern0pt}\ {\isasympp}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ {\isasymequiv}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ {\isasymequiv}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\isanewline
+\ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ U\ V\ {\isasymequiv}\ {\isasymlambda}s{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymO}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ restrict\ s\ V{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec{\isachardoublequoteclose}
+\end{isabelle}
+
 Next, we introduce ringed spaces and their morphisms.
@@
 
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ ringed{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings
+\end{isabelle}
+
 \begin{definition}[morphism of ringed spaces]
@@
 % snippet of code `locale morphism_ringed-spaces` of Comm_Ring_Theory.thy to be inserted here
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\isanewline
+\ \ \ \ \ \ im{\isacharunderscore}{\kern0pt}sheaf\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ b\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ f\ \isanewline
+\ \ \ \ \ \ {\isacharplus}{\kern0pt}\ codom{\isacharcolon}{\kern0pt}\ ringed{\isacharunderscore}{\kern0pt}space\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
+\ \ \ \ \ \ \isakeyword{for}\ X\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ \isakeyword{and}\ {\isasymO}\isactrlsub X\ \isakeyword{and}\ {\isasymrho}\isactrlsub X\ \isakeyword{and}\ b\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ Y\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ \isakeyword{and}\ {\isasymO}\isactrlsub Y\ \isakeyword{and}\ {\isasymrho}\isactrlsub Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ d\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ f\ \isanewline
+\ \ \ \ \ \ {\isacharplus}{\kern0pt}\ \isakeyword{fixes}\ {\isasymphi}\isactrlsub f{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}d\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}morphism{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}sheaves{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}sheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ im{\isacharunderscore}{\kern0pt}sheaf\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\ b\ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymphi}\isactrlsub f{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ direct{\isacharunderscore}{\kern0pt}lim\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ I{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ subset{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}opens{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ U\ {\isasymin}\ I\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ U{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ has{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U\ V{\isachardot}{\kern0pt}\ {\isasymlbrakk}\ U{\isasymin}I{\isacharsemicolon}{\kern0pt}\ V{\isasymin}I\ {\isasymrbrakk}\ {\isasymLongrightarrow}\ {\isasymexists}W{\isasymin}I{\isachardot}{\kern0pt}\ W\ {\isasymsubseteq}\ U\ {\isasyminter}\ V{\isachardoublequoteclose}\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infix}\ {\isachardoublequoteopen}{\isasymsim}{\isachardoublequoteclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isasymsim}\ y\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}fst\ x\ {\isasymin}\ I\ {\isasymand}\ fst\ y\ {\isasymin}\ I{\isacharparenright}{\kern0pt}\ {\isasymand}\ {\isacharparenleft}{\kern0pt}snd\ x\ {\isasymin}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ snd\ y\ {\isasymin}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymexists}W{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}W\ {\isasymin}\ I{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharparenleft}{\kern0pt}W\ {\isasymsubseteq}\ fst\ x\ {\isasyminter}\ fst\ y{\isacharparenright}{\kern0pt}\ {\isasymand}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ W\ {\isacharparenleft}{\kern0pt}snd\ x{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharequal}{\kern0pt}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\ W\ {\isacharparenleft}{\kern0pt}snd\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ rel{\isacharcolon}{\kern0pt}equivalence\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}Sigma\ I\ {\isasymFF}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}{\isacharparenleft}{\kern0pt}x{\isacharcomma}{\kern0pt}\ y{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ x\ {\isasymsim}\ y{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ class{\isacharunderscore}{\kern0pt}of{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymlfloor}{\isacharparenleft}{\kern0pt}{\isacharunderscore}{\kern0pt}{\isacharcomma}{\kern0pt}{\isacharslash}{\kern0pt}\ {\isacharunderscore}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymrfloor}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlfloor}U{\isacharcomma}{\kern0pt}s{\isasymrfloor}\ {\isasymequiv}\ rel{\isachardot}{\kern0pt}Class\ {\isacharparenleft}{\kern0pt}U{\isacharcomma}{\kern0pt}\ s{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim\ {\isasymequiv}\ rel{\isachardot}{\kern0pt}Partition{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
+\ \ {\isachardoublequoteopen}get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound\ U\ V{\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ W{\isachardot}{\kern0pt}\ W\ {\isasymin}\ I\ {\isasymand}\ W\ {\isasymsubseteq}\ U\ {\isasymand}\ W\ {\isasymsubseteq}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ add{\isacharunderscore}{\kern0pt}rel\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}rel\ X\ Y\ {\isasymequiv}\ let\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ x\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ X{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ y{\isachardot}{\kern0pt}\ y\ {\isasymin}\ Y{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ w\ {\isacharequal}{\kern0pt}\ get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ in\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlfloor}w{\isacharcomma}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str\ w\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ x{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymrfloor}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ mult{\isacharunderscore}{\kern0pt}rel\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}rel\ X\ Y\ {\isasymequiv}\ let\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ x\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ X{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ y{\isachardot}{\kern0pt}\ y\ {\isasymin}\ Y{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ w\ {\isacharequal}{\kern0pt}\ get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ in\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlfloor}w{\isacharcomma}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str\ w\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ x{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymrfloor}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ exercise{\isacharunderscore}{\kern0pt}{\isadigit{0}}{\isacharunderscore}{\kern0pt}{\isadigit{3}}{\isadigit{5}}{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}U\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ring\ carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim\ add{\isacharunderscore}{\kern0pt}rel\ mult{\isacharunderscore}{\kern0pt}rel\ {\isasymlfloor}U{\isacharcomma}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub {\isasymrfloor}\ {\isasymlfloor}U{\isacharcomma}{\kern0pt}\ {\isasymone}\isactrlbsub U\isactrlesub {\isasymrfloor}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{end}
+\end{isabelle}
+
 For every $U \in I$, there is a canonical inclusion from $\mathscr{F}(U)$ to $\varinjlim \mathscr{F}(U)$.
@@
 % snippet of code to be inserted here for `definition canonical_fun` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{definition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ direct{\isacharunderscore}{\kern0pt}lim{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ canonical{\isacharunderscore}{\kern0pt}fun\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}canonical{\isacharunderscore}{\kern0pt}fun\ U\ x\ {\isacharequal}{\kern0pt}\ {\isasymlfloor}U{\isacharcomma}{\kern0pt}\ x{\isasymrfloor}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here for `proposition (in direct_lim) universal_property`  
+\begin{isabelle}
+\isacommand{proposition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ direct{\isacharunderscore}{\kern0pt}lim{\isacharparenright}{\kern0pt}\ universal{\isacharunderscore}{\kern0pt}property{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ A{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set{\isachardoublequoteclose}\ \isakeyword{and}\ {\isasympsi}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \isakeyword{and}\ add{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\ \isakeyword{and}\ mult{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \isakeyword{and}\ zero{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\ \isakeyword{and}\ one{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}ring\ A\ add\ mult\ zero\ one{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ U\ {\isasymin}\ I\ {\isasymLongrightarrow}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ {\isacharparenleft}{\kern0pt}{\isasympsi}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub \ A\ add\ mult\ zero\ one{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}{\isasymAnd}U\ V\ x{\isachardot}{\kern0pt}\ {\isasymlbrakk}U\ {\isasymin}\ I{\isacharsemicolon}{\kern0pt}\ V\ {\isasymin}\ I{\isacharsemicolon}{\kern0pt}\ V\ {\isasymsubseteq}\ U{\isacharsemicolon}{\kern0pt}\ x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isasymrbrakk}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasympsi}\ V\ {\isasymcirc}\ {\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ {\isasympsi}\ U\ x{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}V{\isasymin}I{\isachardot}{\kern0pt}\ {\isasymexists}{\isacharbang}{\kern0pt}u{\isachardot}{\kern0pt}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ u\ carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim\ add{\isacharunderscore}{\kern0pt}rel\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}rel\ {\isasymlfloor}V{\isacharcomma}{\kern0pt}{\isasymzero}\isactrlbsub V\isactrlesub {\isasymrfloor}\ {\isasymlfloor}V{\isacharcomma}{\kern0pt}{\isasymone}\isactrlbsub V\isactrlesub {\isasymrfloor}\ A\ add\ mult\ zero\ one\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}U{\isasymin}I{\isachardot}{\kern0pt}\ {\isasymforall}x{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}u\ {\isasymcirc}\ canonical{\isacharunderscore}{\kern0pt}fun\ U{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ {\isasympsi}\ U\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ stalk\ {\isacharequal}{\kern0pt}\ direct{\isacharunderscore}{\kern0pt}lim\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ x{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}elem{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}x\ {\isasymin}\ S{\isachardoublequoteclose}\ \isakeyword{and}\ index{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}I\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymand}\ x\ {\isasymin}\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ carrier{\isacharunderscore}{\kern0pt}stalk{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}stalk\ {\isasymequiv}\ dlim\ {\isasymFF}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}neighborhoods\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ add{\isacharunderscore}{\kern0pt}stalk\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}stalk\ {\isasymequiv}\ add{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ mult{\isacharunderscore}{\kern0pt}stalk\isanewline
+\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}stalk\ {\isasymequiv}\ mult{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ zero{\isacharunderscore}{\kern0pt}stalk{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}stalk\ V\ {\isasymequiv}\ class{\isacharunderscore}{\kern0pt}of\ V\ {\isasymzero}\isactrlbsub V\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ one{\isacharunderscore}{\kern0pt}stalk{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}stalk\ V\ {\isasymequiv}\ class{\isacharunderscore}{\kern0pt}of\ V\ {\isasymone}\isactrlbsub V\isactrlesub {\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{end}
+\end{isabelle}
+
 One further step towards schemes consists in introducing local rings, but first one needs to teach Isabelle simple facts about \emph{maximal ideals} starting with their definition.
@@
 % snippet of code to be inserted here for `locale max_ideal`
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ max{\isacharunderscore}{\kern0pt}ideal\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ ideal\ I\ \ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{for}\ R\ \isakeyword{and}\ I\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \isakeyword{and}\ multiplication\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ neq{\isacharunderscore}{\kern0pt}ring{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}I\ {\isasymnoteq}\ R{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}max{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}{\isasymaa}{\isachardot}{\kern0pt}\ {\isasymlbrakk}ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isacharsemicolon}{\kern0pt}{\isasymaa}\ {\isasymnoteq}\ R{\isacharsemicolon}{\kern0pt}I\ {\isasymsubseteq}\ {\isasymaa}\ {\isasymrbrakk}{\isasymLongrightarrow}\ I\ {\isacharequal}{\kern0pt}\ {\isasymaa}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be included for `proposition is_pr_ideal` of Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{proposition}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ max{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}pr{\isacharunderscore}{\kern0pt}ideal\ R\ I\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be included here for `locale local_ring`
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ local{\isacharunderscore}{\kern0pt}ring\ {\isacharequal}{\kern0pt}\ ring\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}unique{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}I\ J{\isachardot}{\kern0pt}\ max{\isacharunderscore}{\kern0pt}lideal\ I\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ max{\isacharunderscore}{\kern0pt}lideal\ J\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymLongrightarrow}\ I\ {\isacharequal}{\kern0pt}\ J{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ has{\isacharunderscore}{\kern0pt}max{\isacharunderscore}{\kern0pt}lideal{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymexists}{\isasymww}{\isachardot}{\kern0pt}\ max{\isacharunderscore}{\kern0pt}lideal\ {\isasymww}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be included for `lemma local_ring_at_is_local` of Comm_Ring_Theory.thy.
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here `locale local_ring_morphism`	
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphism\ {\isacharequal}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ source{\isacharcolon}{\kern0pt}\ local{\isacharunderscore}{\kern0pt}ring\ A\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ target{\isacharcolon}{\kern0pt}\ local{\isacharunderscore}{\kern0pt}ring\ B\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ f\ A\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ B\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{for}\ f\ \isakeyword{and}\ A\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ multiplication\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ B\ \isakeyword{and}\ addition{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \isakeyword{and}\ multiplication{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\ \ {\isacharplus}{\kern0pt}\ \isakeyword{assumes}\ preimage{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}max{\isacharunderscore}{\kern0pt}lideal{\isacharcolon}{\kern0pt}\isanewline
+\ \ \ \ \ \ {\isachardoublequoteopen}{\isasymAnd}{\isasymww}\isactrlsub A\ {\isasymww}\isactrlsub B{\isachardot}{\kern0pt}\ max{\isacharunderscore}{\kern0pt}lideal\ {\isasymww}\isactrlsub A\ A\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymLongrightarrow}\ max{\isacharunderscore}{\kern0pt}lideal\ {\isasymww}\isactrlsub B\ B\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isasymzero}{\isacharprime}{\kern0pt}\ {\isasymone}{\isacharprime}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ A\ {\isasymww}\isactrlsub B{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isasymww}\isactrlsub A{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be introduced here for `locale locally_ringed_space`
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ ringed{\isacharunderscore}{\kern0pt}space\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ stalks{\isacharunderscore}{\kern0pt}are{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}x\ U{\isachardot}{\kern0pt}\ x\ {\isasymin}\ U\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ stalk{\isachardot}{\kern0pt}is{\isacharunderscore}{\kern0pt}local\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}neighborhoods\ x{\isacharparenright}{\kern0pt}\ x\ U{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here for `lemma stalk_at_prime_is_iso_to_local_ring_at_prime`
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ key{\isacharunderscore}{\kern0pt}map\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ {\isasympp}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}prime{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasympp}\ {\isasymin}\ Spec{\isachardoublequoteclose}\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ pi{\isacharcolon}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal\ R\ {\isasympp}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}%
+\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ st{\isacharcolon}{\kern0pt}\ stalk\ {\isachardoublequoteopen}Spec{\isachardoublequoteclose}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ U\ {\isasymand}\ {\isasympp}{\isasymin}U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ {\isasympp}\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ stalk{\isacharunderscore}{\kern0pt}at{\isacharunderscore}{\kern0pt}prime{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}iso{\isacharunderscore}{\kern0pt}to{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharunderscore}{\kern0pt}prime{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ V{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}{\isasympp}\ {\isasymin}\ V{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}{\isasymphi}{\isachardot}{\kern0pt}\ ring{\isacharunderscore}{\kern0pt}isomorphism\ {\isasymphi}\ st{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}stalk\ st{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}stalk\ st{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}stalk\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}st{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}stalk\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}st{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}stalk\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}R\ \isactrlbsub {\isasympp}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{end}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here for the corresponding statement in Isabelle `lemma spec_is_locally_ringed_space`
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here for `locale ind_morphism_bwt_lim`	up to `definition induced_morphism`
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ ind{\isacharunderscore}{\kern0pt}mor{\isacharunderscore}{\kern0pt}btw{\isacharunderscore}{\kern0pt}stalks\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ x{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isachardoublequoteopen}{\isacharprime}{\kern0pt}a{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}elem{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}x\ {\isasymin}\ X{\isachardoublequoteclose}\isanewline
+\isakeyword{begin}\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ stx{\isacharcolon}{\kern0pt}stalk\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ b\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
+\ \ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ U\ {\isasymand}\ x\ {\isasymin}\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}x{\isachardoublequoteclose}\isanewline
+\isacommand{proof}\isamarkupfalse%
+\ \isacommand{qed}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}auto\ simp{\isacharcolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}elem{\isacharparenright}{\kern0pt}%
+\isanewline
+\isanewline
+\isacommand{interpretation}\isamarkupfalse%
+\ stfx{\isacharcolon}{\kern0pt}\ stalk\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
+\ \ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ U\ {\isasymand}\ {\isacharparenleft}{\kern0pt}f\ x{\isacharparenright}{\kern0pt}\ {\isasymin}\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}f\ x{\isachardoublequoteclose}\isanewline
+\isacommand{proof}\isamarkupfalse%
+\ \isacommand{qed}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}auto\ simp{\isacharcolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}elem{\isacharparenright}{\kern0pt}%
+\isanewline
+\isanewline
+\isacommand{definition}\isamarkupfalse%
+\ induced{\isacharunderscore}{\kern0pt}morphism{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}c\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}d{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}induced{\isacharunderscore}{\kern0pt}morphism\ {\isasymequiv}\ {\isasymlambda}C\ {\isasymin}\ stfx{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}stalk{\isachardot}{\kern0pt}\ \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ let\ r\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ r{\isachardot}{\kern0pt}\ r\ {\isasymin}\ C{\isacharparenright}{\kern0pt}\ in\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ stx{\isachardot}{\kern0pt}class{\isacharunderscore}{\kern0pt}of\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ X\ {\isacharparenleft}{\kern0pt}fst\ r{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymphi}\isactrlsub f\ {\isacharparenleft}{\kern0pt}fst\ r{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}snd\ r{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{end}
+\end{isabelle}
 
@@
 % snippet of code to be introduced here for `locale morphism_locally_ringed_spaces`, still in Comm_Ring_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ morphism{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ are{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}\isanewline
+\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}x\ V{\isachardot}{\kern0pt}\ {\isasymlbrakk}x\ {\isasymin}\ X{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ V{\isacharsemicolon}{\kern0pt}\ f\ x\ {\isasymin}\ V{\isasymrbrakk}\ {\isasymLongrightarrow}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ ind{\isacharunderscore}{\kern0pt}mor{\isacharunderscore}{\kern0pt}btw{\isacharunderscore}{\kern0pt}stalks{\isachardot}{\kern0pt}is{\isacharunderscore}{\kern0pt}local\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ f\ x\ V\ {\isasymphi}\isactrlbsub X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymrho}\isactrlsub X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ f\ {\isasymphi}\isactrlsub f\ x\isactrlesub {\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be introduced for `iso_locally_ringed_spaces`
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ iso{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}homeomorphism{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}homeomorphism\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ f{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}iso{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}sheaves{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}iso{\isacharunderscore}{\kern0pt}sheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ im{\isacharunderscore}{\kern0pt}sheaf\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ b\ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymphi}\isactrlsub f{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be introduced for `locale affine_scheme` in Scheme_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ affine{\isacharunderscore}{\kern0pt}scheme\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ \isanewline
+\ \ \ \ {\isacharplus}{\kern0pt}\ locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ \isanewline
+\ \ \ \ {\isacharplus}{\kern0pt}\ iso{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\isanewline
+\ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isachardoublequoteopen}Spec{\isachardoublequoteclose}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\ f\ {\isasymphi}\isactrlsub f\isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{for}\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ f\ {\isasymphi}\isactrlsub f
+\end{isabelle}
 
@@
 % snippet of code to be introduced here for `lemma spec_is_affine_scheme`
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}affine{\isacharunderscore}{\kern0pt}scheme{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}affine{\isacharunderscore}{\kern0pt}scheme\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}identity\ Spec{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ identity\ {\isacharparenleft}{\kern0pt}{\isasymO}\ U{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be inserted here for `locale scheme`
-
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ scheme\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ \isanewline
+\ \ \ \ \ {\isacharplus}{\kern0pt}\ locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ \isanewline
+\ \ \isakeyword{for}\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isacharplus}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ are{\isacharunderscore}{\kern0pt}affine{\isacharunderscore}{\kern0pt}schemes{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ X\ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymexists}U{\isachardot}{\kern0pt}\ x{\isasymin}U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ {\isasymand}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymand}\ \ {\isacharparenleft}{\kern0pt}{\isasymexists}f\ {\isasymphi}\isactrlsub f{\isachardot}{\kern0pt}\ affine{\isacharunderscore}{\kern0pt}scheme\ \ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}topology{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}open\ X\ is{\isacharunderscore}{\kern0pt}open\ U{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf\ {\isasymO}\isactrlsub X\ U{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms\ {\isasymrho}\ U{\isacharparenright}{\kern0pt}\ b\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str\ add{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\ f\ {\isasymphi}\isactrlsub f{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 To catch on the state of the art in the Lean theorem prover, we finally prove in Isabelle that an affine scheme is a scheme and we give the example of the empty scheme $(\emptyset, \mathscr{O}_\emptyset)$, where $\mathscr{O}_\emptyset(\emptyset)$ is the zero ring $\lbrace 0 \rbrace$.
@@
 % snippets of code to be inserted here for `lemma affine_scheme_is_scheme` and for `empty_scheme_is_scheme`
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ affine{\isacharunderscore}{\kern0pt}scheme{\isacharparenright}{\kern0pt}\ affine{\isacharunderscore}{\kern0pt}scheme{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}scheme{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}scheme\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str{\isachardoublequoteclose}
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ empty{\isacharunderscore}{\kern0pt}scheme{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}scheme{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}scheme\ {\isacharbraceleft}{\kern0pt}{\isadigit{0}}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}nat{\isacharbraceright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isadigit{0}}\ {\isadigit{0}}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ U{\isacharequal}{\kern0pt}{\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}{\isadigit{0}}{\isacharbraceright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U\ V{\isachardot}{\kern0pt}\ identity{\isacharbraceleft}{\kern0pt}{\isadigit{0}}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}nat{\isacharbraceright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isadigit{0}}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U\ x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U\ x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 
@@
 % snippet of code to be included here for `locale topological_space` of Topological_Space_Theory.thy
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ topological{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ \isanewline
+\ \ \isakeyword{fixes}\ S\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{assumes}\ open{\isacharunderscore}{\kern0pt}space\ {\isacharbrackleft}{\kern0pt}simp{\isacharcomma}{\kern0pt}\ intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ S{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}empty\ {\isacharbrackleft}{\kern0pt}simp{\isacharcomma}{\kern0pt}\ intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}imp{\isacharunderscore}{\kern0pt}subset{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ U\ {\isasymsubseteq}\ S{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}inter\ {\isacharbrackleft}{\kern0pt}intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymlbrakk}is{\isacharunderscore}{\kern0pt}open\ U{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ V{\isasymrbrakk}\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}union\ {\isacharbrackleft}{\kern0pt}intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymAnd}F{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ F\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ x{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ {\isacharparenleft}{\kern0pt}{\isasymUnion}x{\isasymin}F{\isachardot}{\kern0pt}\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
+
 Within the locale for topological spaces the axiom \textit{open\_imp\_subset} enforces that an open is automatically a subset of the ambient space.
@@
 % snippets of code to be included here for `inductive generated_topology`, `lemma generated_topology_is_topology`  and `locale homeomorphism`
-\\
+\begin{isabelle}
+\isacommand{inductive}\isamarkupfalse%
+\ generated{\isacharunderscore}{\kern0pt}topology\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \isakeyword{for}\ S\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{and}\ B\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{where}\isanewline
+\ \ \ \ UNIV{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ S{\isachardoublequoteclose}\isanewline
+\ \ {\isacharbar}{\kern0pt}\ Int{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \isakeyword{if}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ U{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ V{\isachardoublequoteclose}\isanewline
+\ \ {\isacharbar}{\kern0pt}\ UN{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ {\isacharparenleft}{\kern0pt}{\isasymUnion}K{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \isakeyword{if}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymAnd}U{\isachardot}{\kern0pt}\ U\ {\isasymin}\ K\ {\isasymLongrightarrow}\ generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ U{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\ \ {\isacharbar}{\kern0pt}\ Basis{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ b{\isachardoublequoteclose}\ \isakeyword{if}\ {\isachardoublequoteopen}b\ {\isasymin}\ B\ {\isasymand}\ b\ {\isasymsubseteq}\ S{\isachardoublequoteclose}
+\end{isabelle}
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ generated{\isacharunderscore}{\kern0pt}topology{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}topology{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{fixes}\ S{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{and}\ B{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}topological{\isacharunderscore}{\kern0pt}space\ S\ {\isacharparenleft}{\kern0pt}generated{\isacharunderscore}{\kern0pt}topology\ S\ B{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
+\begin{isabelle}
+\isacommand{locale}\isamarkupfalse%
+\ homeomorphism\ {\isacharequal}{\kern0pt}\ \isanewline
+\ \ continuous{\isacharunderscore}{\kern0pt}map\ {\isacharplus}{\kern0pt}\ bijective{\isacharunderscore}{\kern0pt}map\ f\ S\ S{\isacharprime}{\kern0pt}\ {\isacharplus}{\kern0pt}\ \isanewline
+\ \ continuous{\isacharunderscore}{\kern0pt}map\ S{\isacharprime}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open{\isacharprime}{\kern0pt}\ S\ is{\isacharunderscore}{\kern0pt}open\ {\isachardoublequoteopen}inverse{\isacharunderscore}{\kern0pt}map\ f\ S\ S{\isacharprime}{\kern0pt}{\isachardoublequoteclose}
+\end{isabelle}
 The formalized material has a size of roughly 7300-line of code including some prerequisites in commutative  algebra and our partial reconstruction of the topology library.

### 2021-03-30 article.tex
Update article

@@
 
+\begin{rem}
+	Note that in the code above the ideal is denoted $I$ while the beloved gothic letters are standard in mathematics for denoting ideals. In our code we use both depending on the situation.
+\end{rem}
+
 One easily checks that $\lbrace 0 \rbrace$ and $R$ are ideals of $R$. In our formalization this translates as follows.
@@
 	\[
-	\lbrace a b \mid a \in \mathfrak{a}, b \in \mathfrak{b} \rbrace
+	\lbrace a b \mid a \in \mathfrak{a}, b \in \mathfrak{b} \rbrace \, .
 	\]
@@
 
-and one easily checks it is an ideal.
+One easily checks $\mathfrak{a} \mathfrak{b}$ is an ideal.
 
@@
 
-The ideal $\mathfrak{a} \mathfrak{b}$ is in fact the intersection of all ideals of $R$ containing the set
+This ideal is in fact the intersection of all ideals of $R$ containing the set
 	\[
@@
 One checks $(S^{-1} R, 0/1, +, 1/1, \times)$ is a ring. The new ring $S^{-1} R$ is called the \emph{quotient ring of $R$ by $S$}. \\
-This construction translates into the following very legible locale.
+This construction translates into the following very legible locale ending with a proof that the quotient ring is indeed a ring.
 
@@
 \isacommand{lemma}\isamarkupfalse%
-\ exercise{\isacharunderscore}{\kern0pt}{\isadigit{0}}{\isacharunderscore}{\kern0pt}{\isadigit{3}}{\isadigit{5}}{\isacharcolon}{\kern0pt}\isanewline
+\ direct{\isacharunderscore}{\kern0pt}{lim}{\isacharunderscore}{\kern0pt}{is}{\isacharunderscore}{\kern0pt}{ring}{\isacharcolon}{\kern0pt}\isanewline
 \ \ \isakeyword{assumes}\ {\isachardoublequoteopen}U\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
@@
 Without this mechanism the terms involved in the statements and proof scripts of such an intricate hierarchy of nested algebraic structures would have to be fed with many arguments, cluttering these statements and proof scripts to the point where they would become unreadable and difficult to use.
-Fortunately, the interpretation mechanism that comes with locales allows for concise and manageable terms with many implicit arguments which are declared beforehand using the interpretation mechanism.
+Fortunately, the interpretation mechanism that comes with locales allows for concise and manageable terms with many implicit arguments which are declared beforehand using the interpretation mechanism and its commands \textit{interpretation} and \textit{interpret}.
 

### 2021-03-30 article.tex
Update article

@@
 \begin{proposition}
+	\label{prop:keyprop}
 	For every $\mathfrak{p} \in \text{Spec}\,R$, the stalk $\mathscr{O}_{\spec, \mathfrak{p}}$ is isomorphic as a ring to $R_{\mathfrak{p}}$.	
@@
 
+Now, it suffices to teach Isabelle that a ring that is isomorphic to a local ring is local.
+
+% snippet of code to be inserted here for the statement of `lemma isomorphic_to_local_is_local`
+
 \begin{cor}
@@
 
-As a sanity check for our formal definitions, we prove in Isabelle that the spectrum of a commutative ring is indeed a locally ringed space, a result that requires some amount of formal machinery.
+As a sanity check for our formal definitions, we eventually prove in Isabelle that the spectrum of a commutative ring is indeed a locally ringed space, a result that required some amount of formal machinery, especially to prove the key proposition \ref{prop:keyprop}.
 

### 2021-03-30 article.tex
Update acknowledgments
Added the snippet for lemma isomorphic_to_local_is_local

@@
 
+\begin{isabelle}
+\isacommand{lemma}\isamarkupfalse%
+\ isomorphic{\isacharunderscore}{\kern0pt}to{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\isanewline
+\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ B\ addB\ multB\ zeroB\ oneB{\isachardoublequoteclose}\isanewline
+\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}ring{\isacharunderscore}{\kern0pt}isomorphism\ f\ A\ addA\ multA\ zeroA\ oneA\ B\ addB\ multB\ zeroB\ oneB{\isachardoublequoteclose}\isanewline
+\ \ \isakeyword{shows}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ A\ addA\ multA\ zeroA\ oneA{\isachardoublequoteclose}
+\end{isabelle}
+
 \begin{cor}
@@
 
-Work on this paper was supported by the European Research Council Advanced Grant ALEXANDRIA (Project 742178).
+Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).
 

### 2021-04-06 article.tex
Update article

@@
 
-Moreover, one has the following results.
+Moreover, one has the following result.
 
@@
 
-Now, it suffices to teach Isabelle that a ring that is isomorphic to a local ring is local.
+Now, it suffices to teach Isabelle that a ring which is isomorphic to a local ring is local.
 
@@
 \\
-To summarize, our work makes a triple contribution to Isabelle/HOL: a first stepping stone towards a new topology library, a second stepping stone towards a new algebra library and a formalization of schemes in algebraic geometry.
-Most importantly, our work demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
+To summarize, our work makes a triple contribution to Isabelle/HOL: a first stepping stone towards a new topology library, a second stepping stone towards a new algebra library and finally it develops a library for modern algebraic geometry.
+\\
+Most importantly, our work meets the challenge of formalizing for the first time Grothendieck's schemes in a simple type theory and in doing so it demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
+We hope this work will help mathematicians interested in the formalization of mathematics to make a more informed decision about which systems are available to them.
+\\
 Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
@@
 
-Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).
+Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).  \\
+Anthony Bordg thanks Kevin Buzzard for his stimulating wit and his communicative energy.
 

### 2021-04-06 article.tex
Update article

@@
 We also hope the present work could serve as a second stepping stone in that direction.
-Also, we seized the opportunity of formalizing schemes to partly rebuild the topology library.
-Our new topology library is entirely built on modern locales instead of using type classes like it is the case in \textit{HOL-Topological\_Spaces.thy}, allowing for more abstraction.
-In particular, our topological spaces have explicit carrier sets instead of using \textit{UNIV}.
+Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy} and \textit{HOL-Analysis/Abstract\_Topology}.
+Our new topology library is entirely built on modern locales without using type classes nor type declarations (via the \textit{typedef} command).
+In particular, our topological spaces have explicit carrier sets as part of their data instead of using \textit{UNIV} or having to define it later as the union of all the open sets.
 % snippet of code to be included here for `locale topological_space` of Topological_Space_Theory.thy
@@
 Within the locale for topological spaces the axiom \textit{open\_imp\_subset} enforces that an open is automatically a subset of the ambient space.
-This is a nice addition to the former definition, since it avoids having to add this assumption in every lemma including an open among its assumptions.
-Our library rebuilds basic facts about topological spaces without using type classes or any deprecated feature of Isabelle and it includes among other things material about the topology generated by a basis, covers, the induced topology on a subset and homeomorphisms.
+This is a welcome addition, since it avoids having to add this assumption in every lemma mentioning an open set among its assumptions, making the economy of dozens of trivial assumptions.
+Our library includes basic facts about topological spaces like the topology generated by a basis, covers, the induced topology on a subset and homeomorphisms.
 % snippets of code to be included here for `inductive generated_topology`, `lemma generated_topology_is_topology`  and `locale homeomorphism`
@@
 \end{isabelle}
-The formalized material has a size of roughly 7300-line of code including some prerequisites in commutative  algebra and our partial reconstruction of the topology library.
+The formalized material has a size of roughly 7300-line of code including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring \dots) and even our partial reconstruction of the topology library (down to the notion of a topological space).
 Given the output of this work, a formalization of schemes in Isabelle, such a relatively short formalization conveys the power of Isabelle module systems.
@@
 \end{quote}	
-This raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage.
+This raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage \cite{PaulsonLamport}.
 Indeed, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
@@
 
+	\bibitem{PaulsonLamport}
+	Lamport, L. and Paulson, L. C.:
+	\newblock \textit{Should Your Specification Language Be Typed}.
+	\newblock  ACM Transactions on Programming Languages and Systems (TOPLAS) 21, no. 3, 502-526 (1999)
+
 \end{thebibliography}

### 2021-04-07 article.tex
Update article

@@
 \section{Concluding Thoughts}
+\setlength{\parindent}{10ex}
 
@@
 \end{isabelle}
-
 Within the locale for topological spaces the axiom \textit{open\_imp\_subset} enforces that an open is automatically a subset of the ambient space.
@@
 \end{isabelle}
+
+Actually, this reliance on modern locales avoiding type classes and type declarations whenever possible is present throughout our development.
+It inaugurates a new discipline of formalizing mathematics with Isabelle/HOL which is exemplary in bridging the gap between set theory and type theory within Isabelle/HOL, with the benefit of avoiding the extension of Isabelle's logic with a new rule for type definition as proposed by Kun\v{c}ar and Popescu in their types-to-sets framework \cite{typestosets}.
+\\
 The formalized material has a size of roughly 7300-line of code including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring \dots) and even our partial reconstruction of the topology library (down to the notion of a topological space).
@@
 We hope this work will help mathematicians interested in the formalization of mathematics to make a more informed decision about which systems are available to them.
-\\
-Actually, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
+
+Last, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
 \begin{quote}
@@
 
+	\bibitem{typestosets}
+	Kunčar, O., Popescu, A.:
+	\newblock \textit{From Types to Sets by Local Type Definition in Higher-Order Logic}. 
+	\newblock J Autom Reasoning 62, 237–260 (2019)
+
 	\bibitem{PaulsonLamport}

### 2021-04-07 article.tex
Update article
Add footnotes with links

@@
 We also hope the present work could serve as a second stepping stone in that direction.
-Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy} and \textit{HOL-Analysis/Abstract\_Topology}.
+Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/Topological_Spaces.html}} and \textit{HOL-Analysis/Abstract\_Topology}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Analysis/Abstract_Topology.html}}.
 Our new topology library is entirely built on modern locales without using type classes nor type declarations (via the \textit{typedef} command).
@@
 	\newblock \textit{From Types to Sets by Local Type Definition in Higher-Order Logic}. 
-	\newblock J Autom Reasoning 62, 237–260 (2019)
+	\newblock J. Autom. Reason. 62, 237–260 (2019)
 

### 2021-04-07 article.tex
Updates from Overleaf

--- 2021-04-06 article.tex
@@
 
+\section{Isabelle/HOL, Simple Type Theory and Locales}
+\label{sec:isabelle}
+
 \section{Schemes in Isabelle/HOL}
@@
 We also hope the present work could serve as a second stepping stone in that direction.
-Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy} and \textit{HOL-Analysis/Abstract\_Topology}.
-Our new topology library is entirely built on modern locales without using type classes nor type declarations (via the \textit{typedef} command).
-In particular, our topological spaces have explicit carrier sets as part of their data instead of using \textit{UNIV} or having to define it later as the union of all the open sets.
+Also, we seized the opportunity of formalizing schemes to partly rebuild the topology library.
+Our new topology library is entirely built on modern locales instead of using type classes like it is the case in \textit{HOL-Topological\_Spaces.thy}, allowing for more abstraction.
+In particular, our topological spaces have explicit carrier sets instead of using \textit{UNIV}.
 % snippet of code to be included here for `locale topological_space` of Topological_Space_Theory.thy
@@
 Within the locale for topological spaces the axiom \textit{open\_imp\_subset} enforces that an open is automatically a subset of the ambient space.
-This is a welcome addition, since it avoids having to add this assumption in every lemma mentioning an open set among its assumptions, making the economy of dozens of trivial assumptions.
-Our library includes basic facts about topological spaces like the topology generated by a basis, covers, the induced topology on a subset and homeomorphisms.
+This is a nice addition to the former definition, since it avoids having to add this assumption in every lemma including an open among its assumptions.
+Our library rebuilds basic facts about topological spaces without using type classes or any deprecated feature of Isabelle and it includes among other things material about the topology generated by a basis, covers, the induced topology on a subset and homeomorphisms.
 % snippets of code to be included here for `inductive generated_topology`, `lemma generated_topology_is_topology`  and `locale homeomorphism`
@@
 \end{isabelle}
-The formalized material has a size of roughly 7300-line of code including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring \dots) and even our partial reconstruction of the topology library (down to the notion of a topological space).
+The formalized material has a size of roughly 7300-line of code including some prerequisites in commutative  algebra and our partial reconstruction of the topology library.
 Given the output of this work, a formalization of schemes in Isabelle, such a relatively short formalization conveys the power of Isabelle module systems.
@@
 \end{quote}	
-This raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage \cite{PaulsonLamport}.
+This raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage.
 Indeed, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
@@
 
-	\bibitem{PaulsonLamport}
-	Lamport, L. and Paulson, L. C.:
-	\newblock \textit{Should Your Specification Language Be Typed}.
-	\newblock  ACM Transactions on Programming Languages and Systems (TOPLAS) 21, no. 3, 502-526 (1999)
-
 \end{thebibliography}

### 2021-04-07 article.tex
A section about Isabelle from Larry

--- 2021-04-07 article.tex
@@
 
+\section{Isabelle/HOL, Simple Type Theory and Locales}
+\label{sec:isabelle}
+
+Isabelle/HOL is a proof assistant for higher-order logic: Church's simple type theory~\cite{church40}, with a number of modest extensions.
+It is therefore based on the typed $\lambda$-calculus with boolean and function types.
+A boolean-valued function is a predicate, which yields a simple typed set theory that is expressive enough to express abstract mathematics, as we shall see below.
+
+In Church's original conception, the sole purpose to types is to prevent inconsistency. People today, influenced by programming languages, prefer to give types a more dominant role.
+
 \section{Schemes in Isabelle/HOL}

### 2021-04-07 article.tex
Updates from Overleaf

@@
 
-\begin{thebibliography}{}
-
-	\bibitem{Group-Ring-Module-AFP}
-	Kobayashi H., Chen L. and Murao H.:
-	\newblock \textit{Groups, Rings and Modules}.
-	\newblock Archive of Formal Proofs (2004)
-
-	\bibitem{VectorSpace-AFP}
-	Lee H.:
-	\newblock \textit{Vector Spaces}.
-	\newblock Archive of Formal Proofs (2014)
-
-	\bibitem{ballarin2014}
-	Ballarin, C.: 
-	\newblock \textit{Locales: A Module System for Mathematical Theories}.
-	\newblock J. Autom. Reason. 52, 123–153 (2014)
-
-	\bibitem{ballarin20}
-	Ballarin, C.:
-	\newblock \textit{Exploring the Structure of an Algebra Text with Locales}. 
-	\newblock J. Autom. Reason. 64(6), 1093–1121 (2020)
-
-	\bibitem{chiclithesis}
-	Chicli L.:
-	\newblock \textit{Sur la formalisation des math\'ematiques dans le Calcul des Constructions Inductives}.
-	\newblock doctoral thesis (2003)
-
-	\bibitem{GrothendieckEGAI}
-	Grothendieck A.:
-	\newblock \textit{\'El\'ements de g\'eom\'etrie alg\'ebrique. I. Le langage des sch\'emas}.
-	\newblock Inst. Hautes \'Etudes Sci. Publ. Math., no. 4, 228. MR 217083 (1960)
-
-	\bibitem{schemesinLean}
-	Buzzard K., Hughes C., Lau K., Livingston A., Mir R. and Morrison S.:
-	\newblock \textit{Schemes in Lean}.
-	\newblock arXiv:2101.02602
-
-	\bibitem{hartshorne}
-	Hartshorne, R.:
-	\newblock \textit{Algebraic Geometry}.
-	\newblock Graduate Texts in Mathematics, Springer (1977)
-
-	\bibitem{bordg18}
-	Bordg A.:
-	\newblock \textit{The Localization of a Commutative Ring}.
-	\newblock Archive of Formal Proofs (2018)
-
-	\bibitem{typestosets}
-	Kunčar, O., Popescu, A.:
-	\newblock \textit{From Types to Sets by Local Type Definition in Higher-Order Logic}. 
-	\newblock J. Autom. Reason. 62, 237–260 (2019)
-
-	\bibitem{PaulsonLamport}
-	Lamport, L. and Paulson, L. C.:
-	\newblock \textit{Should Your Specification Language Be Typed}.
-	\newblock  ACM Transactions on Programming Languages and Systems (TOPLAS) 21, no. 3, 502-526 (1999)
-
-\end{thebibliography}
+\bibliographystyle{plain}
+\bibliography{ALEXANDRIA}
 

### 2021-04-07 article.tex

@@
 As a result, there is an important amount of duplicated code and it makes the situation unclear regarding the status of algebra for the newcomer in the Isabelle world.
-Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the modern locales, a powerful module system in Isabelle for managing theory hierarchies \cite{ballarin2014}.
+Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the modern locales, a powerful module system in Isabelle for managing theory hierarchies \cite{ballarin-locales-module}.
 Therefore, HOL-Algebra contains some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
 Indeed, this last locale uses records and there does not exist multiple inheritances for records, hence the awkward use of the ring record for abelian groups.
-However, a successful experiment was conducted recently in \cite{ballarin20} showing that modern locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
+However, a successful experiment was conducted recently in \cite{ballarin-exploring} showing that modern locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
 So, hopefully, the situation should dramatically improved in the near future.
@@
 For the remainder of this text fix a commutative ring $R$. \\
-The definition of an ideal of $R$ was introduced in Isabelle in \cite{ballarin20}.
+The definition of an ideal of $R$ was introduced in Isabelle in \cite{ballarin-exploring}.
 
@@
 Next, we take a detour into the localization of commutative rings.
-This construction was already formalized by the first author in \cite{bordg18}, but we give a more concise formalization here since the first author gained a better knowledge of the locale mechanism in the meantime.
+This construction was already formalized by the first author in \cite{Localization_Ring-AFP}, but we give a more concise formalization here since the first author gained a better knowledge of the locale mechanism in the meantime.
 \\
@@
 
-For our formalization we built upon Ballarin's work \cite{ballarin20} formalizing parts of Jacobson's \textit{Basic Algebra} textbook.
+For our formalization we built upon Ballarin's work \cite{ballarin-exploring} formalizing parts of Jacobson's \textit{Basic Algebra} textbook.
 We believe Ballarin's nice formalization could serve as a first stepping stone to a new algebra library for Isabelle.

### 2021-04-07 article.tex
Updates from Overleaf

@@
 
-Isabelle/HOL is a proof assistant for higher-order logic: Church's simple type theory~\cite{church40}, with a number of modest extensions.
+Isabelle/HOL~\cite{isa-tutorial} is a proof assistant for higher-order logic: Church's simple type theory~\cite{church40}, with a number of modest extensions.
 It is therefore based on the typed $\lambda$-calculus with boolean and function types.
@@
 
-In Church's original conception, the sole purpose to types is to prevent inconsistency. People today, influenced by programming languages, prefer to give types a more dominant role.
+In Church's original conception, the sole purpose of types is to prevent inconsistency, all collections being represented as sets.
+People today, influenced by programming languages, prefer to give types a more dominant role.
+They expect to have numeric types like \isa{int}, \isa{rat}, \isa{real}, \isa{complex} and for types to play a major role in logical reasoning.
+For example, an expression like \isa{x+y} should be interpreted with respect to the types of \isa{x} and~\isa{y}.
+Type classes \cite{wenzel-type} support this sort of type-based disambiguation in a strong sense, so that \isa{x+y} refers to the correct instance of addition for its operands.
+This works for such trivialities as the basic laws for addition and multiplication (with the help of type classes for groups and rings) and for more advanced topological properties~\cite{hoelzl-filters}.
 
@@
 
-We do not use old-fashioned typeclasses, we do use modern locales.
+We do not use old-fashioned type classes, we do use modern locales.
 We encapsulated within the locale dedicated to a preasheaf of rings $\mathscr{F}$ the ring structures on the underlying sets $\mathscr{F}(U)$'s simply using the functional \textit{add\_str} (\textit{resp.} \textit{mult\_str}, \textit{zero\_str}, \textit{one\_str}) that takes an open subset $U$ and outputs the multiplication (\textit{resp.} the addition, the additive unit, the multiplicative unit) on the set $\mathscr{F}(U)$.

### 2021-04-07 article.tex
brief intro to simple type theory, Isabelle/HOL and schemes

@@
 
-Isabelle/HOL~\cite{isa-tutorial} is a proof assistant for higher-order logic: Church's simple type theory~\cite{church40}, with a number of modest extensions.
-It is therefore based on the typed $\lambda$-calculus with boolean and function types.
-A boolean-valued function is a predicate, which yields a simple typed set theory that is expressive enough to express abstract mathematics, as we shall see below.
+Isabelle/HOL~\cite{isa-tutorial} is a proof assistant for higher-order logic, Church's simple type theory~\cite{church40}, and is therefore based on the typed $\lambda$-calculus with boolean and function types.
+A boolean-valued function is a predicate, which yields a simple typed set theory that is expressive enough to express abstract mathematics, as we demonstrate below.
 
@@
 For example, an expression like \isa{x+y} should be interpreted with respect to the types of \isa{x} and~\isa{y}.
-Type classes \cite{wenzel-type} support this sort of type-based disambiguation in a strong sense, so that \isa{x+y} refers to the correct instance of addition for its operands.
-This works for such trivialities as the basic laws for addition and multiplication (with the help of type classes for groups and rings) and for more advanced topological properties~\cite{hoelzl-filters}.
+Isabelle/HOL's \emph{type classes} \cite{wenzel-type} support this sort of type-based disambiguation in a strong sense, so that \isa{x+y} refers to the correct instance of addition.
+Type classes work for such trivialities as the basic laws for addition and multiplication (with the help of type classes for groups and rings) and for more advanced topological properties~\cite{hoelzl-filters}.
+
+The drawback of type classes is simply that they refer to types.
+Mathematical constructions are generally too complex to formalise as types.
+Even the carrier of a group can be a complex object.
+One solution to this problem is to move to a stronger type system, as found in Coq or Lean, which brings issues of its own.
+Our solution is to define what we need using the naive set theory that comes with higher-order logic, through the mechanism of locales.%
+\footnote{Not to be confused with the locales of topos theory!}
+
+A locale~\cite{ballarin-locales-module} represents an Isabelle/HOL proof context.
+It can take parameters and instances of other locales.
+It can declare components constrained by assumptions.
+Thus they correspond directly to the mathematical practice of defining a monoid, say, as a tuple $(M,{\cdot},1)$ satisfying the obvious properties.
+A locale can inherit multiple instances, as when we define a monoid homomorphism with respect to two monoids.
+
+Logically, a locale is nothing but a predicate; their power comes from the mechanisms provided by Isabelle for creating locale hierarchies.
+If we work in a particular locale, we can refer to its components and assumptions.
+But we can also prove membership of a locale, which means to exhibit particular constructions---say a monoid carrier with its claimed multiplication and identity---and prove that they satisfy the locale's assumptions.
+Sublocale declarations provide a means of proving inclusions between apparently unrelated locales.
+
+We found that locales handled the definitions building up to schemes straightforwardly.
 

### 2021-04-07 article.tex
Add explanation about Lean difficulties

@@
 \end{isabelle}
-To catch on the state of the art in the Lean theorem prover, we finally prove in Isabelle that an affine scheme is a scheme and we give the example of the empty scheme $(\emptyset, \mathscr{O}_\emptyset)$, where $\mathscr{O}_\emptyset(\emptyset)$ is the zero ring $\lbrace 0 \rbrace$.
+To catch on the state of the art in \cite{schemesinLean}, we finally prove in Isabelle that an affine scheme is a scheme and we give the example of the empty scheme $(\emptyset, \mathscr{O}_\emptyset)$, where $\mathscr{O}_\emptyset(\emptyset)$ is the zero ring $\lbrace 0 \rbrace$.
 
@@
 \\
-Most importantly, our work meets the challenge of formalizing for the first time Grothendieck's schemes in a simple type theory and in doing so it demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
+Most importantly, our work meets the challenge of formalizing for the first time Grothendieck's schemes in simple type theory and in doing so it demonstrates that intricate dependencies of algebraic structures can be managed elegantly in Isabelle.
 We hope this work will help mathematicians interested in the formalization of mathematics to make a more informed decision about which systems are available to them.
@@
 \end{quote}	
-This raises the question of whether dependent types could be, at least in some situations, more of a burden than an advantage \cite{PaulsonLamport}.
-Indeed, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
+As we understand it, this difficulty basically comes from defining the sheaf structure of $\spec$ first on the basis given by the so-called \textit{basic open sets} before extending it to all open subsets.
+We did not meet this difficulty in Isabelle, since we did not follow this sheaf-on-a-basis approach and the sheaves in our library are always defined from the get-go on all open subsets instead.
+\\
+Also, Buzzard \textit{et al.} mentions another difficulty encountered when proving that an affine scheme is a scheme. 
+\begin{quote}
+	This means that rewriting the equality $\iota(U) = U$ can cause technical problems with data-carrying types such as $\mathscr{O}_X(\iota(U))$ which depends on $\iota(U)$ (although in our case they were surmountable).
+This is a technical issue with dependent type theory and can sometimes indicate that one is working with the wrong definitions.
+\cite[3.5]{schemesinLean}
+\end{quote}	
+where $\iota: \spec \rightarrow \spec$ is here simply the identity map.
+If, again, we give a slightly different formulation for the definition of a scheme, following Hartshorne \cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the definitional equality, difference which is peculiar to dependent type theories.
+\\
+If we were much more fortunate with our formalization in Isabelle, it is worth mentioning that this difficulty was eventually overcome in Lean using a trick.  
+\begin{quote}
+	Fortunately, in our case, Reid Barton pointed out the following extraordinary trick to us: we can define the map $\mathscr{O}_X(\iota(U)) \rightarrow \mathscr{O}_X(U)$ using restriction rather than trying to force it to be the identity!
+\cite[3.5.]{schemesinLean}
+\end{quote}	    
+However, all these difficulties in Lean, where three attempts at defining schemes were required, raise the question of whether dependent types could be, at least in some situations, more of a burden than an advantage \cite{PaulsonLamport}.
+Moreover, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
 A dual question is to know how deep one can go formalizing mathematics in a simple type theory.

### 2021-04-07 article.tex
Very minor update

@@
 where $\iota: \spec \rightarrow \spec$ is here simply the identity map.
-If, again, we give a slightly different formulation for the definition of a scheme, following Hartshorne \cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the definitional equality, difference which is peculiar to dependent type theories.
+If, again, we give a slightly different formulation for the definition of a scheme, following Hartshorne \cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a direct counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the definitional equality, difference which is peculiar to dependent type theories.
 \\

### 2021-04-07 article.tex
Fix a typo + very minor updates

--- 2021-04-07 article.tex
@@
 People today, influenced by programming languages, prefer to give types a more dominant role.
-They expect to have numeric types like \isa{int}, \isa{rat}, \isa{real}, \isa{complex} and for types to play a major role in logical reasoning.
+They expect to have numeric types like \isa{int}, \isa{nat}, \isa{real}, \isa{complex} and for types to play a major role in logical reasoning.
 For example, an expression like \isa{x+y} should be interpreted with respect to the types of \isa{x} and~\isa{y}.
@@
 where $\iota: \spec \rightarrow \spec$ is here simply the identity map.
-If, again, we give a slightly different formulation for the definition of a scheme, following Hartshorne \cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the definitional equality, difference which is peculiar to dependent type theories.
+If, again, we gave a slightly different formulation for the definition of a scheme, following Hartshorne \cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a direct counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the \textit{definitional equality}, difference which is peculiar to dependent type theories.
 \\

### 2021-04-07 article.tex
revisions to section 2

@@
 Type classes work for such trivialities as the basic laws for addition and multiplication (with the help of type classes for groups and rings) and for more advanced topological properties~\cite{hoelzl-filters}.
+A new type, once proved to be a topological space, instantly inherits such concepts as limits and continuity along with all theorems proved about them,
 
@@
 
-A locale~\cite{ballarin-locales-module} represents an Isabelle/HOL proof context.
+A \emph{locale}~\cite{ballarin-locales-module} represents an Isabelle/HOL proof context.
 It can take parameters and instances of other locales.
@@
 
-Logically, a locale is nothing but a predicate; their power comes from the mechanisms provided by Isabelle for creating locale hierarchies.
+Logically, a locale is nothing but a predicate; their power comes from Isabelle's mechanisms for creating, managing and using locale hierarchies.
 If we work in a particular locale, we can refer to its components and assumptions.
-But we can also prove membership of a locale, which means to exhibit particular constructions---say a monoid carrier with its claimed multiplication and identity---and prove that they satisfy the locale's assumptions.
-Sublocale declarations provide a means of proving inclusions between apparently unrelated locales.
-
-We found that locales handled the definitions building up to schemes straightforwardly.
+But we can also prove membership of a locale, which means to exhibit particular constructions---say a purported monoid carrier along with its multiplication and identity---and prove that they satisfy the locale's assumptions.
+\emph{Sublocale} declarations provide a means of proving inclusions between apparently unrelated locales.
+
+We found that locales handled the tangle of definitions building up to schemes straightforwardly.
 
@@
 For the remainder of this text fix a commutative ring $R$. \\
-The definition of an ideal of $R$ was introduced in Isabelle in \cite{ballarin-exploring}.
+The definition of an ideal of $R$ was introduced in Isabelle  by Ballarin~\cite{ballarin-exploring}.
 

### 2021-04-07 article.tex
moved some text from section 1 to section 2

@@
 
-It is well-known in the Isabelle community that the algebra library should be rebuilt from scratch.
-First, I should say the algebra libraries.
-Indeed, there are many libraries for algebra in Isabelle, the \textit{HOL-Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Algebra/index.html}} started in the previous millennium (1999), the more recent \textit{HOL-Computational\_Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Computational_Algebra/index.html}}, the oldest formalization of algebraic structures (groups, rings, modules, fields, vector spaces \dots) being found in the main library \textit{HOL}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/index.html}}, and this is in addition to some entries in the Archive of Formal Proofs\footnote{https://www.isa-afp.org/} like \textit{Groups, Rings and Modules} \cite{Group-Ring-Module-AFP} and \textit{Vector Spaces} \cite{VectorSpace-AFP} to cite a few.
-As a result, there is an important amount of duplicated code and it makes the situation unclear regarding the status of algebra for the newcomer in the Isabelle world.
-Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the modern locales, a powerful module system in Isabelle for managing theory hierarchies \cite{ballarin-locales-module}.
-Therefore, HOL-Algebra contains some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
-Indeed, this last locale uses records and there does not exist multiple inheritances for records, hence the awkward use of the ring record for abelian groups.
-However, a successful experiment was conducted recently in \cite{ballarin-exploring} showing that modern locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
-So, hopefully, the situation should dramatically improved in the near future.
-\\
-In the same time, some proof assistants have made impressive progress on the algebra front.
-Indeed, in 2003 Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
-More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover also based on a dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
+Proof assistants have made impressive progress on the formalisation of algebra.
+In 2003, Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq, which is based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
+More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover, which based on a similar dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
 \\
@@
 \end{quote}
-We should note that the Isabelle proof assistant is based on a much more minimalist type theory, known as a simple type theory.
+We should note that the Isabelle proof assistant is based on a much more minimalist type theory, known as simple type theory.
 As a consequence, many users of dependent type theories see Isabelle's type theory as a far less expressive system for formalizing advanced mathematics.
@@
 \end{quote}
-In this article we present a concise and elegant formalization of schemes in Isabelle/HOL based on state-of-the-art locales, without using any record.
+In this article we present a concise and elegant formalization of schemes in Isabelle/HOL based on state-of-the-art locales.
 Our presentation follows the classic graduate textbook of Hartshorne \cite{hartshorne}.
@@
 We found that locales handled the tangle of definitions building up to schemes straightforwardly.
+
+It is well-known in the Isabelle community that the algebra library should be rebuilt from scratch.
+First, I should say the algebra libraries.
+Indeed, there are many libraries for algebra in Isabelle, the \textit{HOL-Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Algebra/index.html}} started in the previous millennium (1999), the more recent \textit{HOL-Computational\_Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Computational_Algebra/index.html}}, the oldest formalization of algebraic structures (groups, rings, modules, fields, vector spaces \dots) being found in the main library \textit{HOL}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/index.html}}, and this is in addition to some entries in the Archive of Formal Proofs\footnote{https://www.isa-afp.org/} like \textit{Groups, Rings and Modules} \cite{Group-Ring-Module-AFP} and \textit{Vector Spaces} \cite{VectorSpace-AFP} to cite a few.
+As a result, there is an important amount of duplicated code and it makes the situation unclear regarding the status of algebra for the newcomer in the Isabelle world.
+Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the modern locales, a powerful module system in Isabelle for managing theory hierarchies \cite{ballarin-locales-module}.
+Therefore, HOL-Algebra contains some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
+Indeed, this last locale uses records and there does not exist multiple inheritances for records, hence the awkward use of the ring record for abelian groups.
+However, a successful experiment was conducted recently in \cite{ballarin-exploring} showing that modern locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
+So, hopefully, the situation should dramatically improved in the near future.
+\\
 

### 2021-04-08 article.tex
Revisions to Anthony's material on HOL-Algebra (now in section 2)

@@
 
-Isabelle/HOL~\cite{isa-tutorial} is a proof assistant for higher-order logic, Church's simple type theory~\cite{church40}, and is therefore based on the typed $\lambda$-calculus with boolean and function types.
+Isabelle/HOL~\cite{isa-tutorial} is a proof assistant for higher-order logic---Church's simple type theory~\cite{church40}---and is therefore based on the typed $\lambda$-calculus with boolean and function types.
 A boolean-valued function is a predicate, which yields a simple typed set theory that is expressive enough to express abstract mathematics, as we demonstrate below.
@@
 Even the carrier of a group can be a complex object.
-One solution to this problem is to move to a stronger type system, as found in Coq or Lean, which brings issues of its own.
+Moving to a stronger type system, as done in Coq or Lean, brings issues of its own.
 Our solution is to define what we need using the naive set theory that comes with higher-order logic, through the mechanism of locales.%
@@
 \emph{Sublocale} declarations provide a means of proving inclusions between apparently unrelated locales.
-
 We found that locales handled the tangle of definitions building up to schemes straightforwardly.
 
-It is well-known in the Isabelle community that the algebra library should be rebuilt from scratch.
-First, I should say the algebra libraries.
-Indeed, there are many libraries for algebra in Isabelle, the \textit{HOL-Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Algebra/index.html}} started in the previous millennium (1999), the more recent \textit{HOL-Computational\_Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Computational_Algebra/index.html}}, the oldest formalization of algebraic structures (groups, rings, modules, fields, vector spaces \dots) being found in the main library \textit{HOL}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/index.html}}, and this is in addition to some entries in the Archive of Formal Proofs\footnote{https://www.isa-afp.org/} like \textit{Groups, Rings and Modules} \cite{Group-Ring-Module-AFP} and \textit{Vector Spaces} \cite{VectorSpace-AFP} to cite a few.
-As a result, there is an important amount of duplicated code and it makes the situation unclear regarding the status of algebra for the newcomer in the Isabelle world.
-Second, if these formalizations constitute an impressive body of work, not without its merits, parts of it are deprecated code not using the Isar language or the modern locales, a powerful module system in Isabelle for managing theory hierarchies \cite{ballarin-locales-module}.
-Therefore, HOL-Algebra contains some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
-Indeed, this last locale uses records and there does not exist multiple inheritances for records, hence the awkward use of the ring record for abelian groups.
-However, a successful experiment was conducted recently in \cite{ballarin-exploring} showing that modern locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
-So, hopefully, the situation should dramatically improved in the near future.
-\\
+However, the right way to formalise algebra isn't obvious.
+It is well-known in the Isabelle community that the main algebra library needs to be rebuilt from scratch.
+In fact, there are many libraries for algebra in Isabelle: \textit{HOL-Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Algebra/index.html}} from the previous millennium (1999), the more recent \textit{HOL-Computational\_Algebra}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Computational_Algebra/index.html}}, and moreover some entries in the Archive of Formal Proofs\footnote{https://www.isa-afp.org/} like \textit{Groups, Rings and Modules} \cite{Group-Ring-Module-AFP} and \textit{Vector Spaces} \cite{VectorSpace-AFP} among others.
+As a result, there is a lot of overlapping material, which makes the status of algebra confusing and unclear for the newcomer in the Isabelle world.
+And while these formalizations constitute an impressive body of work, parts of it are deprecated code not using the Isar language or locales.
+
+Even using locales, we can still go wrong.
+The root of the problems in HOL-Algebra is the desire to refer to a structure such as a group with its components using a single variable, as a record data structure.
+The new (at the time) extensible records seemed perfect for the task, but.
+led to some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
+The lack of multiple inheritance for records seems to have required the awkward use of the ring record for abelian groups.
+However, Clemens Ballarin recently conducted a successful experiment \cite{ballarin-exploring} showing that  locales, without records, allow for a smooth handling of basic algebraic structures in Isabelle.
 

### 2021-04-08 article.tex
A last few tweaks

@@
 The root of the problems in HOL-Algebra is the desire to refer to a structure such as a group with its components using a single variable, as a record data structure.
-The new (at the time) extensible records seemed perfect for the task, but.
-led to some peculiarities, a notable one being its locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
+The new (at the time) extensible records seemed perfect for the task.
+But they led to some peculiarities: notably, the locale \emph{abelian\_group} (in \textit{Theory Ring}) which presents the odd twist of requiring a ring structure.
 The lack of multiple inheritance for records seems to have required the awkward use of the ring record for abelian groups.
@@
 Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/Topological_Spaces.html}} and \textit{HOL-Analysis/Abstract\_Topology}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Analysis/Abstract_Topology.html}}.
-Our new topology library is entirely built on modern locales without using type classes nor type declarations (via the \textit{typedef} command).
+Our new topology library is entirely built on modern locales without using type classes or type declarations (via the \textit{typedef} command).
 In particular, our topological spaces have explicit carrier sets as part of their data instead of using \textit{UNIV} or having to define it later as the union of all the open sets.
@@
 
-Actually, this reliance on modern locales avoiding type classes and type declarations whenever possible is present throughout our development.
-It inaugurates a new discipline of formalizing mathematics with Isabelle/HOL which is exemplary in bridging the gap between set theory and type theory within Isabelle/HOL, with the benefit of avoiding the extension of Isabelle's logic with a new rule for type definition as proposed by Kun\v{c}ar and Popescu in their types-to-sets framework \cite{typestosets}.
+Actually, this reliance on locales, avoiding type classes and type declarations whenever possible, pervades our development.
+It inaugurates a new discipline of formalizing mathematics with Isabelle/HOL which is exemplary in bridging the gap between set theory and type theory within Isabelle/HOL, while forgoing the extension of Isabelle's logic with a new rule for type definition as proposed by Kun\v{c}ar and Popescu in their types-to-sets framework \cite{typestosets}.
 \\
-The formalized material has a size of roughly 7300-line of code including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring \dots) and even our partial reconstruction of the topology library (down to the notion of a topological space).
+The formalized material has a size of roughly 7300 lines of code, including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring and much else) and even our partial reconstruction of the topology library (down to the notion of a topological space).
 Given the output of this work, a formalization of schemes in Isabelle, such a relatively short formalization conveys the power of Isabelle module systems.
@@
 
-Last, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the important difficulties he faced during his formalization in Lean:
+Last, it seems that our experience in Isabelle to formalize schemes was much smoother than the corresponding one in Lean, since Kevin Buzzard reported on his blog the serious difficulties he faced during his formalization in Lean:
 \begin{quote}
@@
 where $\iota: \spec \rightarrow \spec$ is here simply the identity map.
-If, again, we gave a slightly different formulation for the definition of a scheme, following Hartshorne \cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a direct counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the \textit{definitional equality}, difference which is peculiar to dependent type theories.
+If, again, we gave a slightly different formulation for the definition of a scheme, following Hartshorne~\cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a direct counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the \textit{definitional equality}, a difference which is peculiar to dependent type theories.
 \\
@@
 However, all these difficulties in Lean, where three attempts at defining schemes were required, raise the question of whether dependent types could be, at least in some situations, more of a burden than an advantage \cite{PaulsonLamport}.
-Moreover, in the age of machine learning one may suspect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
+Moreover, in the age of machine learning, one may expect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.
 A dual question is to know how deep one can go formalizing mathematics in a simple type theory.

### 2021-04-08 article.tex
Update
- shorten indentations
- remove one contraction
- add authorship and corresponding author
- add a few references in biblio for Coq and Lean

@@
 \subtitle{Grothendieck's Schemes in the Proof Assistant Isabelle}
-\author{}
+\author{Anthony Bordg\thanks{apdb3@cam.ac.uk} \and Lawrence Paulson \and Wenda Li}
 \date{\today}
@@
 Proof assistants have made impressive progress on the formalisation of algebra.
-In 2003, Laurent Chicli, as the topic of his PhD thesis, formalized sheaves and affine schemes in the proof assistant Coq, which is based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{chiclithesis}.
-More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard using the brave new Lean theorem prover, which based on a similar dependent type theory\footnote{\url{https://github.com/ramonfmir/lean-scheme}} \cite{schemesinLean}.
+In 2003, Laurent Chicli, as the topic of his PhD thesis \cite{chiclithesis}, formalized sheaves and affine schemes in the proof assistant Coq \cite{coqrefmanual}, which is based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{coquand1986calculus, coquand1988inductively}.
+More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard \cite{schemesinLean} using the brave new Lean theorem prover, which is based on a similar dependent type theory \cite{de2015lean}.
 \\
@@
 
-However, the right way to formalise algebra isn't obvious.
+However, the right way to formalise algebra is not obvious.
 It is well-known in the Isabelle community that the main algebra library needs to be rebuilt from scratch.
@@
 \section{Concluding Thoughts}
-\setlength{\parindent}{10ex}
+\setlength{\parindent}{5ex}
 

### 2021-04-08 article.tex
Fix a few typos

@@
 Type classes work for such trivialities as the basic laws for addition and multiplication (with the help of type classes for groups and rings) and for more advanced topological properties~\cite{hoelzl-filters}.
-A new type, once proved to be a topological space, instantly inherits such concepts as limits and continuity along with all theorems proved about them,
+A new type, once proved to be a topological space, instantly inherits such concepts as limits and continuity along with all theorems proved about them.
 
@@
 Our solution is to define what we need using the naive set theory that comes with higher-order logic, through the mechanism of locales.%
-\footnote{Not to be confused with the locales of topos theory!}
+\footnote{Not to be confused with the locales of point-free topology!}
 

### 2021-04-09 article.tex
Update bibliography
Cleaned snippets using Larry's script & fixed some bugs caused by the script.

@@
 
-\renewcommand{\thesubsection}{\arabic{subsection}}
+\renewcommand\thesubsection {\arabic{subsection}}
 %
@@
 \author{Anthony Bordg\thanks{apdb3@cam.ac.uk} \and Lawrence Paulson \and Wenda Li}
-\date{\today}
+\date\today 
 \maketitle
@@
 
-Proof assistants have made impressive progress on the formalisation of algebra.
+Proof assistants have made impressive progress on the formalisation of algebra \cite{oddorderthm}.
 In 2003, Laurent Chicli, as the topic of his PhD thesis \cite{chiclithesis}, formalized sheaves and affine schemes in the proof assistant Coq \cite{coqrefmanual}, which is based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{coquand1986calculus, coquand1988inductively}.
@@
 It can declare components constrained by assumptions.
-Thus they correspond directly to the mathematical practice of defining a monoid, say, as a tuple $(M,{\cdot},1)$ satisfying the obvious properties.
+Thus they correspond directly to the mathematical practice of defining a monoid, say, as a tuple $(M,\cdot ,1)$ satisfying the obvious properties.
 A locale can inherit multiple instances, as when we define a monoid homomorphism with respect to two monoids.
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ ideal\ {\isacharequal}{\kern0pt}\ subgroup{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}additive{\isacharunderscore}{\kern0pt}group{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}ring\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ ideal{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymlbrakk}\ a\ {\isasymin}\ R{\isacharsemicolon}{\kern0pt}\ b\ {\isasymin}\ I\ {\isasymrbrakk}\ {\isasymLongrightarrow}\ a\ {\isasymcdot}\ b\ {\isasymin}\ I{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymlbrakk}\ a\ {\isasymin}\ R{\isacharsemicolon}{\kern0pt}\ b\ {\isasymin}\ I\ {\isasymrbrakk}\ {\isasymLongrightarrow}\ b\ {\isasymcdot}\ a\ {\isasymin}\ I{\isachardoublequoteclose}
+\isacommand{locale}\ ideal\ =\ subgroup\_of\_additive\_group\_of\_ring\ +\isanewline
+\ \ \isakeyword{assumes}\ ideal:\ "\isasymlbrakk \ a\ \isasymin \ R;\ b\ \isasymin \ I\ \isasymrbrakk \ \isasymLongrightarrow \ a\ \isasymcdot \ b\ \isasymin \ I"\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "\isasymlbrakk \ a\ \isasymin \ R;\ b\ \isasymin \ I\ \isasymrbrakk \ \isasymLongrightarrow \ b\ \isasymcdot \ a\ \isasymin \ I"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}R{\isacharunderscore}{\kern0pt}R{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}ideal\ R\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
-\end{isabelle}
-
-\begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}{\isadigit{0}}{\isacharunderscore}{\kern0pt}R{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}ideal\ {\isacharbraceleft}{\kern0pt}{\isasymzero}{\isacharbraceright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ ideal\_R\_R:\ "ideal\ R\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ ideal\_0\_R:\ "ideal\ \{\isasymzero \}\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ {\isasymaa}\ {\isasymbb}\ {\isasymequiv}\ additive{\isachardot}{\kern0pt}subgroup{\isacharunderscore}{\kern0pt}generated\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharbraceleft}{\kern0pt}x{\isachardot}{\kern0pt}\ {\isasymexists}a\ b{\isachardot}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ a\ {\isasymcdot}\ b\ {\isasymand}\ a\ {\isasymin}\ {\isasymaa}\ {\isasymand}\ b\ {\isasymin}\ {\isasymbb}{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ ideal\_gen\_by\_prod\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ::\ "'a\ set\ \isasymRightarrow \ 'a\ set\ \isasymRightarrow \ 'a\ set"\isanewline
+\ \ \isakeyword{where}\ "ideal\_gen\_by\_prod\ \isasymaa \ \isasymbb \ \isasymequiv \ additive.subgroup\_generated\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \{x.\ \isasymexists a\ b.\ x\ =\ a\ \isasymcdot \ b\ \isasymand \ a\ \isasymin \ \isasymaa \ \isasymand \ b\ \isasymin \ \isasymbb \}"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}subgroup{\isacharunderscore}{\kern0pt}generated{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}ideal\ {\isasymbb}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ideal\ {\isacharparenleft}{\kern0pt}ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ {\isasymaa}\ {\isasymbb}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ ideal\_subgroup\_generated:\isanewline
+\ \ \isakeyword{assumes}\ "ideal\ \isasymaa \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "\ \isakeyword{and}\ "ideal\ \isasymbb \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "\isanewline
+\ \ \isakeyword{shows}\ "ideal\ (ideal\_gen\_by\_prod\ \isasymaa \ \isasymbb )\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}inter{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}ideal\ {\isasymbb}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ideal{\isacharunderscore}{\kern0pt}gen{\isacharunderscore}{\kern0pt}by{\isacharunderscore}{\kern0pt}prod\ {\isasymaa}\ {\isasymbb}\ {\isacharequal}{\kern0pt}\ {\isasymInter}\ {\isacharbraceleft}{\kern0pt}I{\isachardot}{\kern0pt}\ ideal\ I\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharbraceleft}{\kern0pt}a\ {\isasymcdot}\ b\ {\isacharbar}{\kern0pt}a\ b{\isachardot}{\kern0pt}\ a\ {\isasymin}\ {\isasymaa}\ {\isasymand}\ b\ {\isasymin}\ {\isasymbb}{\isacharbraceright}{\kern0pt}\ {\isasymsubseteq}\ I{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ ideal\_gen\_by\_prod\_is\_inter:\isanewline
+\ \ \isakeyword{assumes}\ "ideal\ \isasymaa \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "\ \isakeyword{and}\ "ideal\ \isasymbb \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "\isanewline
+\ \ \isakeyword{shows}\ "ideal\_gen\_by\_prod\ \isasymaa \ \isasymbb \ =\ \isasymInter \ \{I.\ ideal\ I\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymand \ \{a\ \isasymcdot \ b\ |a\ b.\ a\ \isasymin \ \isasymaa \ \isasymand \ b\ \isasymin \ \isasymbb \}\ \isasymsubseteq \ I\}"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ pr{\isacharunderscore}{\kern0pt}ideal\ {\isacharequal}{\kern0pt}\ comm{\isacharcolon}{\kern0pt}comm{\isacharunderscore}{\kern0pt}ring\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ ideal\ I\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{for}\ R\ \isakeyword{and}\ I\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ multiplication\ \isanewline
-\ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ {\isacharplus}{\kern0pt}\ \isakeyword{assumes}\ carrier{\isacharunderscore}{\kern0pt}neq{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}I\ {\isasymnoteq}\ R{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ absorbent{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymlbrakk}x\ {\isasymin}\ R{\isacharsemicolon}{\kern0pt}\ y\ {\isasymin}\ R{\isasymrbrakk}\ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}x\ {\isasymcdot}\ y\ {\isasymin}\ I{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}x\ {\isasymin}\ I\ {\isasymor}\ y\ {\isasymin}\ I{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{locale}\ pr\_ideal\ =\ comm:comm\_ring\ R\ "(+)"\ "(\isasymcdot )"\ "\isasymzero "\ "\isasymone "\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ +\ ideal\ I\ R\ "(+)"\ "(\isasymcdot )"\ "\isasymzero "\ "\isasymone "\isanewline
+\ \ \ \ \isakeyword{for}\ R\ \isakeyword{and}\ I\ \isakeyword{and}\ addition\ (\isakeyword{infixl}\ "+"\ 65)\ \isakeyword{and}\ multiplication\ \isanewline
+\ \ \ \ \ \ \ (\isakeyword{infixl}\ "\isasymcdot "\ 70)\ \isakeyword{and}\ zero\ ("\isasymzero ")\ \isakeyword{and}\ unit\ ("\isasymone ")\isanewline
+\ \ \ +\ \isakeyword{assumes}\ carrier\_neq:\ "I\ \isasymnoteq \ R"\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ absorbent:\ "\isasymlbrakk x\ \isasymin \ R;\ y\ \isasymin \ R\isasymrbrakk \ \isasymLongrightarrow \ (x\ \isasymcdot \ y\ \isasymin \ I)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ (x\ \isasymin \ I\ \isasymor \ y\ \isasymin \ I)"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ not{\isacharunderscore}{\kern0pt}{\isadigit{1}}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymone}\ {\isasymnotin}\ I{\isachardoublequoteclose}\isanewline
-\isacommand{proof}\isamarkupfalse%
-\isanewline
-\ \ \isacommand{assume}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymone}\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
-\ \ \isacommand{then}\isamarkupfalse%
-\ \isacommand{have}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymAnd}x{\isachardot}{\kern0pt}\ {\isasymlbrakk}{\isasymone}\ {\isasymin}\ I{\isacharsemicolon}{\kern0pt}\ x\ {\isasymin}\ R{\isasymrbrakk}\ {\isasymLongrightarrow}\ x\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{by}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}metis\ ideal{\isacharparenleft}{\kern0pt}{\isadigit{1}}{\isacharparenright}{\kern0pt}\ comm{\isachardot}{\kern0pt}multiplicative{\isachardot}{\kern0pt}right{\isacharunderscore}{\kern0pt}unit{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isacommand{with}\isamarkupfalse%
-\ {\isacartoucheopen}{\isasymone}\ {\isasymin}\ I{\isacartoucheclose}\ \isacommand{have}\isamarkupfalse%
-\ {\isachardoublequoteopen}I\ {\isacharequal}{\kern0pt}\ R{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
-\ \ \isacommand{then}\isamarkupfalse%
-\ \isacommand{show}\isamarkupfalse%
-\ False\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ carrier{\isacharunderscore}{\kern0pt}neq\ \isacommand{by}\isamarkupfalse%
-\ blast\isanewline
+\isacommand{lemma}\ (\isakeyword{in}\ pr\_ideal)\ not\_1:\ "\isasymone \ \isasymnotin \ I"\isanewline
+\isacommand{proof}\isanewline
+\ \ \isacommand{assume}\ "\isasymone \ \isasymin \ I"\isanewline
+\ \ \isacommand{then}\ \isacommand{have}\ "\isasymAnd x.\ \isasymlbrakk \isasymone \ \isasymin \ I;\ x\ \isasymin \ R\isasymrbrakk \ \isasymLongrightarrow \ x\ \isasymin \ I"\isanewline
+\ \ \ \ \isacommand{by}\ (metis\ ideal(1)\ comm.multiplicative.right\_unit)\isanewline
+\ \ \isacommand{with}\ \isacartoucheopen \isasymone \ \isasymin \ I\isacartoucheclose \ \isacommand{have}\ "I\ =\ R"\isanewline
+\ \ \ \ \isacommand{by}\ auto\isanewline
+\ \ \isacommand{then}\ \isacommand{show}\ False\isanewline
+\ \ \ \ \isacommand{using}\ carrier\_neq\ \isacommand{by}\ blast\isanewline
 \isacommand{qed}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ submonoid{\isacharunderscore}{\kern0pt}notin{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}S\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}x\ {\isasymin}\ R{\isachardot}{\kern0pt}\ x\ {\isasymnotin}\ I{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}submonoid\ S\ R\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymone}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ pr\_ideal)\ submonoid\_notin:\isanewline
+\ \ \isakeyword{assumes}\ "S\ =\ \{x\ \isasymin \ R.\ x\ \isasymnotin \ I\}"\isanewline
+\ \ \isakeyword{shows}\ "submonoid\ S\ R\ (\isasymcdot )\ \isasymone "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ closed{\isacharunderscore}{\kern0pt}subsets\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymV}\ {\isacharunderscore}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbrackleft}{\kern0pt}{\isadigit{9}}{\isadigit{0}}{\isadigit{0}}{\isacharbrackright}{\kern0pt}\ {\isadigit{9}}{\isadigit{0}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymV}\ {\isasymaa}\ {\isasymequiv}\ {\isacharbraceleft}{\kern0pt}I{\isachardot}{\kern0pt}\ pr{\isacharunderscore}{\kern0pt}ideal\ R\ I\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymand}\ {\isasymaa}\ {\isasymsubseteq}\ I{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ closed\_subsets\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ ::\ "'a\ set\ \isasymRightarrow \ ('a\ set)\ set"\ ("\isasymV \ \_"\ [900]\ 900)\isanewline
+\ \ \isakeyword{where}\ "\isasymV \ \isasymaa \ \isasymequiv \ \{I.\ pr\_ideal\ R\ I\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ \isasymand \ \isasymaa \ \isasymsubseteq \ I\}"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ closed{\isacharunderscore}{\kern0pt}subsets{\isacharunderscore}{\kern0pt}empty{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymV}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ Spec{\isachardoublequoteclose}
-\end{isabelle}
-
-\begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ closed{\isacharunderscore}{\kern0pt}subsets{\isacharunderscore}{\kern0pt}R{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymV}\ R\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ closed\_subsets\_empty:\ "\isasymV \ \{\}\ =\ Spec"
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ closed\_subsets\_R:\ "\isasymV \ R\ =\ \{\}"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
-\ \ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ U\ {\isasymequiv}\ generated{\isacharunderscore}{\kern0pt}topology\ Spec\ \isanewline
-\ \ \ \ \ \ \ \ {\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymexists}{\isasymaa}{\isachardot}{\kern0pt}\ ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymand}\ U\ {\isacharequal}{\kern0pt}\ Spec\ {\isacharminus}{\kern0pt}\ {\isasymV}\ {\isasymaa}{\isacharparenright}{\kern0pt}{\isacharbraceright}{\kern0pt}\ U{\isachardoublequoteclose}
-\end{isabelle}
-
-\begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ zariski{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}topological{\isacharunderscore}{\kern0pt}space{\isacharcolon}{\kern0pt}\isanewline
-\ \ {\isachardoublequoteopen}topological{\isacharunderscore}{\kern0pt}space\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open{\isachardoublequoteclose}
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ is\_zariski\_open\isanewline
+\ \ \ \ ::\ "'a\ set\ set\ \isasymRightarrow \ bool"\ \isakeyword{where}\isanewline
+\ \ "is\_zariski\_open\ U\ \isasymequiv \ generated\_topology\ Spec\ \isanewline
+\ \ \ \ \ \ \ \ \{U.\ (\isasymexists \isasymaa .\ ideal\ \isasymaa \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ \isasymand \ U\ =\ Spec\ -\ \isasymV \ \isasymaa )\}\ U"
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ zariski\_is\_topological\_space:\isanewline
+\ \ "topological\_space\ Spec\ is\_zariski\_open"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\ topological{\isacharunderscore}{\kern0pt}space\isanewline
-\ \ {\isacharplus}{\kern0pt}\ \isakeyword{fixes}\ {\isasymFF}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{and}\ {\isasymrho}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isakeyword{and}\ b{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isacharplus}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymcdot}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphism{\isacharcolon}{\kern0pt}\isanewline
-\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ V{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ V\ {\isasymLongrightarrow}\ V\ {\isasymsubseteq}\ U\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub V\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub V\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub V\isactrlesub \ {\isasymone}\isactrlbsub V\isactrlesub {\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{and}\ ring{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}empty{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymFF}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}b{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{and}\ identity{\isacharunderscore}{\kern0pt}map\ {\isacharbrackleft}{\kern0pt}simp{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ {\isasymFF}\ U\ {\isasymLongrightarrow}\ {\isasymrho}\ U\ U\ x\ {\isacharequal}{\kern0pt}\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{and}\ assoc{\isacharunderscore}{\kern0pt}comp{\isacharcolon}{\kern0pt}\ \isanewline
-\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ V\ W\ x{\isachardot}{\kern0pt}\ {\isasymlbrakk}is{\isacharunderscore}{\kern0pt}open\ U{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ V{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ W{\isacharsemicolon}{\kern0pt}V\ {\isasymsubseteq}\ U{\isacharsemicolon}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ W\ {\isasymsubseteq}\ V{\isacharsemicolon}{\kern0pt}x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isasymrbrakk}\ {\isasymLongrightarrow}\ {\isasymrho}\ U\ W\ x\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ V\ W\ {\isasymcirc}\ {\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\ x{\isachardoublequoteclose}
+\isacommand{locale}\ presheaf\_of\_rings\ =\ topological\_space\isanewline
+\ \ +\ \isakeyword{fixes}\ \isasymFF ::\ "'a\ set\ \isasymRightarrow \ 'b\ set"\isanewline
+\ \ \isakeyword{and}\ \isasymrho ::\ "'a\ set\ \isasymRightarrow \ 'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b)"\ \isakeyword{and}\ b::\ "'b"\isanewline
+\ \ \isakeyword{and}\ add\_str::\ "'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b)"\ ("+\isactrlbsub \_\isactrlesub ")\isanewline
+\ \ \isakeyword{and}\ mult\_str::\ "'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b)"\ ("\isasymcdot \isactrlbsub \_\isactrlesub ")\isanewline
+\ \ \isakeyword{and}\ zero\_str::\ "'a\ set\ \isasymRightarrow \ 'b"\ ("\isasymzero \isactrlbsub \_\isactrlesub ")\ \isanewline
+\ \ \isakeyword{and}\ one\_str::\ "'a\ set\ \isasymRightarrow \ 'b"\ ("\isasymone \isactrlbsub \_\isactrlesub ")\isanewline
+\ \ \isakeyword{assumes}\ is\_ring\_morphism:\isanewline
+\ \ \ \ "\isasymAnd U\ V.\ is\_open\ U\ \isasymLongrightarrow \ is\_open\ V\ \isasymLongrightarrow \ V\ \isasymsubseteq \ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ ring\_homomorphism\ (\isasymrho \ U\ V)\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymFF \ U)\ (+\isactrlbsub U\isactrlesub )\ (\isasymcdot \isactrlbsub U\isactrlesub )\ \isasymzero \isactrlbsub U\isactrlesub \ \isasymone \isactrlbsub U\isactrlesub \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymFF \ V)\ (+\isactrlbsub V\isactrlesub )\ (\isasymcdot \isactrlbsub V\isactrlesub )\ \isasymzero \isactrlbsub V\isactrlesub \ \isasymone \isactrlbsub V\isactrlesub "\isanewline
+\ \ \isakeyword{and}\ ring\_of\_empty:\ "\isasymFF \ \{\}\ =\ \{b\}"\isanewline
+\ \ \isakeyword{and}\ identity\_map\ [simp]:\ "\isasymAnd U.\ is\_open\ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasymAnd x.\ x\ \isasymin \ \isasymFF \ U\ \isasymLongrightarrow \ \isasymrho \ U\ U\ x\ =\ x)"\isanewline
+\ \ \isakeyword{and}\ assoc\_comp:\ \isanewline
+\ \ \ \ "\isasymAnd U\ V\ W\ x.\ \isasymlbrakk is\_open\ U;\ is\_open\ V;\ is\_open\ W;V\ \isasymsubseteq \ U;\ \isanewline
+\ \ \ \ \ \ \ \ \ W\ \isasymsubseteq \ V;x\ \isasymin \ (\isasymFF \ U)\isasymrbrakk \ \isasymLongrightarrow \ \isasymrho \ U\ W\ x\ =\ (\isasymrho \ V\ W\ \isasymcirc \ \isasymrho \ U\ V)\ x"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}from{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}homomorphism{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ U{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ U{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ring\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub {\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ presheaf\_of\_rings)\ is\_ring\_from\_is\_homomorphism:\isanewline
+\ \ \isakeyword{fixes}\ U::\ "'a\ set"\isanewline
+\ \ \isakeyword{assumes}\ "is\_open\ U"\isanewline
+\ \ \isakeyword{shows}\ "ring\ (\isasymFF \ U)\ (+\isactrlbsub U\isactrlesub )\ (\isasymcdot \isactrlbsub U\isactrlesub )\ \isasymzero \isactrlbsub U\isactrlesub \ \isasymone \isactrlbsub U\isactrlesub "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\isanewline
-\ \ \ \ source{\isacharcolon}{\kern0pt}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\isanewline
-\ \ {\isacharplus}{\kern0pt}\ target{\isacharcolon}{\kern0pt}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\isanewline
-\ \ \isakeyword{for}\ X\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isanewline
-\ \ \ \ \isakeyword{and}\ {\isasymFF}\ \isakeyword{and}\ {\isasymrho}\ \isakeyword{and}\ b\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isacharplus}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymcdot}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ {\isasymFF}{\isacharprime}{\kern0pt}\ \isakeyword{and}\ {\isasymrho}{\isacharprime}{\kern0pt}\ \isakeyword{and}\ b{\isacharprime}{\kern0pt}\ \isanewline
-\ \ \ \ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub {\isacharunderscore}{\kern0pt}\isactrlesub {\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ fam{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphism{\isacharcolon}{\kern0pt}\ \isanewline
-\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ {\isacharparenleft}{\kern0pt}fam{\isacharunderscore}{\kern0pt}morphisms\ U{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymFF}{\isacharprime}{\kern0pt}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub \ {\isasymone}{\isacharprime}{\kern0pt}\isactrlbsub U\isactrlesub {\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ comm{\isacharunderscore}{\kern0pt}diagrams{\isacharcolon}{\kern0pt}\ \isanewline
-\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ V\ x{\isachardot}{\kern0pt}\ {\isasymlbrakk}is{\isacharunderscore}{\kern0pt}open\ U{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ V{\isacharsemicolon}{\kern0pt}\ V\ {\isasymsubseteq}\ U{\isacharsemicolon}{\kern0pt}x\ {\isasymin}\ {\isasymFF}\ U\ {\isasymrbrakk}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymrho}{\isacharprime}{\kern0pt}\ U\ V\ {\isasymcirc}\ fam{\isacharunderscore}{\kern0pt}morphisms\ U{\isacharparenright}{\kern0pt}\ x\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fam{\isacharunderscore}{\kern0pt}morphisms\ V\ {\isasymcirc}\ {\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\ x{\isachardoublequoteclose}
+\isacommand{locale}\ morphism\_presheaves\_of\_rings\ =\isanewline
+\ \ \ \ source:\ presheaf\_of\_rings\ X\ is\_open\ \isasymFF \ \isasymrho \ b\ add\_str\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_str\ zero\_str\ one\_str\isanewline
+\ \ +\ target:\ presheaf\_of\_rings\ X\ is\_open\ \isasymFF '\ \isasymrho '\ b'\ add\_str'\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_str'\ zero\_str'\ one\_str'\isanewline
+\ \ \isakeyword{for}\ X\ \isakeyword{and}\ is\_open\isanewline
+\ \ \ \ \isakeyword{and}\ \isasymFF \ \isakeyword{and}\ \isasymrho \ \isakeyword{and}\ b\ \isakeyword{and}\ add\_str\ ("+\isactrlbsub \_\isactrlesub ")\ \isanewline
+\ \ \ \ \isakeyword{and}\ mult\_str\ ("\isasymcdot \isactrlbsub \_\isactrlesub ")\ \isakeyword{and}\ zero\_str\ ("\isasymzero \isactrlbsub \_\isactrlesub ")\ \isanewline
+\ \ \ \ \isakeyword{and}\ one\_str\ ("\isasymone \isactrlbsub \_\isactrlesub ")\ \isakeyword{and}\ \isasymFF '\ \isakeyword{and}\ \isasymrho '\ \isakeyword{and}\ b'\ \isanewline
+\ \ \ \ \isakeyword{and}\ add\_str'\ ("+'{\kern0pt}'\isactrlbsub \_\isactrlesub ")\ \isakeyword{and}\ mult\_str'\ ("\isasymcdot '{\kern0pt}'\isactrlbsub \_\isactrlesub ")\isanewline
+\ \ \ \ \isakeyword{and}\ zero\_str'\ ("\isasymzero '{\kern0pt}'\isactrlbsub \_\isactrlesub ")\ \isakeyword{and}\ one\_str'\ ("\isasymone '{\kern0pt}'\isactrlbsub \_\isactrlesub ")\ +\isanewline
+\ \ \isakeyword{fixes}\ fam\_morphisms::\ "'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'c)"\isanewline
+\ \ \isakeyword{assumes}\ is\_ring\_morphism:\ \isanewline
+\ \ \ \ "\isasymAnd U.\ is\_open\ U\ \isasymLongrightarrow \ ring\_homomorphism\ (fam\_morphisms\ U)\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymFF \ U)\ (+\isactrlbsub U\isactrlesub )\ (\isasymcdot \isactrlbsub U\isactrlesub )\ \isasymzero \isactrlbsub U\isactrlesub \ \isasymone \isactrlbsub U\isactrlesub \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymFF '\ U)\ (+'\isactrlbsub U\isactrlesub )\ (\isasymcdot '\isactrlbsub U\isactrlesub )\ \isasymzero '\isactrlbsub U\isactrlesub \ \isasymone '\isactrlbsub U\isactrlesub "\isanewline
+\ \ \ \ \isakeyword{and}\ comm\_diagrams:\ \isanewline
+\ \ \ \ "\isasymAnd U\ V\ x.\ \isasymlbrakk is\_open\ U;\ is\_open\ V;\ V\ \isasymsubseteq \ U;x\ \isasymin \ \isasymFF \ U\ \isasymrbrakk \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasymrho '\ U\ V\ \isasymcirc \ fam\_morphisms\ U)\ x\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ =\ (fam\_morphisms\ V\ \isasymcirc \ \isasymrho \ U\ V)\ x"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ comp{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}presheaves{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ b\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isasymFF}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ b{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isasymphi}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\isanewline
-\ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isasymFF}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymphi}{\isacharprime}{\kern0pt}\ U\ {\isasymcirc}\ {\isasymphi}\ U\ {\isasymdown}\ {\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{lemma}\ comp\_of\_presheaves:\isanewline
+\ \ \isakeyword{assumes}\ "morphism\_presheaves\_of\_rings\ X\ is\_open\ \isasymFF \ \isasymrho \ b\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ add\_str\ mult\_str\ zero\_str\ one\_str\ \isasymFF '\ \isasymrho '\ b'\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ add\_str'\ mult\_str'\ zero\_str'\ one\_str'\ \isasymphi "\isanewline
+\ \ \ \ \isakeyword{and}\ "morphism\_presheaves\_of\_rings\ X\ is\_open\ \isasymFF '\ \isasymrho '\ b'\isanewline
+\ \ \ \ \ \ \ \ \ \ add\_str'\ mult\_str'\ zero\_str'\ one\_str'\ \isasymFF '{\kern0pt}'\ \isasymrho '{\kern0pt}'\ \isanewline
+\ \ \ \ \ \ \ \ \ \ b'{\kern0pt}'\ add\_str'{\kern0pt}'\ mult\_str'{\kern0pt}'\ zero\_str'{\kern0pt}'\ one\_str'{\kern0pt}'\ \isasymphi '"\isanewline
+\ \ \isakeyword{shows}\ "morphism\_presheaves\_of\_rings\ X\ is\_open\ \isasymFF \ \isasymrho \ b\ add\_str\isanewline
+\ \ \ \ \ \ mult\_str\ zero\_str\ one\_str\ \isasymFF '{\kern0pt}'\ \isasymrho '{\kern0pt}'\ b'{\kern0pt}'\ add\_str'{\kern0pt}'\ \isanewline
+\ \ \ \ \ \ mult\_str'{\kern0pt}'\ zero\_str'{\kern0pt}'\ one\_str'{\kern0pt}'\ (\isasymlambda U.\ (\isasymphi '\ U\ \isasymcirc \ \isasymphi \ U\ \isasymdown \ \isasymFF \ U))"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ iso{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ \isanewline
-\ \ {\isacharequal}{\kern0pt}\ mor{\isacharcolon}{\kern0pt}morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\ \isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}inv{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymexists}{\isasympsi}{\isachardot}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ X\ is{\isacharunderscore}{\kern0pt}open\ \isanewline
-\ \ \ \ {\isasymFF}{\isacharprime}{\kern0pt}\ {\isasymrho}{\isacharprime}{\kern0pt}\ b{\isacharprime}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}str{\isacharprime}{\kern0pt}\ {\isasymFF}\ {\isasymrho}\ b\ \isanewline
-\ \ \ \ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isasympsi}\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ \isanewline
-\ \ \ \ \ \ \ \ \ \ {\isasymlongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymforall}x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}{\isacharprime}{\kern0pt}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fam{\isacharunderscore}{\kern0pt}morphisms\ U\ {\isasymcirc}\ {\isasympsi}\ U{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ x{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasympsi}\ U\ {\isasymcirc}\ fam{\isacharunderscore}{\kern0pt}morphisms\ U{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ x{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{locale}\ iso\_presheaves\_of\_rings\ \isanewline
+\ \ =\ mor:morphism\_presheaves\_of\_rings\ +\ \isanewline
+\ \ \isakeyword{assumes}\ is\_inv:\ "\isasymexists \isasympsi .\ morphism\_presheaves\_of\_rings\ X\ is\_open\ \isanewline
+\ \ \ \ \isasymFF '\ \isasymrho '\ b'\ add\_str'\ mult\_str'\ zero\_str'\ one\_str'\ \isasymFF \ \isasymrho \ b\ \isanewline
+\ \ \ \ add\_str\ mult\_str\ zero\_str\ one\_str\ \isasympsi \ \isasymand \ (\isasymforall U.\ is\_open\ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isasymlongrightarrow \ (\isasymforall x\ \isasymin \ (\isasymFF '\ U).\ (fam\_morphisms\ U\ \isasymcirc \ \isasympsi \ U)\ x\ =\ x)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymand \ (\isasymforall x\ \isasymin \ (\isasymFF \ U).\ (\isasympsi \ U\ \isasymcirc \ fam\_morphisms\ U)\ x\ =\ x))"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\ presheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ locality{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U\ I\ V\ s{\isachardot}{\kern0pt}\ open{\isacharunderscore}{\kern0pt}cover{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}open{\isacharunderscore}{\kern0pt}subset\ S\ \isanewline
-\ \ \ \ \ \ \ \ \ \ is{\isacharunderscore}{\kern0pt}open\ U\ I\ V\ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymLongrightarrow}\ V\ i\ {\isasymsubseteq}\ U{\isacharparenright}{\kern0pt}\ {\isasymLongrightarrow}\ s\ {\isasymin}\ {\isasymFF}\ U\isanewline
-\ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymLongrightarrow}\ {\isasymrho}\ U\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\ s\ {\isacharequal}{\kern0pt}\ {\isasymzero}\isactrlbsub {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymLongrightarrow}\ s\ {\isacharequal}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub {\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ glueing{\isacharcolon}{\kern0pt}\ \ \isanewline
-\ \ \ \ \ \ {\isachardoublequoteopen}{\isasymAnd}U\ I\ V\ s{\isachardot}{\kern0pt}\ open{\isacharunderscore}{\kern0pt}cover{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}open{\isacharunderscore}{\kern0pt}subset\ S\ is{\isacharunderscore}{\kern0pt}open\ U\ I\ V\ \isanewline
-\ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymforall}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymlongrightarrow}\ V\ i\ {\isasymsubseteq}\ U\ {\isasymand}\ s\ i\ {\isasymin}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}i\ j{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymLongrightarrow}\ j{\isasymin}I\ {\isasymLongrightarrow}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}V\ i\ {\isasyminter}\ V\ j{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s\ i{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharequal}{\kern0pt}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}V\ j{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}V\ i\ {\isasyminter}\ V\ j{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s\ j{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymexists}t{\isachardot}{\kern0pt}\ t\ {\isasymin}\ {\isasymFF}\ U\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}i{\isachardot}{\kern0pt}\ i{\isasymin}I\ {\isasymlongrightarrow}\ {\isasymrho}\ U\ {\isacharparenleft}{\kern0pt}V\ i{\isacharparenright}{\kern0pt}\ t\ {\isacharequal}{\kern0pt}\ s\ i{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{locale}\ sheaf\_of\_rings\ =\ presheaf\_of\_rings\ +\isanewline
+\ \ \isakeyword{assumes}\ locality:\ "\isasymAnd U\ I\ V\ s.\ open\_cover\_of\_open\_subset\ S\ \isanewline
+\ \ \ \ \ \ \ \ \ \ is\_open\ U\ I\ V\ \isasymLongrightarrow \ (\isasymAnd i.\ i\isasymin I\ \isasymLongrightarrow \ V\ i\ \isasymsubseteq \ U)\ \isasymLongrightarrow \ s\ \isasymin \ \isasymFF \ U\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasymAnd i.\ i\isasymin I\ \isasymLongrightarrow \ \isasymrho \ U\ (V\ i)\ s\ =\ \isasymzero \isactrlbsub (V\ i)\isactrlesub )\ \isasymLongrightarrow \ s\ =\ \isasymzero \isactrlbsub U\isactrlesub "\isanewline
+\ \ \ \ \isakeyword{and}\ glueing:\ \ \isanewline
+\ \ \ \ \ \ "\isasymAnd U\ I\ V\ s.\ open\_cover\_of\_open\_subset\ S\ is\_open\ U\ I\ V\ \isanewline
+\ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasymforall i.\ i\isasymin I\ \isasymlongrightarrow \ V\ i\ \isasymsubseteq \ U\ \isasymand \ s\ i\ \isasymin \ \isasymFF \ (V\ i))\ \isanewline
+\ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasymAnd i\ j.\ i\isasymin I\ \isasymLongrightarrow \ j\isasymin I\ \isasymLongrightarrow \ \isasymrho \ (V\ i)\ (V\ i\ \isasyminter \ V\ j)\ (s\ i)\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ =\ \isasymrho \ (V\ j)\ (V\ i\ \isasyminter \ V\ j)\ (s\ j))\ \isanewline
+\ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasymexists t.\ t\ \isasymin \ \isasymFF \ U\ \isasymand \ (\isasymforall i.\ i\isasymin I\ \isasymlongrightarrow \ \isasymrho \ U\ (V\ i)\ t\ =\ s\ i))"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ morphism{\isacharunderscore}{\kern0pt}sheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}presheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings
+\isacommand{locale}\ morphism\_sheaves\_of\_rings\ =\ morphism\_presheaves\_of\_rings
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}sheaf\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ U{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}open{\isacharunderscore}{\kern0pt}subset{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ U{\isachardoublequoteclose}\isanewline
+\isacommand{locale}\ ind\_sheaf\ =\ sheaf\_of\_rings\ +\isanewline
+\ \ \isakeyword{fixes}\ U::\ "'a\ set"\isanewline
+\ \ \isakeyword{assumes}\ is\_open\_subset:\ "is\_open\ U"\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ it{\isacharcolon}{\kern0pt}\ ind{\isacharunderscore}{\kern0pt}topology\ S\ is{\isacharunderscore}{\kern0pt}open\ U\isanewline
-
-\isacommand{definition}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}sheaf\ V\ {\isasymequiv}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms\ V\ W\ {\isasymequiv}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ W{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isacharplus}{\kern0pt}\isactrlbsub {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isasymcdot}\isactrlbsub {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymzero}\isactrlbsub {\isacharparenleft}{\kern0pt}U{\isasyminter}V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str\ V\ {\isasymequiv}\ {\isasymone}\isactrlbsub {\isacharparenleft}{\kern0pt}U{\isasyminter}V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
-\ \ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ U\ it{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}open\ ind{\isacharunderscore}{\kern0pt}sheaf\ ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ b\ ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str\ ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str\ ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str\ ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str{\isachardoublequoteclose}\isanewline
+\isacommand{interpretation}\ it:\ ind\_topology\ S\ is\_open\ U\isanewline
+
+\isacommand{definition}\ ind\_sheaf::\ "'a\ set\ \isasymRightarrow \ 'b\ set"\isanewline
+\ \ \isakeyword{where}\ "ind\_sheaf\ V\ \isasymequiv \ \isasymFF \ (U\ \isasyminter \ V)"\isanewline
+\isanewline
+\isacommand{definition}\ ind\_ring\_morphisms::\ "'a\ set\ \isasymRightarrow \ 'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b)"\isanewline
+\ \ \isakeyword{where}\ "ind\_ring\_morphisms\ V\ W\ \isasymequiv \ \isasymrho \ (U\ \isasyminter \ V)\ (U\ \isasyminter \ W)"\isanewline
+\isanewline
+\isacommand{definition}\ ind\_add\_str::\ "'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b)"\isanewline
+\ \ \isakeyword{where}\ "ind\_add\_str\ V\ \isasymequiv \ \isasymlambda x\ y.\ +\isactrlbsub (U\ \isasyminter \ V)\isactrlesub \ x\ y"\isanewline
+\isanewline
+\isacommand{definition}\ ind\_mult\_str::\ "'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b)"\isanewline
+\ \ \isakeyword{where}\ "ind\_mult\_str\ V\ \isasymequiv \ \isasymlambda x\ y.\ \isasymcdot \isactrlbsub (U\ \isasyminter \ V)\isactrlesub \ x\ y"\isanewline
+\isanewline
+\isacommand{definition}\ ind\_zero\_str::\ "'a\ set\ \isasymRightarrow \ 'b"\isanewline
+\ \ \isakeyword{where}\ "ind\_zero\_str\ V\ \isasymequiv \ \isasymzero \isactrlbsub (U\isasyminter V)\isactrlesub "\isanewline
+\isanewline
+\isacommand{definition}\ ind\_one\_str::\ "'a\ set\ \isasymRightarrow \ 'b"\isanewline
+\ \ \isakeyword{where}\ "ind\_one\_str\ V\ \isasymequiv \ \isasymone \isactrlbsub (U\isasyminter V)\isactrlesub "\isanewline
+\isanewline
+\isacommand{lemma}\ ind\_sheaf\_is\_sheaf:\isanewline
+\ \ "sheaf\_of\_rings\ U\ it.ind\_is\_open\ ind\_sheaf\ ind\_ring\_morphisms\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ b\ ind\_add\_str\ ind\_mult\_str\ ind\_zero\_str\ ind\_one\_str"\isanewline
 
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ im{\isacharunderscore}{\kern0pt}sheaf\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\ continuous{\isacharunderscore}{\kern0pt}map\isanewline
+\isacommand{locale}\ im\_sheaf\ =\ sheaf\_of\_rings\ +\ continuous\_map\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{definition}\isamarkupfalse%
-\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isacharequal}{\kern0pt}{\isachargreater}{\kern0pt}\ {\isacharprime}{\kern0pt}b\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}im{\isacharunderscore}{\kern0pt}sheaf\ V\ {\isasymequiv}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\ U\ V\ {\isasymequiv}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V\ x\ y{\isachardot}{\kern0pt}\ {\isacharplus}{\kern0pt}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V\ x\ y{\isachardot}{\kern0pt}\ {\isasymcdot}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub \ x\ y{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V{\isachardot}{\kern0pt}\ {\isasymzero}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymequiv}\ {\isasymlambda}V{\isachardot}{\kern0pt}\ {\isasymone}\isactrlbsub {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ S\ V{\isacharparenright}{\kern0pt}\isactrlesub {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
-\ \ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ S{\isacharprime}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open{\isacharprime}{\kern0pt}\ im{\isacharunderscore}{\kern0pt}sheaf\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\ b\isanewline
-\ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf{\isachardoublequoteclose}\isanewline
+\isacommand{definition}\ im\_sheaf::\ "'c\ set\ =>\ 'b\ set"\isanewline
+\ \ \isakeyword{where}\ "im\_sheaf\ V\ \isasymequiv \ \isasymFF \ (f\isactrlsup \isasyminverse \ S\ V)"\isanewline
+\isanewline
+\isacommand{definition}\ im\_sheaf\_morphisms::\ "'c\ set\ \isasymRightarrow \ 'c\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'b)"\isanewline
+\ \ \isakeyword{where}\ "im\_sheaf\_morphisms\ U\ V\ \isasymequiv \ \isasymrho \ (f\isactrlsup \isasyminverse \ S\ U)\ (f\isactrlsup \isasyminverse \ S\ V)"\isanewline
+\isanewline
+\isacommand{definition}\ add\_im\_sheaf::\ "'c\ set\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b"\isanewline
+\ \ \isakeyword{where}\ "add\_im\_sheaf\ \isasymequiv \ \isasymlambda V\ x\ y.\ +\isactrlbsub (f\isactrlsup \isasyminverse \ S\ V)\isactrlesub \ x\ y"\isanewline
+\isanewline
+\isacommand{definition}\ mult\_im\_sheaf::\ "'c\ set\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b\ \isasymRightarrow \ 'b"\isanewline
+\ \ \isakeyword{where}\ "mult\_im\_sheaf\ \isasymequiv \ \isasymlambda V\ x\ y.\ \isasymcdot \isactrlbsub (f\isactrlsup \isasyminverse \ S\ V)\isactrlesub \ x\ y"\isanewline
+\isanewline
+\isacommand{definition}\ zero\_im\_sheaf::\ "'c\ set\ \isasymRightarrow \ 'b"\isanewline
+\ \ \isakeyword{where}\ "zero\_im\_sheaf\ \isasymequiv \ \isasymlambda V.\ \isasymzero \isactrlbsub (f\isactrlsup \isasyminverse \ S\ V)\isactrlesub "\isanewline
+\isanewline
+\isacommand{definition}\ one\_im\_sheaf::\ "'c\ set\ \isasymRightarrow \ 'b"\isanewline
+\ \ \isakeyword{where}\ "one\_im\_sheaf\ \isasymequiv \ \isasymlambda V.\ \isasymone \isactrlbsub (f\isactrlsup \isasyminverse \ S\ V)\isactrlesub "\isanewline
+\isanewline
+\isacommand{lemma}\ im\_sheaf\_is\_sheaf:\isanewline
+\ \ "sheaf\_of\_rings\ S'\ is\_open'\ im\_sheaf\ im\_sheaf\_morphisms\ b\isanewline
+\ \ \ \ \ \ \ \ \ \ add\_im\_sheaf\ mult\_im\_sheaf\ zero\_im\_sheaf\ one\_im\_sheaf"\isanewline
 \isacommand{end}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ quotient{\isacharunderscore}{\kern0pt}ring\ {\isacharequal}{\kern0pt}\ comm{\isacharcolon}{\kern0pt}comm{\isacharunderscore}{\kern0pt}ring\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ submonoid\ S\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \ \ \isakeyword{for}\ S\ \isakeyword{and}\ R\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \isakeyword{and}\ multiplication\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
+\isacommand{locale}\ quotient\_ring\ =\ comm:comm\_ring\ R\ "(+)"\ "(\isasymcdot )"\ "\isasymzero "\ "\isasymone "\ \isanewline
+\ \ \ \ \ \ \ \ \ \ +\ submonoid\ S\ R\ "(\isasymcdot )"\ "\isasymone "\isanewline
+\ \ \ \ \ \ \isakeyword{for}\ S\ \isakeyword{and}\ R\ \isakeyword{and}\ addition\ (\isakeyword{infixl}\ "+"\ 65)\ \isanewline
+\ \ \ \ \ \ \ \ \isakeyword{and}\ multiplication\ (\isakeyword{infixl}\ "\isasymcdot "\ 70)\ \isakeyword{and}\ zero\ ("\isasymzero ")\ \isakeyword{and}\ unit\ ("\isasymone ")\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{definition}\isamarkupfalse%
-\ rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infix}\ {\isachardoublequoteopen}{\isasymsim}{\isachardoublequoteclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isasymsim}\ y\ {\isasymequiv}\ {\isasymexists}s{\isadigit{1}}{\isachardot}{\kern0pt}\ s{\isadigit{1}}\ {\isasymin}\ S\ {\isasymand}\ s{\isadigit{1}}\ {\isasymcdot}\ {\isacharparenleft}{\kern0pt}snd\ y\ {\isasymcdot}\ fst\ x\ {\isacharminus}{\kern0pt}\ snd\ x\ {\isasymcdot}\ fst\ y{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isasymzero}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ rel{\isacharcolon}{\kern0pt}\ equivalence\ {\isachardoublequoteopen}R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}{\isacharparenleft}{\kern0pt}x{\isacharcomma}{\kern0pt}y{\isacharparenright}{\kern0pt}\ {\isasymin}\ {\isacharparenleft}{\kern0pt}R{\isasymtimes}S{\isacharparenright}{\kern0pt}{\isasymtimes}{\isacharparenleft}{\kern0pt}R{\isasymtimes}S{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ x\ {\isasymsim}\ y{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ frac{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}{\isacharslash}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}r\ {\isacharslash}{\kern0pt}\ s\ {\isasymequiv}\ rel{\isachardot}{\kern0pt}Class\ {\isacharparenleft}{\kern0pt}r{\isacharcomma}{\kern0pt}\ s{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ add{\isacharunderscore}{\kern0pt}rel{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharcomma}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharcomma}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}r{\isacharslash}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharslash}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isasymcdot}s{\isacharprime}{\kern0pt}\ {\isacharplus}{\kern0pt}\ r{\isacharprime}{\kern0pt}{\isasymcdot}s{\isacharparenright}{\kern0pt}\ {\isacharslash}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isasymcdot}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ mult{\isacharunderscore}{\kern0pt}rel{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharcomma}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharcomma}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymin}\ R\ {\isasymtimes}\ S{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}r{\isacharslash}{\kern0pt}s{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isacharprime}{\kern0pt}{\isacharslash}{\kern0pt}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}r{\isasymcdot}\ r{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharslash}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isasymcdot}s{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
-\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ zero{\isacharunderscore}{\kern0pt}rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
-\ \ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}rel\ {\isacharequal}{\kern0pt}\ frac\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ one{\isacharunderscore}{\kern0pt}rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
-\ \ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}rel\ {\isacharequal}{\kern0pt}\ frac\ {\isasymone}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{sublocale}\isamarkupfalse%
-\ comm{\isacharunderscore}{\kern0pt}ring\ carrier{\isacharunderscore}{\kern0pt}quotient{\isacharunderscore}{\kern0pt}ring\ add{\isacharunderscore}{\kern0pt}rel\ mult{\isacharunderscore}{\kern0pt}rel\ zero{\isacharunderscore}{\kern0pt}rel\ one{\isacharunderscore}{\kern0pt}rel\isanewline
+\isacommand{definition}\ rel::\ "('a\ \isasymtimes \ 'a)\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ \isasymRightarrow \ bool"\ (\isakeyword{infix}\ "\isasymsim "\ 80)\isanewline
+\ \ \isakeyword{where}\ "x\ \isasymsim \ y\ \isasymequiv \ \isasymexists s1.\ s1\ \isasymin \ S\ \isasymand \ s1\ \isasymcdot \ (snd\ y\ \isasymcdot \ fst\ x\ -\ snd\ x\ \isasymcdot \ fst\ y)\ =\ \isasymzero "\isanewline
+\isanewline
+\isacommand{interpretation}\ rel:\ equivalence\ "R\ \isasymtimes \ S"\ "\{(x,y)\ \isasymin \ (R\isasymtimes S)\isasymtimes (R\isasymtimes S).\ x\ \isasymsim \ y\}"\isanewline
+\isanewline
+\isacommand{definition}\ frac::\ "'a\ \isasymRightarrow \ 'a\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set"\ (\isakeyword{infixl}\ "'/"\ 75)\isanewline
+\ \ \isakeyword{where}\ "r\ /\ s\ \isasymequiv \ rel.Class\ (r,\ s)"\isanewline
+\isanewline
+\isacommand{lemma}\ add\_rel\_frac:\isanewline
+\ \ \isakeyword{assumes}\ "(r,s)\ \isasymin \ R\ \isasymtimes \ S"\ \isakeyword{and}\ "(r',s')\isasymin \ R\ \isasymtimes \ S"\isanewline
+\ \ \isakeyword{shows}\ "add\_rel\ (r/s)\ (r'/s')\ =\ (r\isasymcdot s'\ +\ r'\isasymcdot s)\ /\ (s\isasymcdot s')"
+\isanewline
+\isanewline
+\isacommand{lemma}\ mult\_rel\_frac:\isanewline
+\ \ \isakeyword{assumes}\ "(r,s)\ \isasymin \ R\ \isasymtimes \ S"\ \isakeyword{and}\ "(r',s')\isasymin \ R\ \isasymtimes \ S"\isanewline
+\ \ \isakeyword{shows}\ "mult\_rel\ (r/s)\ (r'/s')\ =\ (r\isasymcdot \ r')\ /\ (s\isasymcdot s')"
+\isanewline
+\isanewline
+\isacommand{definition}\ zero\_rel::"('a\ \isasymtimes \ 'a)\ set"\ \isakeyword{where}\isanewline
+\ \ "zero\_rel\ =\ frac\ \isasymzero \ \isasymone "\isanewline
+\isanewline
+\isacommand{definition}\ one\_rel::"('a\ \isasymtimes \ 'a)\ set"\ \isakeyword{where}\isanewline
+\ \ "one\_rel\ =\ frac\ \isasymone \ \isasymone "\isanewline
+\isanewline
+\isacommand{sublocale}\ comm\_ring\ carrier\_quotient\_ring\ add\_rel\ mult\_rel\ zero\_rel\ one\_rel\isanewline
 \isanewline
@@
 \begin{isabelle}
-\isacommand{context}\isamarkupfalse%
-\ pr{\isacharunderscore}{\kern0pt}ideal\isanewline
+\isacommand{context}\ pr\_ideal\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ submonoid{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}submonoid\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\isacommand{proof}\isamarkupfalse%
-\isanewline
-\ \ \isacommand{show}\isamarkupfalse%
-\ {\isachardoublequoteopen}a\ {\isasymcdot}\ b\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ \isakeyword{if}\ {\isachardoublequoteopen}a\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ {\isachardoublequoteopen}b\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ \isakeyword{for}\ a\ b\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ that\ \isacommand{by}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}metis\ Diff{\isacharunderscore}{\kern0pt}iff\ absorbent\ comm{\isachardot}{\kern0pt}multiplicative{\isachardot}{\kern0pt}composition{\isacharunderscore}{\kern0pt}closed{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isacommand{show}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymone}\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isacommand{using}\isamarkupfalse%
-\ ideal{\isachardot}{\kern0pt}ideal{\isacharparenleft}{\kern0pt}{\isadigit{2}}{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}axioms\ pr{\isacharunderscore}{\kern0pt}ideal{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}neq\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharunderscore}{\kern0pt}axioms\ \isanewline
-\ \ \ \ \isacommand{by}\isamarkupfalse%
-\ fastforce\isanewline
-\isacommand{qed}\isamarkupfalse%
-\ auto%
-\isanewline
-\isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ local{\isacharcolon}{\kern0pt}quotient{\isacharunderscore}{\kern0pt}ring\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}\isanewline
-\ \ \isacommand{apply}\isamarkupfalse%
-\ intro{\isacharunderscore}{\kern0pt}locales\isanewline
-\ \ \isacommand{by}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}meson\ submonoid{\isacharunderscore}{\kern0pt}def\ submonoid{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}%
-
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}\isactrlsup {\isasyminverse}\ R\isactrlbsub {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ uminus{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}uminus{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}uminus{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
+\isacommand{lemma}\ submonoid\_pr\_ideal:\isanewline
+\ \ \isakeyword{shows}\ "submonoid\ (R\ \isasymsetminus \ I)\ R\ (\isasymcdot )\ \isasymone "\isanewline
+\isacommand{proof}\isanewline
+\ \ \isacommand{show}\ "a\ \isasymcdot \ b\ \isasymin \ R\isasymsetminus I"\ \isakeyword{if}\ "a\ \isasymin \ R\isasymsetminus I"\ "b\ \isasymin \ R\isasymsetminus I"\ \isakeyword{for}\ a\ b\isanewline
+\ \ \ \ \isacommand{using}\ that\ \isacommand{by}\ (metis\ Diff\_iff\ absorbent\ comm.multiplicative.composition\_closed)\isanewline
+\ \ \isacommand{show}\ "\isasymone \ \isasymin \ R\isasymsetminus I"\isanewline
+\ \ \ \ \isacommand{using}\ ideal.ideal(2)\ ideal\_axioms\ pr\_ideal.carrier\_neq\ pr\_ideal\_axioms\ \isanewline
+\ \ \ \ \isacommand{by}\ fastforce\isanewline
+\isacommand{qed}\ auto%
+\isanewline
+\isanewline
+\isacommand{interpretation}\ local:quotient\_ring\ "(R\ \isasymsetminus \ I)"\ R\ "(+)"\ "(\isasymcdot )"\ \isasymzero \ \isasymone \isanewline
+\ \ \isacommand{apply}\ intro\_locales\isanewline
+\ \ \isacommand{by}\ (meson\ submonoid\_def\ submonoid\_pr\_ideal)
+
+\isanewline
+\isacommand{definition}\ carrier\_local\_ring\_at::\ "('a\ \isasymtimes \ 'a)\ set\ set"\isanewline
+\ \ \isakeyword{where}\ "carrier\_local\_ring\_at\ \isasymequiv \ (R\ \isasymsetminus \ I)\isactrlsup \isasyminverse \ R\isactrlbsub (+)\ (\isasymcdot )\ \isasymzero \isactrlesub "\isanewline
+\isanewline
+\isacommand{definition}\ add\_local\_ring\_at::\ "('a\ \isasymtimes \ 'a)\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set"\isanewline
+\ \ \isakeyword{where}\ "add\_local\_ring\_at\ \isasymequiv \ local.add\_rel\ "\isanewline
+\isanewline
+\isacommand{definition}\ mult\_local\_ring\_at::\ "('a\ \isasymtimes \ 'a)\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set"\isanewline
+\ \ \isakeyword{where}\ "mult\_local\_ring\_at\ \isasymequiv \ local.mult\_rel\ "\isanewline
+\isanewline
+\isacommand{definition}\ uminus\_local\_ring\_at::\ "('a\ \isasymtimes \ 'a)\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set"\isanewline
+\ \ \isakeyword{where}\ "uminus\_local\_ring\_at\ \isasymequiv \ local.uminus\_rel\ "\isanewline
+\isanewline
+\isacommand{definition}\ zero\_local\_ring\_at::\ "('a\ \isasymtimes \ 'a)\ set"\isanewline
+\ \ \isakeyword{where}\ "zero\_local\_ring\_at\ \isasymequiv \ local.zero\_rel"\isanewline
+\isanewline
+\isacommand{definition}\ one\_local\_ring\_at::\ "('a\ \isasymtimes \ 'a)\ set"\isanewline
+\ \ \isakeyword{where}\ "one\_local\_ring\_at\ \isasymequiv \ local.one\_rel"\isanewline
 \isanewline
@@
 This allows us to introduce the next construction.	\\
-Let $U$ be an open subset of $\text{Spec}\,R$. We define $\mathscr{O}_{\spec}(U)$ to be the set of all functions 
+Let $U$ be an open subset of $\text{Spec}\,R$. We define $\mathscr{O}_{\spec} (U)$ to be the set of all functions 
 	\[
@@
 \\
-We endow $\mathscr{O}_{\spec}(U)$ with the sum and product of such functions and we take for the additive unit (\textit{resp.} multiplicative unit) the function that maps each $\mathfrak{p}$ on the additive unit (\textit{resp.} multiplicative unit) of $R_{\mathfrak{p}}$.
-\\
-Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_{\spec}(U) \rightarrow \mathscr{O}_{\spec}(V)$ maps each $s \in \mathscr{O}_{\spec}(U)$ on its restriction to $V$. \\
-One checks $\mathscr{O}_{\spec}$ is a sheaf of rings on $\text{Spec}\,R$ and the pair $(\text{Spec}\,R, \mathscr{O}_{\spec})$ is called the \emph{spectrum of the ring $R$}. \\
+We endow $\mathscr{O}_{\spec} (U)$ with the sum and product of such functions and we take for the additive unit (\textit{resp.} multiplicative unit) the function that maps each $\mathfrak{p}$ on the additive unit (\textit{resp.} multiplicative unit) of $R_{\mathfrak{p}}$.
+\\
+Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_{\spec} (U) \rightarrow \mathscr{O}_{\spec} (V)$ maps each $s \in \mathscr{O}_{\spec} (U)$ on its restriction to $V$. \\
+One checks $\mathscr{O}_{\spec} $ is a sheaf of rings on $\text{Spec}\,R$ and the pair $(\text{Spec}\,R, \mathscr{O}_{\spec} )$ is called the \emph{spectrum of the ring $R$}. \\
 This last construction translates smoothly in Isabelle.
@@
 \begin{isabelle}
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac\ s\ V\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}{\isasymexists}r\ f{\isachardot}{\kern0pt}\ r\ {\isasymin}\ R\ {\isasymand}\ f\ {\isasymin}\ R\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}{\isasymqq}\ {\isasymin}\ V{\isachardot}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ f\ {\isasymnotin}\ {\isasymqq}\ {\isasymand}\ s\ {\isasymqq}\ {\isacharequal}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}frac\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasymqq}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ r\ f{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}regular\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}regular\ s\ U\ {\isasymequiv}\ {\isasymforall}{\isasympp}{\isachardot}{\kern0pt}\ {\isasympp}\ {\isasymin}\ U\ {\isasymlongrightarrow}\ \isanewline
-\ \ {\isacharparenleft}{\kern0pt}{\isasymexists}V{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ V\ {\isasymand}\ V\ {\isasymsubseteq}\ U\ {\isasymand}\ {\isasympp}\ {\isasymin}\ V\ {\isasymand}\ {\isacharparenleft}{\kern0pt}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac\ s\ V{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymO}\ {\isacharunderscore}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbrackleft}{\kern0pt}{\isadigit{9}}{\isadigit{0}}{\isacharbrackright}{\kern0pt}\ {\isadigit{9}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymO}\ U\ {\isasymequiv}\ {\isacharbraceleft}{\kern0pt}s{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymPi}\isactrlsub E\ {\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}R\isactrlbsub {\isasympp}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}regular\ s\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ s\ s{\isacharprime}{\kern0pt}\ {\isasymequiv}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isacharparenleft}{\kern0pt}s\ {\isasympp}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isacharprime}{\kern0pt}\ {\isasympp}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ s\ s{\isacharprime}{\kern0pt}\ {\isasymequiv}\ \isanewline
-\ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isacharparenleft}{\kern0pt}s\ {\isasympp}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isacharprime}{\kern0pt}\ {\isasympp}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ {\isasymequiv}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ {\isasymequiv}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\isanewline
-\ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ U\ V\ {\isasymequiv}\ {\isasymlambda}s{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymO}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ restrict\ s\ V{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec{\isachardoublequoteclose}
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ \isanewline
+\ \ \ \ is\_locally\_frac::\ "('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isasymRightarrow \ 'a\ set\ set\ \isasymRightarrow \ bool"\isanewline
+\ \ \ \ \isakeyword{where}\ "is\_locally\_frac\ s\ V\ \isasymequiv \ (\isasymexists r\ f.\ r\ \isasymin \ R\ \isasymand \ f\ \isasymin \ R\ \isasymand \ (\isasymforall \isasymqq \ \isasymin \ V.\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ f\ \isasymnotin \ \isasymqq \ \isasymand \ s\ \isasymqq \ =\ quotient\_ring.frac\ (R\ \isasymsetminus \ \isasymqq )\ R\ (+)\ (\isasymcdot )\ \isasymzero \ r\ f))"\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ is\_regular\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ ::\ "('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isasymRightarrow \ 'a\ set\ set\ \isasymRightarrow \ bool"\isanewline
+\ \ \isakeyword{where}\ "is\_regular\ s\ U\ \isasymequiv \ \isasymforall \isasympp .\ \isasympp \ \isasymin \ U\ \isasymlongrightarrow \ \isanewline
+\ \ (\isasymexists V.\ is\_zariski\_open\ V\ \isasymand \ V\ \isasymsubseteq \ U\ \isasymand \ \isasympp \ \isasymin \ V\ \isasymand \ (is\_locally\_frac\ s\ V))"\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ sheaf\_spec\isanewline
+\ \ \ \ ::\ "'a\ set\ set\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ set"\ ("\isasymO \ \_"\ [90]\ 90)\isanewline
+\ \ \isakeyword{where}\ "\isasymO \ U\ \isasymequiv \ \{s\isasymin (\isasymPi \isactrlsub E\ \isasympp \isasymin U.\ (R\isactrlbsub \isasympp \ (+)\ (\isasymcdot )\ \isasymzero \isactrlesub )).\ is\_regular\ s\ U\}"\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ add\_sheaf\_spec\isanewline
+\ \ \ \ ::\ "('a\ set)\ set\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)"\isanewline
+\ \ \ \ \isakeyword{where}\ "add\_sheaf\_spec\ U\ s\ s'\ \isasymequiv \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isasymlambda \isasympp \isasymin U.\ quotient\_ring.add\_rel\ (R\ \isasymsetminus \ \isasympp )\ R\ (+)\ (\isasymcdot )\ \isasymzero \ (s\ \isasympp )\ (s'\ \isasympp )"\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ mult\_sheaf\_spec\isanewline
+\ \ \ \ ::\ "('a\ set)\ set\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)"\isanewline
+\ \ \ \ \isakeyword{where}\ "mult\_sheaf\_spec\ U\ s\ s'\ \isasymequiv \ \isanewline
+\ \ \ \ \ \ \ \ \ \isasymlambda \isasympp \isasymin U.\ quotient\_ring.mult\_rel\ (R\ \isasymsetminus \ \isasympp )\ R\ (+)\ (\isasymcdot )\ \isasymzero \ (s\ \isasympp )\ (s'\ \isasympp )"\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ zero\_sheaf\_spec\isanewline
+\ \ \ \ ::\ "'a\ set\ set\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)"\isanewline
+\ \ \ \ \isakeyword{where}\ "zero\_sheaf\_spec\ U\ \isasymequiv \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymlambda \isasympp \isasymin U.\ quotient\_ring.zero\_rel\ (R\ \isasymsetminus \ \isasympp )\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ one\_sheaf\_spec\isanewline
+\ \ \ \ ::\ "'a\ set\ set\ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)"\isanewline
+\ \ \ \ \isakeyword{where}\ "one\_sheaf\_spec\ U\ \isasymequiv \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymlambda \isasympp \isasymin U.\ quotient\_ring.one\_rel\ (R\ \isasymsetminus \ \isasympp )\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "\isanewline
+\isanewline
+\isacommand{definition}\ (\isakeyword{in}\ comm\_ring)\ sheaf\_spec\_morphisms\isanewline
+\ \ \ \ \ \ \ \ ::\ "'a\ set\ set\ \isasymRightarrow \ 'a\ set\ set\ \isasymRightarrow \ (('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymRightarrow \ ('a\ set\ \isasymRightarrow \ ('a\ \isasymtimes \ 'a)\ set))"\isanewline
+\ \ \ \ \ \ \ \ \isakeyword{where}\ "sheaf\_spec\_morphisms\ U\ V\ \isasymequiv \ \isasymlambda s\isasymin (\isasymO \ U).\ restrict\ s\ V"\isanewline
+\isanewline
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ sheaf\_spec\_is\_sheaf:\isanewline
+\ \ \isakeyword{shows}\ "sheaf\_of\_rings\ Spec\ is\_zariski\_open\ sheaf\_spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ sheaf\_spec\_morphisms\ \isasymO b\ add\_sheaf\_spec\ mult\_sheaf\_spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero\_sheaf\_spec\ one\_sheaf\_spec"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ ringed{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings
+\isacommand{locale}\ ringed\_space\ =\ sheaf\_of\_rings
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\isanewline
-\ \ \ \ \ \ im{\isacharunderscore}{\kern0pt}sheaf\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ b\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ f\ \isanewline
-\ \ \ \ \ \ {\isacharplus}{\kern0pt}\ codom{\isacharcolon}{\kern0pt}\ ringed{\isacharunderscore}{\kern0pt}space\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
-\ \ \ \ \ \ \isakeyword{for}\ X\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ \isakeyword{and}\ {\isasymO}\isactrlsub X\ \isakeyword{and}\ {\isasymrho}\isactrlsub X\ \isakeyword{and}\ b\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\isanewline
-\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ Y\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ \isakeyword{and}\ {\isasymO}\isactrlsub Y\ \isakeyword{and}\ {\isasymrho}\isactrlsub Y\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ d\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isakeyword{and}\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isakeyword{and}\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
+\isacommand{locale}\ morphism\_ringed\_spaces\ =\isanewline
+\ \ \ \ \ \ im\_sheaf\ X\ is\_open\isactrlsub X\ \isasymO \isactrlsub X\ \isasymrho \isactrlsub X\ b\ add\_str\isactrlsub X\ mult\_str\isactrlsub X\ zero\_str\isactrlsub X\ one\_str\isactrlsub X\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Y\ is\_open\isactrlsub Y\ f\ \isanewline
+\ \ \ \ \ \ +\ codom:\ ringed\_space\ Y\ is\_open\isactrlsub Y\ \isasymO \isactrlsub Y\ \isasymrho \isactrlsub Y\ d\ add\_str\isactrlsub Y\ mult\_str\isactrlsub Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero\_str\isactrlsub Y\ one\_str\isactrlsub Y\isanewline
+\ \ \ \ \ \ \isakeyword{for}\ X\ \isakeyword{and}\ is\_open\isactrlsub X\ \isakeyword{and}\ \isasymO \isactrlsub X\ \isakeyword{and}\ \isasymrho \isactrlsub X\ \isakeyword{and}\ b\ \isakeyword{and}\ add\_str\isactrlsub X\ \isakeyword{and}\ mult\_str\isactrlsub X\isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ zero\_str\isactrlsub X\ \isakeyword{and}\ one\_str\isactrlsub X\ \isakeyword{and}\ Y\ \isakeyword{and}\ is\_open\isactrlsub Y\ \isakeyword{and}\ \isasymO \isactrlsub Y\ \isakeyword{and}\ \isasymrho \isactrlsub Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ d\ \isakeyword{and}\ add\_str\isactrlsub Y\ \isakeyword{and}\ mult\_str\isactrlsub Y\ \isakeyword{and}\ zero\_str\isactrlsub Y\ \isakeyword{and}\ one\_str\isactrlsub Y\isanewline
 \ \ \ \ \ \ \ \ \ \ \isakeyword{and}\ f\ \isanewline
-\ \ \ \ \ \ {\isacharplus}{\kern0pt}\ \isakeyword{fixes}\ {\isasymphi}\isactrlsub f{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}d\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}morphism{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}sheaves{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}morphism{\isacharunderscore}{\kern0pt}sheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Y\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ im{\isacharunderscore}{\kern0pt}sheaf\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\ b\ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymphi}\isactrlsub f{\isachardoublequoteclose}
+\ \ \ \ \ \ +\ \isakeyword{fixes}\ \isasymphi \isactrlsub f::\ "'c\ set\ \isasymRightarrow \ ('d\ \isasymRightarrow \ 'b)"\isanewline
+\ \ \ \ \isakeyword{assumes}\ is\_morphism\_of\_sheaves:\ "morphism\_sheaves\_of\_rings\ Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ is\_open\isactrlsub Y\ \isasymO \isactrlsub Y\ \isasymrho \isactrlsub Y\ d\ add\_str\isactrlsub Y\ mult\_str\isactrlsub Y\ zero\_str\isactrlsub Y\ one\_str\isactrlsub Y\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ im\_sheaf\ im\_sheaf\_morphisms\ b\ add\_im\_sheaf\ mult\_im\_sheaf\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero\_im\_sheaf\ one\_im\_sheaf\ \isasymphi \isactrlsub f"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ direct{\isacharunderscore}{\kern0pt}lim\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ I{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ subset{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}opens{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ U\ {\isasymin}\ I\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ U{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ has{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}U\ V{\isachardot}{\kern0pt}\ {\isasymlbrakk}\ U{\isasymin}I{\isacharsemicolon}{\kern0pt}\ V{\isasymin}I\ {\isasymrbrakk}\ {\isasymLongrightarrow}\ {\isasymexists}W{\isasymin}I{\isachardot}{\kern0pt}\ W\ {\isasymsubseteq}\ U\ {\isasyminter}\ V{\isachardoublequoteclose}\isanewline
+\isacommand{locale}\ direct\_lim\ =\ sheaf\_of\_rings\ +\isanewline
+\ \ \isakeyword{fixes}\ I::\ "'a\ set\ set"\isanewline
+\ \ \isakeyword{assumes}\ subset\_of\_opens:\ "\isasymAnd U.\ U\ \isasymin \ I\ \isasymLongrightarrow \ is\_open\ U"\isanewline
+\ \ \ \ \isakeyword{and}\ has\_lower\_bound:\ "\isasymAnd U\ V.\ \isasymlbrakk \ U\isasymin I;\ V\isasymin I\ \isasymrbrakk \ \isasymLongrightarrow \ \isasymexists W\isasymin I.\ W\ \isasymsubseteq \ U\ \isasyminter \ V"\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{definition}\isamarkupfalse%
-\ rel{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infix}\ {\isachardoublequoteopen}{\isasymsim}{\isachardoublequoteclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isasymsim}\ y\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}fst\ x\ {\isasymin}\ I\ {\isasymand}\ fst\ y\ {\isasymin}\ I{\isacharparenright}{\kern0pt}\ {\isasymand}\ {\isacharparenleft}{\kern0pt}snd\ x\ {\isasymin}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ snd\ y\ {\isasymin}\ {\isasymFF}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymexists}W{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}W\ {\isasymin}\ I{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharparenleft}{\kern0pt}W\ {\isasymsubseteq}\ fst\ x\ {\isasyminter}\ fst\ y{\isacharparenright}{\kern0pt}\ {\isasymand}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ W\ {\isacharparenleft}{\kern0pt}snd\ x{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharequal}{\kern0pt}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\ W\ {\isacharparenleft}{\kern0pt}snd\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ rel{\isacharcolon}{\kern0pt}equivalence\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}Sigma\ I\ {\isasymFF}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}{\isacharparenleft}{\kern0pt}x{\isacharcomma}{\kern0pt}\ y{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ x\ {\isasymsim}\ y{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ class{\isacharunderscore}{\kern0pt}of{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymlfloor}{\isacharparenleft}{\kern0pt}{\isacharunderscore}{\kern0pt}{\isacharcomma}{\kern0pt}{\isacharslash}{\kern0pt}\ {\isacharunderscore}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymrfloor}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlfloor}U{\isacharcomma}{\kern0pt}s{\isasymrfloor}\ {\isasymequiv}\ rel{\isachardot}{\kern0pt}Class\ {\isacharparenleft}{\kern0pt}U{\isacharcomma}{\kern0pt}\ s{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim\ {\isasymequiv}\ rel{\isachardot}{\kern0pt}Partition{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
-\ \ {\isachardoublequoteopen}get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound\ U\ V{\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ W{\isachardot}{\kern0pt}\ W\ {\isasymin}\ I\ {\isasymand}\ W\ {\isasymsubseteq}\ U\ {\isasymand}\ W\ {\isasymsubseteq}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ add{\isacharunderscore}{\kern0pt}rel\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}rel\ X\ Y\ {\isasymequiv}\ let\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ x\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ X{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ y{\isachardot}{\kern0pt}\ y\ {\isasymin}\ Y{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ w\ {\isacharequal}{\kern0pt}\ get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\isanewline
+\isacommand{definition}\ rel::\ "('a\ set\ \isasymtimes \ 'b)\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ \isasymRightarrow \ bool"\ (\isakeyword{infix}\ "\isasymsim "\ 80)\isanewline
+\ \ \isakeyword{where}\ "x\ \isasymsim \ y\ \isasymequiv \ (fst\ x\ \isasymin \ I\ \isasymand \ fst\ y\ \isasymin \ I)\ \isasymand \ (snd\ x\ \isasymin \ \isasymFF \ (fst\ x)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymand \ snd\ y\ \isasymin \ \isasymFF \ (fst\ y))\ \isasymand \ (\isasymexists W.\ (W\ \isasymin \ I)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymand \ (W\ \isasymsubseteq \ fst\ x\ \isasyminter \ fst\ y)\ \isasymand \ \isasymrho \ (fst\ x)\ W\ (snd\ x)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ =\ \isasymrho \ (fst\ y)\ W\ (snd\ y))"\isanewline
+\isanewline
+\isacommand{interpretation}\ rel:equivalence\ "(Sigma\ I\ \isasymFF )"\ "\{(x,\ y).\ x\ \isasymsim \ y\}"\isanewline
+\isanewline
+\isacommand{definition}\ class\_of::\ "'a\ set\ \isasymRightarrow \ 'b\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\ ("\isasymlfloor (\_,/\ \_)\isasymrfloor ")\isanewline
+\ \ \isakeyword{where}\ "\isasymlfloor U,s\isasymrfloor \ \isasymequiv \ rel.Class\ (U,\ s)"\isanewline
+\isanewline
+\isacommand{definition}\ carrier\_direct\_lim::\ "('a\ set\ \isasymtimes \ 'b)\ set\ set"\isanewline
+\ \ \isakeyword{where}\ "carrier\_direct\_lim\ \isasymequiv \ rel.Partition"\isanewline
+\isanewline
+\isacommand{definition}\ get\_lower\_bound::\ "'a\ set\ \isasymRightarrow \ 'a\ set\ \isasymRightarrow \ 'a\ set"\ \isakeyword{where}\isanewline
+\ \ "get\_lower\_bound\ U\ V=\ (SOME\ W.\ W\ \isasymin \ I\ \isasymand \ W\ \isasymsubseteq \ U\ \isasymand \ W\ \isasymsubseteq \ V)"\isanewline
+\isanewline
+\isacommand{definition}\ add\_rel\ ::\ "('a\ set\ \isasymtimes \ 'b)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "add\_rel\ X\ Y\ \isasymequiv \ let\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ x\ =\ (SOME\ x.\ x\ \isasymin \ X);\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ (SOME\ y.\ y\ \isasymin \ Y);\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ w\ =\ get\_lower\_bound\ (fst\ x)\ (fst\ y)\isanewline
 \ \ \ \ \ \ \ \ \ \ \ \ in\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlfloor}w{\isacharcomma}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}str\ w\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ x{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymrfloor}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ mult{\isacharunderscore}{\kern0pt}rel\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}rel\ X\ Y\ {\isasymequiv}\ let\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ x\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ X{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ y{\isachardot}{\kern0pt}\ y\ {\isasymin}\ Y{\isacharparenright}{\kern0pt}{\isacharsemicolon}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ w\ {\isacharequal}{\kern0pt}\ get{\isacharunderscore}{\kern0pt}lower{\isacharunderscore}{\kern0pt}bound\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymlfloor w,\ add\_str\ w\ (\isasymrho \ (fst\ x)\ w\ (snd\ x))\ (\isasymrho \ (fst\ y)\ w\ (snd\ y))\isasymrfloor "\isanewline
+\isanewline
+\isacommand{definition}\ mult\_rel\ ::\ "('a\ set\ \isasymtimes \ 'b)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "mult\_rel\ X\ Y\ \isasymequiv \ let\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ x\ =\ (SOME\ x.\ x\ \isasymin \ X);\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ (SOME\ y.\ y\ \isasymin \ Y);\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ w\ =\ get\_lower\_bound\ (fst\ x)\ (fst\ y)\isanewline
 \ \ \ \ \ \ \ \ \ \ \ \ in\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlfloor}w{\isacharcomma}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}str\ w\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ x{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ x{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymrho}\ {\isacharparenleft}{\kern0pt}fst\ y{\isacharparenright}{\kern0pt}\ w\ {\isacharparenleft}{\kern0pt}snd\ y{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isasymrfloor}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ direct{\isacharunderscore}{\kern0pt}{lim}{\isacharunderscore}{\kern0pt}{is}{\isacharunderscore}{\kern0pt}{ring}{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}U\ {\isasymin}\ I{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}ring\ carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim\ add{\isacharunderscore}{\kern0pt}rel\ mult{\isacharunderscore}{\kern0pt}rel\ {\isasymlfloor}U{\isacharcomma}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub {\isasymrfloor}\ {\isasymlfloor}U{\isacharcomma}{\kern0pt}\ {\isasymone}\isactrlbsub U\isactrlesub {\isasymrfloor}{\isachardoublequoteclose}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymlfloor w,\ mult\_str\ w\ (\isasymrho \ (fst\ x)\ w\ (snd\ x))\ (\isasymrho \ (fst\ y)\ w\ (snd\ y))\isasymrfloor "\isanewline
+\isanewline
+\isacommand{lemma}\ direct\_{lim}\_{is}\_{ring}:\isanewline
+\ \ \isakeyword{assumes}\ "U\ \isasymin \ I"\isanewline
+\ \ \isakeyword{shows}\ "ring\ carrier\_direct\_lim\ add\_rel\ mult\_rel\ \isasymlfloor U,\ \isasymzero \isactrlbsub U\isactrlesub \isasymrfloor \ \isasymlfloor U,\ \isasymone \isactrlbsub U\isactrlesub \isasymrfloor "\isanewline
 \isanewline
@@
 \begin{isabelle}
-\isacommand{definition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ direct{\isacharunderscore}{\kern0pt}lim{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ canonical{\isacharunderscore}{\kern0pt}fun\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}canonical{\isacharunderscore}{\kern0pt}fun\ U\ x\ {\isacharequal}{\kern0pt}\ {\isasymlfloor}U{\isacharcomma}{\kern0pt}\ x{\isasymrfloor}{\isachardoublequoteclose}
+\isacommand{definition}\ (\isakeyword{in}\ direct\_lim)\ \isanewline
+\ \ \ \ \ \ \ \ canonical\_fun\ ::\ "'a\ set\ \isasymRightarrow \ 'b\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "canonical\_fun\ U\ x\ =\ \isasymlfloor U,\ x\isasymrfloor "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{proposition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ direct{\isacharunderscore}{\kern0pt}lim{\isacharparenright}{\kern0pt}\ universal{\isacharunderscore}{\kern0pt}property{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ A{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ set{\isachardoublequoteclose}\ \isakeyword{and}\ {\isasympsi}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}b\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \isakeyword{and}\ add{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\ \isakeyword{and}\ mult{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \isakeyword{and}\ zero{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\ \isakeyword{and}\ one{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}c{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}ring\ A\ add\ mult\ zero\ one{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}{\isasymAnd}U{\isachardot}{\kern0pt}\ U\ {\isasymin}\ I\ {\isasymLongrightarrow}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ {\isacharparenleft}{\kern0pt}{\isasympsi}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymcdot}\isactrlbsub U\isactrlesub {\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlbsub U\isactrlesub \ {\isasymone}\isactrlbsub U\isactrlesub \ A\ add\ mult\ zero\ one{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}{\isasymAnd}U\ V\ x{\isachardot}{\kern0pt}\ {\isasymlbrakk}U\ {\isasymin}\ I{\isacharsemicolon}{\kern0pt}\ V\ {\isasymin}\ I{\isacharsemicolon}{\kern0pt}\ V\ {\isasymsubseteq}\ U{\isacharsemicolon}{\kern0pt}\ x\ {\isasymin}\ {\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isasymrbrakk}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasympsi}\ V\ {\isasymcirc}\ {\isasymrho}\ U\ V{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ {\isasympsi}\ U\ x{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}V{\isasymin}I{\isachardot}{\kern0pt}\ {\isasymexists}{\isacharbang}{\kern0pt}u{\isachardot}{\kern0pt}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ u\ carrier{\isacharunderscore}{\kern0pt}direct{\isacharunderscore}{\kern0pt}lim\ add{\isacharunderscore}{\kern0pt}rel\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}rel\ {\isasymlfloor}V{\isacharcomma}{\kern0pt}{\isasymzero}\isactrlbsub V\isactrlesub {\isasymrfloor}\ {\isasymlfloor}V{\isacharcomma}{\kern0pt}{\isasymone}\isactrlbsub V\isactrlesub {\isasymrfloor}\ A\ add\ mult\ zero\ one\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}U{\isasymin}I{\isachardot}{\kern0pt}\ {\isasymforall}x{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymFF}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}u\ {\isasymcirc}\ canonical{\isacharunderscore}{\kern0pt}fun\ U{\isacharparenright}{\kern0pt}\ x\ {\isacharequal}{\kern0pt}\ {\isasympsi}\ U\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{proposition}\ (\isakeyword{in}\ direct\_lim)\ universal\_property:\isanewline
+\ \ \isakeyword{fixes}\ A::\ "'c\ set"\ \isakeyword{and}\ \isasympsi ::\ "'a\ set\ \isasymRightarrow \ ('b\ \isasymRightarrow \ 'c)"\ \isanewline
+\ \ \ \ \isakeyword{and}\ add::\ "'c\ \isasymRightarrow \ 'c\ \isasymRightarrow \ 'c"\ \isakeyword{and}\ mult::\ "'c\ \isasymRightarrow \ 'c\ \isasymRightarrow \ 'c"\ \isanewline
+\ \ \ \ \isakeyword{and}\ zero::\ "'c"\ \isakeyword{and}\ one::\ "'c"\isanewline
+\ \ \isakeyword{assumes}\ "ring\ A\ add\ mult\ zero\ one"\isanewline
+\ \ \ \ \isakeyword{and}\ "\isasymAnd U.\ U\ \isasymin \ I\ \isasymLongrightarrow \ ring\_homomorphism\ (\isasympsi \ U)\ (\isasymFF \ U)\ (+\isactrlbsub U\isactrlesub )\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymcdot \isactrlbsub U\isactrlesub )\ \isasymzero \isactrlbsub U\isactrlesub \ \isasymone \isactrlbsub U\isactrlesub \ A\ add\ mult\ zero\ one"\isanewline
+\ \ \ \ \isakeyword{and}\ "\isasymAnd U\ V\ x.\ \isasymlbrakk U\ \isasymin \ I;\ V\ \isasymin \ I;\ V\ \isasymsubseteq \ U;\ x\ \isasymin \ (\isasymFF \ U)\isasymrbrakk \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ (\isasympsi \ V\ \isasymcirc \ \isasymrho \ U\ V)\ x\ =\ \isasympsi \ U\ x"\isanewline
+\ \ \isakeyword{shows}\ "\isasymforall V\isasymin I.\ \isasymexists !u.\ ring\_homomorphism\ u\ carrier\_direct\_lim\ add\_rel\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_rel\ \isasymlfloor V,\isasymzero \isactrlbsub V\isactrlesub \isasymrfloor \ \isasymlfloor V,\isasymone \isactrlbsub V\isactrlesub \isasymrfloor \ A\ add\ mult\ zero\ one\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymand \ (\isasymforall U\isasymin I.\ \isasymforall x\isasymin (\isasymFF \ U).\ (u\ \isasymcirc \ canonical\_fun\ U)\ x\ =\ \isasympsi \ U\ x)"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ stalk\ {\isacharequal}{\kern0pt}\ direct{\isacharunderscore}{\kern0pt}lim\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ x{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}elem{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}x\ {\isasymin}\ S{\isachardoublequoteclose}\ \isakeyword{and}\ index{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}I\ {\isacharequal}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymand}\ x\ {\isasymin}\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isacommand{locale}\ stalk\ =\ direct\_lim\ +\isanewline
+\ \ \isakeyword{fixes}\ x::\ "'a"\isanewline
+\ \ \isakeyword{assumes}\ is\_elem:\ "x\ \isasymin \ S"\ \isakeyword{and}\ index:\ "I\ =\ \{U.\ is\_open\ U\ \isasymand \ x\ \isasymin \ U\}"\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{definition}\isamarkupfalse%
-\ carrier{\isacharunderscore}{\kern0pt}stalk{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}stalk\ {\isasymequiv}\ dlim\ {\isasymFF}\ {\isasymrho}\ {\isacharparenleft}{\kern0pt}neighborhoods\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ add{\isacharunderscore}{\kern0pt}stalk\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}stalk\ {\isasymequiv}\ add{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ mult{\isacharunderscore}{\kern0pt}stalk\isanewline
-\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}stalk\ {\isasymequiv}\ mult{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ zero{\isacharunderscore}{\kern0pt}stalk{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}stalk\ V\ {\isasymequiv}\ class{\isacharunderscore}{\kern0pt}of\ V\ {\isasymzero}\isactrlbsub V\isactrlesub {\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ one{\isacharunderscore}{\kern0pt}stalk{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}stalk\ V\ {\isasymequiv}\ class{\isacharunderscore}{\kern0pt}of\ V\ {\isasymone}\isactrlbsub V\isactrlesub {\isachardoublequoteclose}\isanewline
+\isacommand{definition}\ carrier\_stalk::\ "('a\ set\ \isasymtimes \ 'b)\ set\ set"\isanewline
+\ \ \isakeyword{where}\ "carrier\_stalk\ \isasymequiv \ dlim\ \isasymFF \ \isasymrho \ (neighborhoods\ x)"\isanewline
+\isanewline
+\isacommand{definition}\ add\_stalk\isanewline
+\ \ \ \ ::\ "('a\ set\ \isasymtimes \ 'b)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "add\_stalk\ \isasymequiv \ add\_rel"\isanewline
+\isanewline
+\isacommand{definition}\ mult\_stalk\isanewline
+\ \ \ \ ::\ "('a\ set\ \isasymtimes \ 'b)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "mult\_stalk\ \isasymequiv \ mult\_rel"\isanewline
+\isanewline
+\isacommand{definition}\ zero\_stalk::\ "'a\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "zero\_stalk\ V\ \isasymequiv \ class\_of\ V\ \isasymzero \isactrlbsub V\isactrlesub "\isanewline
+\isanewline
+\isacommand{definition}\ one\_stalk::\ "'a\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\isanewline
+\ \ \isakeyword{where}\ "one\_stalk\ V\ \isasymequiv \ class\_of\ V\ \isasymone \isactrlbsub V\isactrlesub "\isanewline
 \isanewline
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ max{\isacharunderscore}{\kern0pt}ideal\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ ideal\ I\ \ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{for}\ R\ \isakeyword{and}\ I\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \isakeyword{and}\ multiplication\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ neq{\isacharunderscore}{\kern0pt}ring{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}I\ {\isasymnoteq}\ R{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}max{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}{\isasymaa}{\isachardot}{\kern0pt}\ {\isasymlbrakk}ideal\ {\isasymaa}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isacharsemicolon}{\kern0pt}{\isasymaa}\ {\isasymnoteq}\ R{\isacharsemicolon}{\kern0pt}I\ {\isasymsubseteq}\ {\isasymaa}\ {\isasymrbrakk}{\isasymLongrightarrow}\ I\ {\isacharequal}{\kern0pt}\ {\isasymaa}{\isachardoublequoteclose}
+\isacommand{locale}\ max\_ideal\ =\ comm\_ring\ R\ "(+)"\ "(\isasymcdot )"\ "\isasymzero "\ "\isasymone "\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ +\ ideal\ I\ \ R\ "(+)"\ "(\isasymcdot )"\ "\isasymzero "\ "\isasymone "\isanewline
+\ \ \isakeyword{for}\ R\ \isakeyword{and}\ I\ \isakeyword{and}\ addition\ (\isakeyword{infixl}\ "+"\ 65)\ \isanewline
+\ \ \ \ \isakeyword{and}\ multiplication\ (\isakeyword{infixl}\ "\isasymcdot "\ 70)\ \isakeyword{and}\ zero\ ("\isasymzero ")\ \isakeyword{and}\ unit\ ("\isasymone ")\ +\isanewline
+\ \ \isakeyword{assumes}\ neq\_ring:\ "I\ \isasymnoteq \ R"\ \isanewline
+\ \ \ \ \ \ \ \isakeyword{and}\ is\_max:\ "\isasymAnd \isasymaa .\ \isasymlbrakk ideal\ \isasymaa \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone ;\isasymaa \ \isasymnoteq \ R;I\ \isasymsubseteq \ \isasymaa \ \isasymrbrakk \isasymLongrightarrow \ I\ =\ \isasymaa "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{proposition}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ max{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}pr{\isacharunderscore}{\kern0pt}ideal\ R\ I\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\isacommand{proposition}\ (\isakeyword{in}\ max\_ideal)\ is\_pr\_ideal:\ "pr\_ideal\ R\ I\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ local{\isacharunderscore}{\kern0pt}ring\ {\isacharequal}{\kern0pt}\ ring\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}unique{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}I\ J{\isachardot}{\kern0pt}\ max{\isacharunderscore}{\kern0pt}lideal\ I\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ max{\isacharunderscore}{\kern0pt}lideal\ J\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymLongrightarrow}\ I\ {\isacharequal}{\kern0pt}\ J{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ has{\isacharunderscore}{\kern0pt}max{\isacharunderscore}{\kern0pt}lideal{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymexists}{\isasymww}{\isachardot}{\kern0pt}\ max{\isacharunderscore}{\kern0pt}lideal\ {\isasymww}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}
+\isacommand{locale}\ local\_ring\ =\ ring\ +\isanewline
+\ \ \isakeyword{assumes}\ is\_unique:\ "\isasymAnd I\ J.\ max\_lideal\ I\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ max\_lideal\ J\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ \isasymLongrightarrow \ I\ =\ J"\isanewline
+\ \ \ \ \isakeyword{and}\ has\_max\_lideal:\ "\isasymexists \isasymww .\ max\_lideal\ \isasymww \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}\ local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ pr\_ideal)\ local\_ring\_at\_is\_local:\isanewline
+\ \ \isakeyword{shows}\ "local\_ring\ carrier\_local\_ring\_at\ add\_local\_ring\_at\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_local\_ring\_at\ zero\_local\_ring\_at\ one\_local\_ring\_at"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphism\ {\isacharequal}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ source{\isacharcolon}{\kern0pt}\ local{\isacharunderscore}{\kern0pt}ring\ A\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ target{\isacharcolon}{\kern0pt}\ local{\isacharunderscore}{\kern0pt}ring\ B\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \ \ \ \ \ \ \ \ {\isacharplus}{\kern0pt}\ ring{\isacharunderscore}{\kern0pt}homomorphism\ f\ A\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}\ B\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{for}\ f\ \isakeyword{and}\ A\ \isakeyword{and}\ addition\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ multiplication\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \isakeyword{and}\ zero\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ B\ \isakeyword{and}\ addition{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \isakeyword{and}\ multiplication{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isachardoublequoteopen}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}\ {\isadigit{7}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ zero{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymzero}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\ \isakeyword{and}\ unit{\isacharprime}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymone}{\isacharprime}{\kern0pt}{\isacharprime}{\kern0pt}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
-\ \ {\isacharplus}{\kern0pt}\ \isakeyword{assumes}\ preimage{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}max{\isacharunderscore}{\kern0pt}lideal{\isacharcolon}{\kern0pt}\isanewline
-\ \ \ \ \ \ {\isachardoublequoteopen}{\isasymAnd}{\isasymww}\isactrlsub A\ {\isasymww}\isactrlsub B{\isachardot}{\kern0pt}\ max{\isacharunderscore}{\kern0pt}lideal\ {\isasymww}\isactrlsub A\ A\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ {\isasymLongrightarrow}\ max{\isacharunderscore}{\kern0pt}lideal\ {\isasymww}\isactrlsub B\ B\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharprime}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isasymzero}{\isacharprime}{\kern0pt}\ {\isasymone}{\isacharprime}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ A\ {\isasymww}\isactrlsub B{\isacharparenright}{\kern0pt}\ {\isacharequal}{\kern0pt}\ {\isasymww}\isactrlsub A{\isachardoublequoteclose}
+\isacommand{locale}\ local\_ring\_morphism\ =\isanewline
+\ \ \ \ \ \ \ \ \ \ source:\ local\_ring\ A\ "(+)"\ "(\isasymcdot )"\ \isasymzero \ \isasymone \ \isanewline
+\ \ \ \ \ \ \ \ \ \ +\ target:\ local\_ring\ B\ "(+')"\ "(\isasymcdot ')"\ "\isasymzero '"\ "\isasymone '"\isanewline
+\ \ \ \ \ \ \ \ \ \ +\ ring\_homomorphism\ f\ A\ "(+)"\ "(\isasymcdot )"\ "\isasymzero "\ "\isasymone "\ B\ "(+')"\ "(\isasymcdot ')"\ "\isasymzero '"\ "\isasymone '"\isanewline
+\ \ \isakeyword{for}\ f\ \isakeyword{and}\ A\ \isakeyword{and}\ addition\ (\isakeyword{infixl}\ "+"\ 65)\ \isakeyword{and}\ multiplication\ (\isakeyword{infixl}\ "\isasymcdot "\ 70)\ \isanewline
+\ \ \ \ \ \isakeyword{and}\ zero\ ("\isasymzero ")\ \isakeyword{and}\ unit\ ("\isasymone ")\ \isakeyword{and}\ B\ \isakeyword{and}\ addition'\ (\isakeyword{infixl}\ "+'{\kern0pt}'"\ 65)\ \isanewline
+\ \ \ \ \ \isakeyword{and}\ multiplication'\ (\isakeyword{infixl}\ "\isasymcdot '{\kern0pt}'"\ 70)\ \isakeyword{and}\ zero'\ ("\isasymzero '{\kern0pt}'")\ \isakeyword{and}\ unit'\ ("\isasymone '{\kern0pt}'")\isanewline
+\ \ +\ \isakeyword{assumes}\ preimage\_of\_max\_lideal:\isanewline
+\ \ \ \ \ \ "\isasymAnd \isasymww \isactrlsub A\ \isasymww \isactrlsub B.\ max\_lideal\ \isasymww \isactrlsub A\ A\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ \isasymLongrightarrow \ max\_lideal\ \isasymww \isactrlsub B\ B\ (+')\ (\isasymcdot ')\ \isasymzero '\ \isasymone '\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ (f\isactrlsup \isasyminverse \ A\ \isasymww \isactrlsub B)\ =\ \isasymww \isactrlsub A"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ ringed{\isacharunderscore}{\kern0pt}space\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ stalks{\isacharunderscore}{\kern0pt}are{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}x\ U{\isachardot}{\kern0pt}\ x\ {\isasymin}\ U\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ stalk{\isachardot}{\kern0pt}is{\isacharunderscore}{\kern0pt}local\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ is{\isacharunderscore}{\kern0pt}open\ {\isasymFF}\ {\isasymrho}\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isacharparenleft}{\kern0pt}neighborhoods\ x{\isacharparenright}{\kern0pt}\ x\ U{\isachardoublequoteclose}
+\isacommand{locale}\ locally\_ringed\_space\ =\ ringed\_space\ +\isanewline
+\ \ \isakeyword{assumes}\ stalks\_are\_local:\ "\isasymAnd x\ U.\ x\ \isasymin \ U\ \isasymLongrightarrow \ is\_open\ U\ \isasymLongrightarrow \ stalk.is\_local\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ is\_open\ \isasymFF \ \isasymrho \ add\_str\ mult\_str\ zero\_str\ one\_str\ (neighborhoods\ x)\ x\ U"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ key{\isacharunderscore}{\kern0pt}map\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ {\isasympp}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}prime{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasympp}\ {\isasymin}\ Spec{\isachardoublequoteclose}\isanewline
+\isacommand{locale}\ key\_map\ =\ comm\_ring\ +\isanewline
+\ \ \isakeyword{fixes}\ \isasympp ::\ "'a\ set"\ \isakeyword{assumes}\ is\_prime:\ "\isasympp \ \isasymin \ Spec"\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ pi{\isacharcolon}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal\ R\ {\isasympp}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}%
-\isanewline
-\isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ st{\isacharcolon}{\kern0pt}\ stalk\ {\isachardoublequoteopen}Spec{\isachardoublequoteclose}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ U\ {\isasymand}\ {\isasympp}{\isasymin}U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ {\isasympp}\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ stalk{\isacharunderscore}{\kern0pt}at{\isacharunderscore}{\kern0pt}prime{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}iso{\isacharunderscore}{\kern0pt}to{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharunderscore}{\kern0pt}prime{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ V{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}{\isasympp}\ {\isasymin}\ V{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}{\isasymphi}{\isachardot}{\kern0pt}\ ring{\isacharunderscore}{\kern0pt}isomorphism\ {\isasymphi}\ st{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}stalk\ st{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}stalk\ st{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}stalk\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}st{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}stalk\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}st{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}stalk\ V{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}R\ \isactrlbsub {\isasympp}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}pi{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isacommand{interpretation}\ pi:pr\_ideal\ R\ \isasympp \ "(+)"\ "(\isasymcdot )"\ \isasymzero \ \isasymone 
+\isanewline
+\isanewline
+\isacommand{interpretation}\ st:\ stalk\ "Spec"\ is\_zariski\_open\ sheaf\_spec\ sheaf\_spec\_morphisms\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymO b\ add\_sheaf\_spec\ mult\_sheaf\_spec\ zero\_sheaf\_spec\ one\_sheaf\_spec\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "\{U.\ is\_zariski\_open\ U\ \isasymand \ \isasympp \isasymin U\}"\ \isasympp \isanewline
+\isanewline
+\isacommand{lemma}\ stalk\_at\_prime\_is\_iso\_to\_local\_ring\_at\_prime:\isanewline
+\ \ \isakeyword{assumes}\ "is\_zariski\_open\ V"\ \isakeyword{and}\ "\isasympp \ \isasymin \ V"\isanewline
+\ \ \isakeyword{shows}\ "\isasymexists \isasymphi .\ ring\_isomorphism\ \isasymphi \ st.carrier\_stalk\ st.add\_stalk\ st.mult\_stalk\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ (st.zero\_stalk\ V)\ (st.one\_stalk\ V)\ (R\ \isactrlbsub \isasympp \ (+)\ (\isasymcdot )\ \isasymzero \isactrlesub )\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ (pi.add\_local\_ring\_at)\ (pi.mult\_local\_ring\_at)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ (pi.zero\_local\_ring\_at)\ (pi.one\_local\_ring\_at)"\isanewline
 \isanewline
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ isomorphic{\isacharunderscore}{\kern0pt}to{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ B\ addB\ multB\ zeroB\ oneB{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}ring{\isacharunderscore}{\kern0pt}isomorphism\ f\ A\ addA\ multA\ zeroA\ oneA\ B\ addB\ multB\ zeroB\ oneB{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ A\ addA\ multA\ zeroA\ oneA{\isachardoublequoteclose}
+\isacommand{lemma}\ isomorphic\_to\_local\_is\_local:\isanewline
+\ \ \isakeyword{assumes}\ "local\_ring\ B\ addB\ multB\ zeroB\ oneB"\isanewline
+\ \ \ \ \isakeyword{and}\ "ring\_isomorphism\ f\ A\ addA\ multA\ zeroA\ oneA\ B\ addB\ multB\ zeroB\ oneB"\isanewline
+\ \ \isakeyword{shows}\ "local\_ring\ A\ addA\ multA\ zeroA\ oneA"
 \end{isabelle}
@@
 \begin{cor}
-	$(\text{Spec}\,R, \mathscr{O}_{\spec})$ is a locally ringed space.
+	$(\text{Spec}\,R, \mathscr{O}_{\spec} )$ is a locally ringed space.
 \end{cor}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ spec\_is\_locally\_ringed\_space:\isanewline
+\ \ \isakeyword{shows}\ "locally\_ringed\_space\ Spec\ is\_zariski\_open\ sheaf\_spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ sheaf\_spec\_morphisms\ \isasymO b\ add\_sheaf\_spec\ mult\_sheaf\_spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero\_sheaf\_spec\ one\_sheaf\_spec"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ ind{\isacharunderscore}{\kern0pt}mor{\isacharunderscore}{\kern0pt}btw{\isacharunderscore}{\kern0pt}stalks\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ x{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isachardoublequoteopen}{\isacharprime}{\kern0pt}a{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}elem{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}x\ {\isasymin}\ X{\isachardoublequoteclose}\isanewline
+\isacommand{locale}\ ind\_mor\_btw\_stalks\ =\ morphism\_ringed\_spaces\ +\isanewline
+\ \ \isakeyword{fixes}\ x::"'a"\isanewline
+\ \ \isakeyword{assumes}\ is\_elem:\ "x\ \isasymin \ X"\isanewline
 \isakeyword{begin}\isanewline
 \isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ stx{\isacharcolon}{\kern0pt}stalk\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ b\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
-\ \ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ U\ {\isasymand}\ x\ {\isasymin}\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}x{\isachardoublequoteclose}\isanewline
-\isacommand{proof}\isamarkupfalse%
-\ \isacommand{qed}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}auto\ simp{\isacharcolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}elem{\isacharparenright}{\kern0pt}%
-\isanewline
-\isanewline
-\isacommand{interpretation}\isamarkupfalse%
-\ stfx{\isacharcolon}{\kern0pt}\ stalk\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
-\ \ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}U{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ U\ {\isasymand}\ {\isacharparenleft}{\kern0pt}f\ x{\isacharparenright}{\kern0pt}\ {\isasymin}\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}f\ x{\isachardoublequoteclose}\isanewline
-\isacommand{proof}\isamarkupfalse%
-\ \isacommand{qed}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}auto\ simp{\isacharcolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}elem{\isacharparenright}{\kern0pt}%
-\isanewline
-\isanewline
-\isacommand{definition}\isamarkupfalse%
-\ induced{\isacharunderscore}{\kern0pt}morphism{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}c\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}d{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymtimes}\ {\isacharprime}{\kern0pt}b{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}induced{\isacharunderscore}{\kern0pt}morphism\ {\isasymequiv}\ {\isasymlambda}C\ {\isasymin}\ stfx{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}stalk{\isachardot}{\kern0pt}\ \ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ let\ r\ {\isacharequal}{\kern0pt}\ {\isacharparenleft}{\kern0pt}SOME\ r{\isachardot}{\kern0pt}\ r\ {\isasymin}\ C{\isacharparenright}{\kern0pt}\ in\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ stx{\isachardot}{\kern0pt}class{\isacharunderscore}{\kern0pt}of\ {\isacharparenleft}{\kern0pt}f\isactrlsup {\isasyminverse}\ X\ {\isacharparenleft}{\kern0pt}fst\ r{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymphi}\isactrlsub f\ {\isacharparenleft}{\kern0pt}fst\ r{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}snd\ r{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
+\isacommand{interpretation}\ stx:stalk\ X\ is\_open\isactrlsub X\ \isasymO \isactrlsub X\ \isasymrho \isactrlsub X\ b\ add\_str\isactrlsub X\ mult\_str\isactrlsub X\ zero\_str\isactrlsub X\ \isanewline
+\ \ one\_str\isactrlsub X\ "\{U.\ is\_open\isactrlsub X\ U\ \isasymand \ x\ \isasymin \ U\}"\ "x"\isanewline
+\isacommand{proof}\ \isacommand{qed}\ (auto\ simp:\ is\_elem)
+\isanewline
+\isanewline
+\isacommand{interpretation}\ stfx:\ stalk\ Y\ is\_open\isactrlsub Y\ \isasymO \isactrlsub Y\ \isasymrho \isactrlsub Y\ d\ add\_str\isactrlsub Y\ mult\_str\isactrlsub Y\ zero\_str\isactrlsub Y\ \isanewline
+\ \ one\_str\isactrlsub Y\ "\{U.\ is\_open\isactrlsub Y\ U\ \isasymand \ (f\ x)\ \isasymin \ U\}"\ "f\ x"\isanewline
+\isacommand{proof}\ \isacommand{qed}\ (auto\ simp:\ is\_elem)
+\isanewline
+\isanewline
+\isacommand{definition}\ induced\_morphism::\ "('c\ set\ \isasymtimes \ 'd)\ set\ \isasymRightarrow \ ('a\ set\ \isasymtimes \ 'b)\ set"\ \isanewline
+\ \ \isakeyword{where}\ "induced\_morphism\ \isasymequiv \ \isasymlambda C\ \isasymin \ stfx.carrier\_stalk.\ \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ let\ r\ =\ (SOME\ r.\ r\ \isasymin \ C)\ in\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ stx.class\_of\ (f\isactrlsup \isasyminverse \ X\ (fst\ r))\ (\isasymphi \isactrlsub f\ (fst\ r)\ (snd\ r))"\isanewline
 \isanewline
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ morphism{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ are{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}morphisms{\isacharcolon}{\kern0pt}\isanewline
-\ \ \ \ {\isachardoublequoteopen}{\isasymAnd}x\ V{\isachardot}{\kern0pt}\ {\isasymlbrakk}x\ {\isasymin}\ X{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ V{\isacharsemicolon}{\kern0pt}\ f\ x\ {\isasymin}\ V{\isasymrbrakk}\ {\isasymLongrightarrow}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ ind{\isacharunderscore}{\kern0pt}mor{\isacharunderscore}{\kern0pt}btw{\isacharunderscore}{\kern0pt}stalks{\isachardot}{\kern0pt}is{\isacharunderscore}{\kern0pt}local\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ f\ x\ V\ {\isasymphi}\isactrlbsub X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymrho}\isactrlsub X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ f\ {\isasymphi}\isactrlsub f\ x\isactrlesub {\isachardoublequoteclose}
+\isacommand{locale}\ morphism\_locally\_ringed\_spaces\ =\ morphism\_ringed\_spaces\ +\isanewline
+\ \ \isakeyword{assumes}\ are\_local\_morphisms:\isanewline
+\ \ \ \ "\isasymAnd x\ V.\ \isasymlbrakk x\ \isasymin \ X;\ is\_open\isactrlsub Y\ V;\ f\ x\ \isasymin \ V\isasymrbrakk \ \isasymLongrightarrow \ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ ind\_mor\_btw\_stalks.is\_local\ X\ is\_open\isactrlsub X\ \isasymO \isactrlsub X\ \isasymrho \isactrlsub X\ add\_str\isactrlsub X\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_str\isactrlsub X\ zero\_str\isactrlsub X\ one\_str\isactrlsub X\ is\_open\isactrlsub Y\ \isasymO \isactrlsub Y\ \isasymrho \isactrlsub Y\ add\_str\isactrlsub Y\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_str\isactrlsub Y\ zero\_str\isactrlsub Y\ one\_str\isactrlsub Y\ f\ x\ V\ \isasymphi \isactrlbsub X\ is\_open\isactrlsub X\ \isasymO \isactrlsub X\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymrho \isactrlsub X\ is\_open\isactrlsub Y\ \isasymO \isactrlsub Y\ \isasymrho \isactrlsub Y\ f\ \isasymphi \isactrlsub f\ x\isactrlesub "
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ iso{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\ morphism{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ is{\isacharunderscore}{\kern0pt}homeomorphism{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}homeomorphism\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ f{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}iso{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}sheaves{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}iso{\isacharunderscore}{\kern0pt}sheaves{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ im{\isacharunderscore}{\kern0pt}sheaf\ im{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}morphisms\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ b\ add{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ mult{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ zero{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ one{\isacharunderscore}{\kern0pt}im{\isacharunderscore}{\kern0pt}sheaf\ {\isasymphi}\isactrlsub f{\isachardoublequoteclose}
+\isacommand{locale}\ iso\_locally\_ringed\_spaces\ =\ morphism\_locally\_ringed\_spaces\ +\isanewline
+\ \ \isakeyword{assumes}\ is\_homeomorphism:\ "homeomorphism\ X\ is\_open\isactrlsub X\ Y\ is\_open\isactrlsub Y\ f"\ \isanewline
+\ \ \ \ \ \ \isakeyword{and}\ is\_iso\_of\_sheaves:\ "iso\_sheaves\_of\_rings\ Y\ is\_open\isactrlsub Y\ \isasymO \isactrlsub Y\ \isasymrho \isactrlsub Y\ d\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ add\_str\isactrlsub Y\ mult\_str\isactrlsub Y\ zero\_str\isactrlsub Y\ one\_str\isactrlsub Y\ im\_sheaf\ im\_sheaf\_morphisms\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ b\ add\_im\_sheaf\ mult\_im\_sheaf\ zero\_im\_sheaf\ one\_im\_sheaf\ \isasymphi \isactrlsub f"
 \end{isabelle}
@@
 \begin{definition}[affine scheme]
-	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(\text{Spec}\,R, \mathscr{O}_{\spec})$ for some commutative ring $R$. 
+	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic (as a locally ringed space) to the spectrum $(\text{Spec}\,R, \mathscr{O}_{\spec} )$ for some commutative ring $R$.
 \end{definition}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ affine{\isacharunderscore}{\kern0pt}scheme\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ \isanewline
-\ \ \ \ {\isacharplus}{\kern0pt}\ locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ \isanewline
-\ \ \ \ {\isacharplus}{\kern0pt}\ iso{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\isanewline
-\ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isachardoublequoteopen}Spec{\isachardoublequoteclose}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymlambda}U{\isachardot}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isachardoublequoteclose}\ f\ {\isasymphi}\isactrlsub f\isanewline
-\ \ \ \ \ \ \ \ \ \ \isakeyword{for}\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ f\ {\isasymphi}\isactrlsub f
+\isacommand{locale}\ affine\_scheme\ =\ comm\_ring\ \isanewline
+\ \ \ \ +\ locally\_ringed\_space\ X\ is\_open\ \isasymO \isactrlsub X\ \isasymrho \ b\ add\_str\ mult\_str\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero\_str\ one\_str\ \isanewline
+\ \ \ \ +\ iso\_locally\_ringed\_spaces\ X\ is\_open\ \isasymO \isactrlsub X\ \isasymrho \ b\ add\_str\ mult\_str\isanewline
+\ \ \ \ \ \ \ \ zero\_str\ one\_str\ "Spec"\ is\_zariski\_open\ sheaf\_spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ sheaf\_spec\_morphisms\ \isasymO b\ "\isasymlambda U.\ add\_sheaf\_spec\ U"\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "\isasymlambda U.\ mult\_sheaf\_spec\ U"\ "\isasymlambda U.\ zero\_sheaf\_spec\ U"\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "\isasymlambda U.\ one\_sheaf\_spec\ U"\ f\ \isasymphi \isactrlsub f\isanewline
+\ \ \ \ \ \ \ \ \ \ \isakeyword{for}\ X\ is\_open\ \isasymO \isactrlsub X\ \isasymrho \ b\ add\_str\ mult\_str\ zero\_str\ one\_str\ f\ \isasymphi \isactrlsub f
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}affine{\isacharunderscore}{\kern0pt}scheme{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}affine{\isacharunderscore}{\kern0pt}scheme\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}identity\ Spec{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ identity\ {\isacharparenleft}{\kern0pt}{\isasymO}\ U{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ comm\_ring)\ spec\_is\_affine\_scheme:\isanewline
+\ \ \isakeyword{shows}\ "affine\_scheme\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ Spec\ is\_zariski\_open\ sheaf\_spec\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ sheaf\_spec\_morphisms\ \isasymO b\ (\isasymlambda U.\ add\_sheaf\_spec\ U)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymlambda U.\ mult\_sheaf\_spec\ U)\ (\isasymlambda U.\ zero\_sheaf\_spec\ U)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymlambda U.\ one\_sheaf\_spec\ U)\ (identity\ Spec)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymlambda U.\ identity\ (\isasymO \ U))"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ scheme\ {\isacharequal}{\kern0pt}\ comm{\isacharunderscore}{\kern0pt}ring\ \isanewline
-\ \ \ \ \ {\isacharplus}{\kern0pt}\ locally{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}space\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ \isanewline
-\ \ \isakeyword{for}\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ {\isacharplus}{\kern0pt}\isanewline
-\ \ \isakeyword{assumes}\ are{\isacharunderscore}{\kern0pt}affine{\isacharunderscore}{\kern0pt}schemes{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymAnd}x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ X\ {\isasymLongrightarrow}\ {\isacharparenleft}{\kern0pt}{\isasymexists}U{\isachardot}{\kern0pt}\ x{\isasymin}U\ \isanewline
-\ \ \ \ \ \ \ \ \ \ {\isasymand}\ is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymand}\ \ {\isacharparenleft}{\kern0pt}{\isasymexists}f\ {\isasymphi}\isactrlsub f{\isachardot}{\kern0pt}\ affine{\isacharunderscore}{\kern0pt}scheme\ \ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ U\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}topology{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}open\ X\ is{\isacharunderscore}{\kern0pt}open\ U{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf\ {\isasymO}\isactrlsub X\ U{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}morphisms\ {\isasymrho}\ U{\isacharparenright}{\kern0pt}\ b\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}add{\isacharunderscore}{\kern0pt}str\ add{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}mult{\isacharunderscore}{\kern0pt}str\ mult{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}zero{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}ind{\isacharunderscore}{\kern0pt}sheaf{\isachardot}{\kern0pt}ind{\isacharunderscore}{\kern0pt}one{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str\ U{\isacharparenright}{\kern0pt}\ f\ {\isasymphi}\isactrlsub f{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{locale}\ scheme\ =\ comm\_ring\ \isanewline
+\ \ \ \ \ +\ locally\_ringed\_space\ X\ is\_open\ \isasymO \isactrlsub X\ \isasymrho \ b\ add\_str\ mult\_str\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero\_str\ one\_str\ \isanewline
+\ \ \isakeyword{for}\ X\ is\_open\ \isasymO \isactrlsub X\ \isasymrho \ b\ add\_str\ mult\_str\ zero\_str\ one\_str\ +\isanewline
+\ \ \isakeyword{assumes}\ are\_affine\_schemes:\ "\isasymAnd x.\ x\ \isasymin \ X\ \isasymLongrightarrow \ (\isasymexists U.\ x\isasymin U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \isasymand \ is\_open\ U\ \isasymand \ \ (\isasymexists f\ \isasymphi \isactrlsub f.\ affine\_scheme\ \ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ U\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ (ind\_topology.ind\_is\_open\ X\ is\_open\ U)\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ (ind\_sheaf.ind\_sheaf\ \isasymO \isactrlsub X\ U)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (ind\_sheaf.ind\_ring\_morphisms\ \isasymrho \ U)\ b\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (ind\_sheaf.ind\_add\_str\ add\_str\ U)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (ind\_sheaf.ind\_mult\_str\ mult\_str\ U)\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (ind\_sheaf.ind\_zero\_str\ zero\_str\ U)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (ind\_sheaf.ind\_one\_str\ one\_str\ U)\ f\ \isasymphi \isactrlsub f))"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ affine{\isacharunderscore}{\kern0pt}scheme{\isacharparenright}{\kern0pt}\ affine{\isacharunderscore}{\kern0pt}scheme{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}scheme{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}scheme\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}\ X\ is{\isacharunderscore}{\kern0pt}open\ {\isasymO}\isactrlsub X\ {\isasymrho}\ b\ add{\isacharunderscore}{\kern0pt}str\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult{\isacharunderscore}{\kern0pt}str\ zero{\isacharunderscore}{\kern0pt}str\ one{\isacharunderscore}{\kern0pt}str{\isachardoublequoteclose}
-\end{isabelle}
-
-\begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ empty{\isacharunderscore}{\kern0pt}scheme{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}scheme{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}scheme\ {\isacharbraceleft}{\kern0pt}{\isadigit{0}}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}nat{\isacharbraceright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isadigit{0}}\ {\isadigit{0}}\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ U{\isacharequal}{\kern0pt}{\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isacharbraceleft}{\kern0pt}{\isadigit{0}}{\isacharbraceright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U\ V{\isachardot}{\kern0pt}\ identity{\isacharbraceleft}{\kern0pt}{\isadigit{0}}{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}nat{\isacharbraceright}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isadigit{0}}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U\ x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\kern0pt}{\isasymlambda}U\ x\ y{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymlambda}U{\isachardot}{\kern0pt}\ {\isadigit{0}}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{lemma}\ (\isakeyword{in}\ affine\_scheme)\ affine\_scheme\_is\_scheme:\isanewline
+\ \ \isakeyword{shows}\ "scheme\ R\ (+)\ (\isasymcdot )\ \isasymzero \ \isasymone \ X\ is\_open\ \isasymO \isactrlsub X\ \isasymrho \ b\ add\_str\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ mult\_str\ zero\_str\ one\_str"
+\end{isabelle}
+
+\begin{isabelle}
+\isacommand{lemma}\ empty\_scheme\_is\_scheme:\isanewline
+\ \ \isakeyword{shows}\ "scheme\ \{0::nat\}\ (\isasymlambda x\ y.\ 0)\ (\isasymlambda x\ y.\ 0)\ 0\ 0\ \{\}\ (\isasymlambda U.\ U=\{\})\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymlambda U.\ \{0\})\ (\isasymlambda U\ V.\ identity\{0::nat\})\ 0\ (\isasymlambda U\ x\ y.\ 0)\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ (\isasymlambda U\ x\ y.\ 0)\ (\isasymlambda U.\ 0)\ (\isasymlambda U.\ 0)"
 \end{isabelle}
@@
 \section{Concluding Thoughts}
-\setlength{\parindent}{5ex}
+\setlength\parindent {5ex}
 
@@
 \begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ topological{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ \isanewline
-\ \ \isakeyword{fixes}\ S\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{assumes}\ open{\isacharunderscore}{\kern0pt}space\ {\isacharbrackleft}{\kern0pt}simp{\isacharcomma}{\kern0pt}\ intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ S{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}empty\ {\isacharbrackleft}{\kern0pt}simp{\isacharcomma}{\kern0pt}\ intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ {\isacharbraceleft}{\kern0pt}{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}imp{\isacharunderscore}{\kern0pt}subset{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}open\ U\ {\isasymLongrightarrow}\ U\ {\isasymsubseteq}\ S{\isachardoublequoteclose}\isanewline
-\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}inter\ {\isacharbrackleft}{\kern0pt}intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isasymlbrakk}is{\isacharunderscore}{\kern0pt}open\ U{\isacharsemicolon}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open\ V{\isasymrbrakk}\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \isakeyword{and}\ open{\isacharunderscore}{\kern0pt}union\ {\isacharbrackleft}{\kern0pt}intro{\isacharbrackright}{\kern0pt}{\isacharcolon}{\kern0pt}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isachardoublequoteopen}{\isasymAnd}F{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymAnd}x{\isachardot}{\kern0pt}\ x\ {\isasymin}\ F\ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ x{\isacharparenright}{\kern0pt}\isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymLongrightarrow}\ is{\isacharunderscore}{\kern0pt}open\ {\isacharparenleft}{\kern0pt}{\isasymUnion}x{\isasymin}F{\isachardot}{\kern0pt}\ x{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
+\isacommand{locale}\ topological\_space\ =\ \isanewline
+\ \ \isakeyword{fixes}\ S\ ::\ "'a\ set"\ \isakeyword{and}\ is\_open\ ::\ "'a\ set\ \isasymRightarrow \ bool"\isanewline
+\ \ \isakeyword{assumes}\ open\_space\ [simp,\ intro]:\ "is\_open\ S"\ \isanewline
+\ \ \ \ \isakeyword{and}\ open\_empty\ [simp,\ intro]:\ "is\_open\ \{\}"\ \isanewline
+\ \ \ \ \isakeyword{and}\ open\_imp\_subset:\ "is\_open\ U\ \isasymLongrightarrow \ U\ \isasymsubseteq \ S"\isanewline
+\ \ \ \ \isakeyword{and}\ open\_inter\ [intro]:\ "\isasymlbrakk is\_open\ U;\ is\_open\ V\isasymrbrakk \ \isasymLongrightarrow \ is\_open\ (U\ \isasyminter \ V)"\ \isanewline
+\ \ \ \ \isakeyword{and}\ open\_union\ [intro]:\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "\isasymAnd F::('a\ set)\ set.\ (\isasymAnd x.\ x\ \isasymin \ F\ \isasymLongrightarrow \ is\_open\ x)\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isasymLongrightarrow \ is\_open\ (\isasymUnion x\isasymin F.\ x)"
 \end{isabelle}
@@
 \begin{isabelle}
-\isacommand{inductive}\isamarkupfalse%
-\ generated{\isacharunderscore}{\kern0pt}topology\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \isakeyword{for}\ S\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{and}\ B\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set{\isachardoublequoteclose}\isanewline
+\isacommand{inductive}\ generated\_topology\ ::\ "'a\ set\ \isasymRightarrow \ 'a\ set\ set\ \isasymRightarrow \ 'a\ set\ \isasymRightarrow \ bool"\ \isanewline
+\ \ \ \ \isakeyword{for}\ S\ ::\ "'a\ set"\ \isakeyword{and}\ B\ ::\ "'a\ set\ set"\isanewline
 \ \ \isakeyword{where}\isanewline
-\ \ \ \ UNIV{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ S{\isachardoublequoteclose}\isanewline
-\ \ {\isacharbar}{\kern0pt}\ Int{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ {\isacharparenleft}{\kern0pt}U\ {\isasyminter}\ V{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \isakeyword{if}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ U{\isachardoublequoteclose}\ \isakeyword{and}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ V{\isachardoublequoteclose}\isanewline
-\ \ {\isacharbar}{\kern0pt}\ UN{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ {\isacharparenleft}{\kern0pt}{\isasymUnion}K{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ \isanewline
-\ \ \ \ \ \ \ \ \ \ \ \ \isakeyword{if}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymAnd}U{\isachardot}{\kern0pt}\ U\ {\isasymin}\ K\ {\isasymLongrightarrow}\ generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ U{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
-\ \ {\isacharbar}{\kern0pt}\ Basis{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}generated{\isacharunderscore}{\kern0pt}topology\ S\ B\ b{\isachardoublequoteclose}\ \isakeyword{if}\ {\isachardoublequoteopen}b\ {\isasymin}\ B\ {\isasymand}\ b\ {\isasymsubseteq}\ S{\isachardoublequoteclose}
-\end{isabelle}
-\begin{isabelle}
-\isacommand{lemma}\isamarkupfalse%
-\ generated{\isacharunderscore}{\kern0pt}topology{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}topology{\isacharcolon}{\kern0pt}\isanewline
-\ \ \isakeyword{fixes}\ S{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set{\isachardoublequoteclose}\ \isakeyword{and}\ B{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set{\isachardoublequoteclose}\isanewline
-\ \ \isakeyword{shows}\ {\isachardoublequoteopen}topological{\isacharunderscore}{\kern0pt}space\ S\ {\isacharparenleft}{\kern0pt}generated{\isacharunderscore}{\kern0pt}topology\ S\ B{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}
-\end{isabelle}
-\begin{isabelle}
-\isacommand{locale}\isamarkupfalse%
-\ homeomorphism\ {\isacharequal}{\kern0pt}\ \isanewline
-\ \ continuous{\isacharunderscore}{\kern0pt}map\ {\isacharplus}{\kern0pt}\ bijective{\isacharunderscore}{\kern0pt}map\ f\ S\ S{\isacharprime}{\kern0pt}\ {\isacharplus}{\kern0pt}\ \isanewline
-\ \ continuous{\isacharunderscore}{\kern0pt}map\ S{\isacharprime}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}open{\isacharprime}{\kern0pt}\ S\ is{\isacharunderscore}{\kern0pt}open\ {\isachardoublequoteopen}inverse{\isacharunderscore}{\kern0pt}map\ f\ S\ S{\isacharprime}{\kern0pt}{\isachardoublequoteclose}
+\ \ \ \ UNIV:\ "generated\_topology\ S\ B\ S"\isanewline
+\ \ |\ Int:\ "generated\_topology\ S\ B\ (U\ \isasyminter \ V)"\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \isakeyword{if}\ "generated\_topology\ S\ B\ U"\ \isakeyword{and}\ "generated\_topology\ S\ B\ V"\isanewline
+\ \ |\ UN:\ "generated\_topology\ S\ B\ (\isasymUnion K)"\ \isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \isakeyword{if}\ "(\isasymAnd U.\ U\ \isasymin \ K\ \isasymLongrightarrow \ generated\_topology\ S\ B\ U)"\isanewline
+\ \ |\ Basis:\ "generated\_topology\ S\ B\ b"\ \isakeyword{if}\ "b\ \isasymin \ B\ \isasymand \ b\ \isasymsubseteq \ S"
+\end{isabelle}
+\begin{isabelle}
+\isacommand{lemma}\ generated\_topology\_is\_topology:\isanewline
+\ \ \isakeyword{fixes}\ S::\ "'a\ set"\ \isakeyword{and}\ B::\ "'a\ set\ set"\isanewline
+\ \ \isakeyword{shows}\ "topological\_space\ S\ (generated\_topology\ S\ B)"
+\end{isabelle}
+\begin{isabelle}
+\isacommand{locale}\ homeomorphism\ =\ \isanewline
+\ \ continuous\_map\ +\ bijective\_map\ f\ S\ S'\ +\ \isanewline
+\ \ continuous\_map\ S'\ is\_open'\ S\ is\_open\ "inverse\_map\ f\ S\ S'"
 \end{isabelle}

### 2021-04-09 article.tex
Very minor updates

@@
 \\
-Also, Buzzard \textit{et al.} mentions another difficulty encountered when proving that an affine scheme is a scheme. 
+Also, Buzzard \textit{et al.} mention another difficulty encountered when proving that an affine scheme is a scheme. 
 \begin{quote}
@@
 where $\iota: \spec \rightarrow \spec$ is here simply the identity map.
-If, again, we gave a slightly different formulation for the definition of a scheme, following Hartshorne~\cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a direct counterpart in Isabelle, since it arose because of the difference between the so-called \textit{equality types} and the \textit{definitional equality}, a difference which is peculiar to dependent type theories.
+If, again, we gave a slightly different formulation for the definition of a scheme, following Hartshorne~\cite{hartshorne} instead of the Stacks project \cite{stacksproject} as they did, it seems that this difficulty cannot possibly have a direct counterpart in Isabelle, since it arose from the difference between the so-called \textit{equality types}, also known as \textit{identity types}, and the \textit{definitional equality}, a difference which is peculiar to dependent type theories.
 \\

### 2021-04-09 article.tex
Improve a couple of sentences

@@
 \emph{Sublocale} declarations provide a means of proving inclusions between apparently unrelated locales.
-We found that locales handled the tangle of definitions building up to schemes straightforwardly.
+We found that locales handled the tangle of definitions building up to schemes faithfully and concisely.
 
 However, the right way to formalise algebra is not obvious.
+During the formal development the user has to decide how mathematical knowledge should be best structured in the proof assistant so that it can be used mechanically in an efficient way.
 It is well-known in the Isabelle community that the main algebra library needs to be rebuilt from scratch.

### 2021-04-09 article.tex
Very minor update

@@
 
-However, the right way to formalise algebra is not obvious.
-During the formal development the user has to decide how mathematical knowledge should be best structured in the proof assistant so that it can be used mechanically in an efficient way.
+However, the right way to formalise advanced algebra is not obvious.
+During the formal development the user has to decide how mathematical structures should be best organized in the proof assistant so that they can be used mechanically in an efficient way.
 It is well-known in the Isabelle community that the main algebra library needs to be rebuilt from scratch.

### 2021-04-09 article.tex
Remove Lamport reference and use Coquelicot instead

@@
 \end{quote}	    
-However, all these difficulties in Lean, where three attempts at defining schemes were required, raise the question of whether dependent types could be, at least in some situations, more of a burden than an advantage \cite{PaulsonLamport}.
+However, all these difficulties in Lean, where three attempts at defining schemes were required, raise the question of whether dependent types could be, at least in some situations, more of a burden than an advantage.
+The issue with dependent types has also been highlighted in the context of formalising analysis in the proof assistant Coq.
+\begin{quote}
+	A more salient issue is the overall use of dependent types for defining some notions.
+For instance, [\dots] rewriting an expression such as $(f+~g)'(x)$ into $f'(x)+g'(x)$, while straightforward in mathematics, is next to impossible to achieve in Coq, as the proof terms have to be manually built by the user beforehand.
+Third, these proof terms can quickly blow up, and thus become impossible for the user to exhibit, \textit{e.g.} in the case of iterated derivatives or differentiation under an integral.
+By the way, integrals in Coq suffer from the same issues.
+\cite[1.]{boldo2015coquelicot}
+\end{quote}	 
 Moreover, in the age of machine learning, one may expect there is a trade-off between the expressiveness of a type theory and one's ability to subject it to automation, for instance through SMT solvers and the so-called hammers embedded in some proof assistants.

### 2021-04-09 article.tex
Add a remark on Chicli's Coq code

@@
 
+% To define a Keywords section: 
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+
 % notations:
@@
 
+\keywords{Formal Verification, High-order Logic, Type Theory, Algebraic Geometry, Schemes}
+
 \section{Motivation and Problems}
@@
 In 2003, Laurent Chicli, as the topic of his PhD thesis \cite{chiclithesis}, formalized sheaves and affine schemes in the proof assistant Coq \cite{coqrefmanual}, which is based on a powerful dependent type theory known as the \emph{Calculus of Inductive Constructions} \cite{coquand1986calculus, coquand1988inductively}.
+However, Chicli's Coq code certainly became deprecated long ago.
 More recently, in 2019 Grothendieck's schemes \cite{GrothendieckEGAI} have been formalized by a group of mainly six mathematicians led by Kevin Buzzard \cite{schemesinLean} using the brave new Lean theorem prover, which is based on a similar dependent type theory \cite{de2015lean}.
@@
 \\
-The formalized material has a size of roughly 7300 lines of code, including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring and much else) and even our partial reconstruction of the topology library (down to the notion of a topological space).
+The formalized material has a size of roughly 7300 lines of code \cite{Grothendieck_Schemes-AFP}, including all the prerequisites in commutative  algebra (prime and maximal ideals, localization of a ring and much else) and even our partial reconstruction of the topology library (down to the notion of a topological space).
 Given the output of this work, a formalization of schemes in Isabelle, such a relatively short formalization conveys the power of Isabelle module systems.

### 2021-04-09 article.tex
Updates from Overleaf

@@
 For instance, [\dots] rewriting an expression such as $(f+~g)'(x)$ into $f'(x)+g'(x)$, while straightforward in mathematics, is next to impossible to achieve in Coq, as the proof terms have to be manually built by the user beforehand.
-Third, these proof terms can quickly blow up, and thus become impossible for the user to exhibit, \textit{e.g.} in the case of iterated derivatives or differentiation under an integral.
+Third, these proof terms can quickly blow up, and thus become impossible for the user to exhibit, \textit{e.g.}\ in the case of iterated derivatives or differentiation under an integral.
 By the way, integrals in Coq suffer from the same issues.
-\cite[1.]{boldo2015coquelicot}
+\cite[p.\ts42]{boldo2015coquelicot}
 \end{quote}	 
@@
 Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).  \\
-Anthony Bordg thanks Kevin Buzzard for his stimulating wit and his communicative energy.
+We thank Kevin Buzzard for his stimulating wit and his communicative energy.
 
